### 2025-01-20 paper/paper.tex
Added paper and all plots for voltage divider.

\documentclass[reprint,superscriptaddress,prb,floatfix,showkeys]{revtex4-2}
\usepackage{empheq}
\usepackage{float}
\usepackage{lipsum}
\usepackage{mathtools, cuted}
\usepackage{esvect}
\usepackage{xcolor}
\usepackage[caption = false]{subfig}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{physics}
\usepackage[mathlines]{lineno}
\usepackage[capitalise]{cleveref}
\usepackage[english]{babel}
\usepackage{orcidlink}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}

%------------- COMMANDS -------------

\newcommand{\C}{\mathbb{C}} %complex
\newcommand{\R}{\mathbb{R}} %reals
\newcommand{\Z}{\mathbb{Z}} %integers
\renewcommand{\P}{\mathbb{P}} %prob

\newcommand{\m}{\text{m}} %m index
\newcommand{\M}{\text{M}} %m index
\newcommand{\N}{\text{N}} %n index
\newcommand{\n}{\text{n}} %n index
\renewcommand{\a}{\textbf{\text{a}}} %a index

\newcommand{\brac}[1]{\left(#1 \right)} %nice brackets
\newcommand{\bk}[1]{\langle #1 \rangle}

\newcommand{\TODO}[1]{\textcolor{red}{TODO: #1}}

%------------- MAIN -------------

\begin{document}

\title{Efficient Machine Learning in a Memristor Network}

\author{Monica Conte}
\affiliation{Soft Condensed Matter \& Biophysics, Debye Institute for Nanomaterials Science, Utrecht University, Princetonplein 1, 3584 CC Utrecht, The Netherlands.}

\date{\today}

\begin{abstract}
    Inspired by the brain's energy-efficient processing, we propose a physical implementation of artificial neural networks to surpass digital systems in speed and energy efficiency. We consider a network with nodes connected by conical microfluidic memristor channels filled with aqueous electrolyte [1]. These memristors exhibit tunable conductance, responsive to electrical, chemical, and mechanical stimuli, as well as channel geometry. Based on this adaptability, we develop a hybrid training algorithm that adjusts either channel geometry or external stimuli as weights. Physical relaxation replaces the feedforward pass, while a combined physical-numerical gradient descent drives the backward pass. This approach enables tasks such as input-output voltage mapping and linear regression.
\end{abstract}
\maketitle

\renewcommand{\figurename}{FIG.}

\section{\label{sec:Intro}Introduction}

% ## Artificial Neural Networks ##
% - What they can achieve
% - Energy cost
% - Explain the two phases

Artificial neural networks (ANNs) have become central to many technological advancements, achieving remarkable success in tasks ranging from image recognition to natural language processing. These networks typically operate in two phases: inference and backpropagation. The energy requirements of ANNs has grown significantly, negatively impacting the efficiency and scalability of ANNs \cite{energy_cost}.

% ## Physical Neural Networks ##
% - what they are, what is the scope (physical instead of math training)
% - advantages: faster, computations are less energy demanding.

While the inference energy consumption has been addressed by hardware accelerators, the backpropagation still remains a problem. As an alternative to ANN performed strictly in-silico, physical neural networks (PNN) have been introduced, where physical processes rather than mathematical operations are trained \cite{}. In fact, physical processes are often faster and consume less energy than their digital counterpart.

% ## PNN algorithms in literature ##

% ## Our networks and our algorithm ##

Not only, but physical neural networks make the similarity with the human brain more evident, opening the doors to the development of an artificial brain. For this, we choose to work with networks whose constructing elements are memristors living in aqueous solution and that respond to electrical, chemical and mechanical stimuli at the same time.

Fluidic channels are emerging as a promising technology in the field of neuromorphic computing due to their ability to emulate synaptic functions. These nanoscale devices can store information through conductance changes. Their unique properties make them suitable for implementing artificial neural networks and other types of electrical networks.

In recent years, machine learning algorithms have increasingly been applied to memristor networks to train specific input-output relations. These algorithms typically modify the dynamics of the memristors to achieve desired computational tasks.

% ## What we could achive ##

% ## Structure of the paper ##

The paper is roganized as follows. Section 2 reviews related work on memristor networks, machine learning algorithms, and physical learning methods. Section 3 describes the methods used in our study, including the network model, machine learning algorithm, and the physical learning approach. In Section 4, we present our proposed method for coupling memristors with capacitors and discuss the necessary properties for effective training. Section 5 details our experimental setup and implementation. The results and analysis are provided in Section 6, followed by conclusions and suggestions for future work in Section 7.

\newpage

\section{\label{sec:memristor_network}Memristor Network}

The PNN we consider is an electrical network make of nodes connected by resistive elements. As resistive elements, we consider conical microfluidic channels that are schematically represented in \cref{fig:memristor_scheme}. 
\begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth]{plots/memristor/memristor_scheme.pdf}
    \caption{A schematic representation of the conical fluidic memristor. A cone of lenght $L$, base radius $R_b$ and tip radius $R_t$ with charged surface connnects two bulk reservoirs of a 1:1 electrolyte in an acqueous solution. The bulk density in the base $\rho_b$ differs from the bulk density in the tip $\rho_t$. At the far side of the memristor, an electrical potential and pressure drop are applied. Overall, this results in a chemical, electrical and mechanical sensistive system.}
    \label{fig:memristor_scheme}
\end{figure} 
An azimuthally symmetric conical channel connects two reservoirs that contain an incompressible aqueous 1:1 electrolyte with viscosity $\eta=1.01mPa s$ containing ions with diffusion coefficients $D = 1.75\mu m^2 ms^{-1}$ and charge $\pm e$ with $e$ the proton charge. The cone has a base radius of $R_b = 200$nm, a tip radius of $R_t=50$nm and has a length $L = 10\mu$m, which sets it in the long channel limit where entrance and exit effects can be neglected. The walls of the channel are homogeneously charged and generate a surface potential $\psi_0$ that attracts the opposite-sign ions present in the solution due to the dissociation of the electrolyte. The electric potential decreases exponentially away from the surface due to the electrostatic screening of the attracted ions: an electric double layer (EDL) forms on the charged surfaces.

At the far side of both reservoirs, electrical potential, pressure and ion concentration are imposed. As a result, the memristor feels a potential drop $\Delta V = V_b - V_t$ defined as the difference between the potential in the base and in the tip. The ions within the EDL region generate an electro-osmotic fluid flow $Q_V = (\pi R_b R_t\epsilon\psi_0/L\eta)\Delta V$. Meanwhile, the pressure drop $\Delta P = P_b - P_t$, given by the difference between the base and the tip pressure, induces a Poiseuille-like flow $Q_P = (\pi R_b^3 R_t^3/8L\eta\langle R^2\rangle)\Delta P$. Finally, the ions experience a concentration gradient $\Delta \rho = \rho_b - \rho_t$, defined by the difference between the ion concentration in the reservoir connected to the base of the channel, $\rho_b$, and the concentration at the tip, $\rho_t$. Consequently, a diffusive fluid flow arises. However, we consider only the pressure and potential contributions to the total fluid flow, $Q = Q_P + Q_V$, assuming the diffusive flow to be negligible.  The resulting fluid flow generates non-trivial ion concentration profiles which, in turn, directly infulences the channel's conductance $g$. 
%It has already been shown that, for $\Delta P = 0$, the channel shows current rectification, thus working as a diode \cite{}, due to concentration polarization.

In the steady-state, the channel is exposed to constant chemical, pressure and electrical signal, the corresponding conductance $g_{\infty}\brac{\boldsymbol{\Delta}}$ depends on the three stimuli $\boldsymbol{\Delta}= (\boldsymbol{\Delta})$ and is determined by the ion concentration profiles according to 
\[
\frac{g_{\infty}\brac{\boldsymbol{\Delta}}}{g_0} = \int_0^{L} \frac{\bar{\rho}\left(x, \boldsymbol{\Delta}\right)}{2\rho_b L} dx                                           
\]
where $g_0$ is the Ohmic conductance and $\bar{\rho}(x)$ the radially averaged salt concentration as a function of $x\in[0,L]$\cite{Rene_IonicNeuromorphic}. By solving the stationary condition of the total salt flux, an expression for the average salt concentration can be found and reads
\begin{multline}
\frac{\bar{\rho}\left(x, \boldsymbol{\Delta}\right)}{2\rho_b} = 1 - \frac{\Delta \rho}{\rho_b} \mathcal{I}\left(x, \Delta V, \Delta P\right) \\
 + \frac{ \rho_{in}\left( \Delta V \right) }{2\rho_b \text{Pe}} \left[ \mathcal{F}(x) - \mathcal{I}\left(x, \Delta V, \Delta P\right) \right]
\label{eq:rho_average}
\end{multline}
where we defined, for the sake of simplicity and readability, two functions
\[
\mathcal{I}\left(x, \Delta V, \Delta P\right) = \frac{e^{\frac{x}{L}\frac{R_t^2}{R_b R(x)} \text{Pe}}-1}{e^{\frac{R_t}{R_b} \text{Pe}}-1}, \ \ \ \ \mathcal{F}(x) = \frac{x}{L}\frac{R_t}{R(x)}.
\]
Moreover, we introduced an expression for the concentration inhomogeneity 
\[
\rho_{in}\brac{\Delta V} = 2\frac{(R_b-R_t)\sigma}{R_t^2}\frac{e\Delta V}{k_B T}
\]
and the Péclet number
$
\text{Pe} = QL/D\pi R_t^2
$
which quantifies the importance of the flow $Q$ over diffusion \cite{Rene_PressureSensitive}.

%To better deal with numerical instabilities, we use a limit expression of \cref{eq:rho_average} when $\text{Pe} \ll \left( R_b/R_t \right)^2$ \cite{Rene_PressureSensitive}. With this consideration, the expression for the average salt concentration we use is the following
%\[
%\frac{\rho(x)}{2\rho_b} = 
%\begin{array}{cc}
 % \{ & 
  %  \begin{array}{cc}
   %   0 & x\leq 0 \\
    %  \frac{100-x}{100} & 0\leq x\leq 100
    %\end{array}
%\end{array}
%\]

When the external stimuli vary dynamically in time, they generate ion accumulation and deplition in the channel, changing consequently the conductivity. We assume the dynamics of the time-dependent conductance $g(t)$ as a single exponential decay towards the steady-state conductance $g_{\infty}$ with a diffusion-like timescale $\tau = L^2/12D$, as in Ref. \cite{Rene_IonicNeuromorphic}. The equation for the conductance reads
\begin{equation}
\frac{\partial g\brac{\boldsymbol{\Delta}(t), t}}{\partial t} = \frac{g_{\infty}\brac{\boldsymbol{\Delta}(t)}-g\brac{\boldsymbol{\Delta}(t), t}}{\tau}
\label{eq:eqofmotconductance}
\end{equation}
with $\boldsymbol{\Delta}(t) = \brac{\Delta V\brac{t},\Delta P\brac{t}, \Delta \rho\brac{t}}$
As in Ref. \cite{Rene_IonicNeuromorphic}, we consider the time scale relative to voltage-driven ion accumulation or depletion in the channel. We justify this choice by stating that pressure-driven dynamics is faster and recalling that we neglect chemically-driven transport. Due to the fact that the conductance depends on the history of the signals applied, this system is called memristor. Aside from the direct dependence of the conductance on the external stimuli $\boldsymbol{\Delta}$, there is an implicit dependence on the geometricl properties such as lenght $L$ and radius ratio $R_b/R_t$ that we choose to consider.

The PNN is composed of $\N$ nodes, an example is shown in \cref{fig:memristor_network}. 
\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\columnwidth]{plots/memristor/memristor_network.pdf}
    \caption{An example of a network of five nodes connected by six memristors. The nodes are divided in input nodes (green circles), hidden nodes (gray nodes) and output nodes (purple circles) each of them is characterized by a triplet of physical quantities, representing the potential, pressure, and density. Th resulting stimuli on the memristor is given by the difference between base and tip signal, it thus depends on the oreintation of the memristor. In the case of the memristor that connects the first and the second node, for example, the exteranl stimuli are $\Delta V = V_2 - V_1$, $\Delta P = P_2 - P_1$ and $\Delta \rho = \rho_2 - \rho_1$. The zig-zag lines directed towards the input nodes indicate where the electrical signal is applied, while the zig-zag lines pointing outwards from the nodes indicate where the electrical signal is measured.}
    \label{fig:memristor_network}
\end{figure} 
Each node $\n\in[1,\N]$ is characterized by a value of electrical potential $V_{\n}$, pressure $P_{\n}$ and bulk density $\rho_{\n}$. Even though each node in the network is characterized by three physical properties, only electrical current flows through the network. This current propagates via the memristive elements, enabling modifications to the electric potential at other nodes. In contrast, pressure and density are externally imposed at each node and do not propagate through the network. The set of nodes is divided in thee sets. A node belongs to the set of \textit{input nodes} if it is used to imput current in the circuit, its value of voltage is known and fixed. After the imputs are imposed, the electrical signal travels throught the network and the resulting output potential is read in the nodes belonging to \textit{output nodes}. The remaining nodes, that do not function as input or output, are included in the set of \textit{hidden nodes}.

The nodes in the PNN are connected by $\M$ memristive elements. Consequently, a memristor connecting two nodes experinces potential drop, pressure drop and concentration gradient given by the difference between the node where the base of the memristor is connected to, and the node to which the tip is linked. The memristor is characterized by its conductance state $g_{\m}$ with $\m\in[1,\M]$, consequence of both the geomtery parameters and the external stimuli.

To solve numerically the resulting circuit, it is necessary to simultaneously address the circuit equations and the time evolution equation for the memristors' conductance. 
The circuit equations are handled using the open-source circuit solver \textsc{AHKAB}\cite{}, which computes the electric potentials at the nodes and the currents through the edges discretizing the differential equations in timesteps $\Delta t$. To incorporate the memristive elements, we approximate the time evolution of the conductances using a discretized form of \cref{eq:eqofmotconductance}, employing the Euler-forward method. Specifically, the conductance at a given timestep is calculated from its value at the previous timestep as:
\begin{multline}
g_{\m}\brac{\boldsymbol{\Delta}(t), t} = g_{\m}\brac{\boldsymbol{\Delta}(t), t-\Delta t} + \\
 \frac{g_{\m,\infty}\brac{\boldsymbol{\Delta}(t)-g_{\m}\brac{\boldsymbol{\Delta}, t}}}{\tau}\Delta t.
\end{multline}
In this work, we only apply constant voltage supplies to the input nodes of the circuit. Nonetheless, we notice that solving the dynamical equations is needed due to the dynamical change in the conductance of the memristors that, in turn, results in time-dependent potential drops across them.

\section{Training Algorithm for a Memristor Network}

As in a traditional algorithm for an ANN, the core mechanism of the training is to modify the weights associated to the connections of the network such that it maps specific inputs to desired outputs. In the case of the electrical network at hand, the training algorithm is designed to output desired voltage values in the output nodes, applying specific voltage values in the input nodes.
\begin{figure}[!h]
    \centering
    \includegraphics[width=0.8\columnwidth]{plots/training/two_types_weights.pdf}
    \caption{(a) Memristor network with weights defined in the nodes. (b) Memristor network where wegiths characterize each edge.}
    \label{fig:two_types_weights}
\end{figure} 
\begin{figure*}[t] 
    \centering
    \includegraphics[width=\textwidth]{plots/training/training_scheme.pdf}
    \caption{}
    \label{fig:training_scheme}
\end{figure*}
Recalling that the dynamics of the memristors we consider depends on both external stimuli and geometrical properties, we have several possibilities for defining the weights of the network. However, there is a fundamental distinction between these two categories: external stimuli are applied to the nodes, while geometrical properties are defined edge-wise. Consequently, we distinguish between a training algorithm where the weights are defined on the nodes, as in \cref{fig:two_types_weights}(a), and one where the weights are defined on the edges, see \cref{fig:two_types_weights}(b). In this work, we focus on training a single property as the weight, while keeping all other parameters fixed as initially defined. For example, we may select an external stimulus, such as the imposed pressure or the density at each node. Alternatively, we can choose the length or radius ratio between the base and tip of the channel. The training process is carried out by iterating a scheme, illustrated in \cref{fig:training_scheme}, which consists of two phases: a forward pass and a backward pass.

In the feedforward phase, the network is fed with specific electric potential in the input nodes. Following both circuit laws and memristor's dynamics, the network reaches a steady state where electrical potentials can be measured in the output nodes. Clearly, the output of the network depends on the set of weights imposed on the network $\boldsymbol{w}$, regardless them being node or edge defined. The value of the outputs can be used to quantify the status of the network, meaning that it indicated how far the answer of the network is from the desired one. Specifically, we define a cost function that computes the difference squared between the voltage in the output nodes and the values of desired voltages
\[
C\left( \boldsymbol{w} \right) = \sum_{i \in \Lambda} \brac{V_i\brac{\boldsymbol{w}} - V_i^D}^2,
\]
where $\Lambda$ represents the set of indeces belonging to the output nodes, $V_i\brac{\boldsymbol{w}}$ the voltage measured in the output nodes and $V^D$ is a vector containing the values of desired output nodes.

The backward phase has the fundamental purpose of finding a set of weights that minimize the cost function. We follow the method of the \textit{steepest descent}, for which the update of the weights from one training step $s$ to the following $s+1$,
\begin{equation}
\boldsymbol{w}^{s+1} = \boldsymbol{w}^{s} - \alpha \boldsymbol{\nabla}C\brac{\boldsymbol{w}},
\label{eq:weight_update}
\end{equation}
results in a decrease in the cost funtion until a minimum is reached, for sufficienlty small values of $\alpha$ \cite{steepest_descent_book}. The gradient in the update rule is computed using a \textit{finite differences method}
\begin{equation}
\boldsymbol{\nabla}C\brac{\boldsymbol{w}} = \frac{C\brac{\boldsymbol{w}+\boldsymbol{\Delta w}}-C\brac{\boldsymbol{w}}}{\Delta w},
\label{eq:gradient_cost_func}
\end{equation}
where $\boldsymbol{\Delta w}$ is a vector with the same number of entries as the weight vector, but every entry has a value $\Delta w$.

In the training algortihm, we first initialize the system with the memristor parameters specified in \cref{sec:memristor_network} and with some initial pressure and concentration values at each node. With the knowledge of input and desired output voltage values, it is possible to performe the first forward pass, from which we obtain the cost function $C\brac{\boldsymbol{w}}$, that we store since it is needed in the computation its gradient. Subsequently, we proceed with the backward pass. We compute each entry of the gradient in \cref{eq:gradient_cost_func} by selecting the corresponding weight, a node or an edge parameter, increment its value of $\Delta w$ and applying a forward step to obtain the corresponding entry of $C\brac{\boldsymbol{w}+\boldsymbol{\Delta w}}$. With the stored value of $C\brac{\boldsymbol{w}}$, we are able to compute the gradient in \cref{eq:gradient_cost_func} and use it to eventually calculate the weight update in \cref{eq:weight_update}.

Althought performed numerically in this work, we highlight that the feedforward pass is a physical process in which the system natually relaxes to its steady state. Moreover, also the backward pass we use can be translated to a physical event since involves performing the forward pass a number of time as the number of the weights. Once the cost functions are determined, only the simple algebric calculations of \cref{eq:weight_update} are left to be computed. We peopse this method as a hybrid physical and in-silico training algorithm also as a future experimental approach to the probelm.

\subsection{Training a Voltage Divider}

A voltage divider is an electrical circuit made of two resistances connected in series, that returns a fraction of the input voltage. Given the simplicity of its structure, we use it as an initial playground for the training algorithm described above. Specifically, we choose the lenghts of the memristor channels as the weights, to be trained such that giving $V_1 = 5V$ and $V_3 = 0V$ as inputs, we get $V_2 = 4V$ as output. In \cref{fig:vd_scheme} a schematic of the memristor voltage divider is shown.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\columnwidth]{plots/voltage_divider/vd_scheme.pdf}
    \caption{}
    \label{fig:vd_scheme}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth]{plots/voltage_divider/mse_weights.pdf}
    \caption{}
    \label{fig:cont_disc_gen}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\columnwidth]{plots/voltage_divider/evolution_finalnw.pdf}
    \caption{}
    \label{fig:cont_disc_gen}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\columnwidth]{plots/voltage_divider/mse_others.pdf}
    \caption{}
    \label{fig:cont_disc_gen}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth]{plots/voltage_divider/weights_others.pdf}
    \caption{}
    \label{fig:cont_disc_gen}
\end{figure}

\cleardoublepage
\subsection{Linear Regression}

\section{Conclusion}

\appendix

\clearpage
\bibliographystyle{unsrt} 
\bibliography{biblio}

\end{document}

### 2025-01-20 codes/parameters.py

@@ -18,6 +18,7 @@ color_font_edges = 'white'
 # --------- PLOTS STYLES ---------
 
 figsize_2horizontal = (11,5)
+figsize_3horizontal = (13,5)
 figsize_1 = (4.4,4)
 
 legend_size = 15
@@ -27,7 +28,7 @@ marker_size = 10
 
 
 mse_styles = {
-    'allostery_length': dict(c = "mediumpurple", lw=3, label = rf'$L$'),
+    'allostery_length': dict(c = "green", lw=3, label = rf'$L$'),
     'allostery_rho': dict(c = "plum", lw=3, label = rf'$\rho$'),
     'allostery_rbrt': dict(c = "darkgray", lw=3, label = rf'$R_b/R_t$'),
     'allostery_pressure': dict(c = 'mediumpurple', lw=3, label = rf'$P$')

### 2025-01-20 codes/training.py

@@ -13,7 +13,6 @@ def write_weights_to_file(G, step, weight_type, path_patch):
     
     for index, edge in enumerate(G.edges()): 
         if weight_type=='length' or weight_type=='rbrt':
-            print(G.edges[edge][weight_type])
             file.write(f"{index}\t{G.edges[edge][weight_type]}\n")
     for node in G.nodes():
         if weight_type=='pressure' or weight_type=='rho':  
@@ -110,15 +109,9 @@ def update_weights(G,base_error, weight_type, delta_weight, learning_rate):
                 
             gradients.append((new_error - base_error)/denominator)
 
-            # print((new_error - base_error), denominator)
-        
         for node in G.nodes():
 
             G.nodes[node][f'{weight_type}'] -= learning_rate*gradients[int(node)]
-            # print(G.nodes[node][f'{weight_type}'])
-
-            # print(learning_rate, gradients[int(node)], learning_rate*gradients[int(node)])
-             
     else:
 
         for index, edge in enumerate(G.edges()):
@@ -134,13 +127,10 @@ def update_weights(G,base_error, weight_type, delta_weight, learning_rate):
                 denominator = delta_weight
             
             gradients.append((new_error - base_error)/delta_weight)
-            # print((new_error - base_error), delta_weight)
-
             
         for index, edge in enumerate(G.edges()):    #Different loop cause you don't want to change edges yet
 
             G.edges[edge][f'{weight_type}'] -= learning_rate*gradients[index]
-            # print(learning_rate, gradients[index],learning_rate*gradients[index])
 
         
     return G

### 2025-01-20 codes/voltage_divider.py

@@ -41,6 +41,32 @@ plotting.plot_potential_drops_each_node(ax, G_ml)
 fig.tight_layout()
 fig.savefig(f"../paper/plots/voltage_divider/evolution_finalnw.pdf")
 
+# --------- PLOT ERROR AND WEIGHTS WITH OTHER WEIGHTS ---------
+
+G_ml = G.copy(as_view=False)  
+# training.train(G_ml, training_steps=training_steps, weight_type='length', delta_weight = 1e-3, learning_rate=10)
+G_ml = G.copy(as_view=False)  
+# training.train(G_ml, training_steps=training_steps, weight_type='rbrt', delta_weight = 1e-3, learning_rate=2)
+G_ml = G.copy(as_view=False)  
+# training.train(G_ml, training_steps=training_steps, weight_type='rho', delta_weight = 1e-5, learning_rate=1e-3)
+
+fig, ax = plt.subplots(figsize = par.figsize_1)
+plotting.plot_mse(ax, fig, f'allostery_length')
+plotting.plot_mse(ax, fig, f'allostery_rbrt')
+plotting.plot_mse(ax, fig, f'allostery_rho')
+ax.legend()
+fig.tight_layout()
+fig.savefig(f"../paper/plots/voltage_divider/mse_others.pdf")
+
+fig, ax = plt.subplots(1, 3, figsize = par.figsize_3horizontal)
+plotting.plot_weights(ax[0], G, training_steps=training_steps, training_job='allostery', weight_type='length')
+plotting.plot_weights(ax[1], G, training_steps=training_steps, training_job='allostery', weight_type='rbrt')
+plotting.plot_weights(ax[2], G, training_steps=training_steps, training_job='allostery', weight_type='rho')
+# ax.legend()
+fig.tight_layout()
+fig.savefig(f"../paper/plots/voltage_divider/weights_others.pdf")
+
+
 end = time.time()
 
 print("Running time = ", end-start, "seconds")

### 2025-01-27 paper/paper.tex
New paper plot with mse and errors

@@
 
-\section{Training Algorithm for a Memristor Network}
+\section{\label{sec:training}Training Algorithm for a Memristor Network}
 
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\columnwidth]{plots/voltage_divider/mse_weights.pdf}
-    \caption{}
-    \label{fig:cont_disc_gen}
-\end{figure}
+We initialize the system with pressures $P_1 =  P_2 = 1 bar$ and ion concetration $\rho_1 = \rho_2 = 0.2 mM$ on each node, length $L_1 = L_2 = 10\mu m$ and base to tip radius ratio $R_1 = R_2 = 4$ on each edge.
+After choosing one of these four physical quantities as training parameter $\boldsymbol{w} = \brac{w_1, w_2}$, we implement the training as descibe in \cref{sec:training} that modifies it, while the other parameters are kept constant.
+In \cref{} we show that the cost function decreases of many order
 

### 2025-01-27 codes/parameters.py

@@ -2,8 +2,8 @@
 
 DATA_PATH = '../data/'
 PLOT_PATH = '../plots/'
-PACKAGE_PATH = '/home/monicaconte/nica/phd/Projects/Learning_with_memristors/Learning_Neural_Networks/codes/ahkab'
-# PACKAGE_PATH = '/Users/monicaconte/PhD/Projects/Contrastive_Learning_Memristors/Learning_Neural_Networks_true/codes/ahkab'
+# PACKAGE_PATH = '/home/monicaconte/nica/phd/Projects/Learning_with_memristors/Learning_Neural_Networks/codes/ahkab'
+PACKAGE_PATH = '/Users/monicaconte/PhD/Projects/Contrastive_Learning_Memristors/Learning_Neural_Networks_true/codes/ahkab'
 
 # --------- NETWORKS PLOTS STYLES ---------
 
@@ -30,8 +30,8 @@ marker_size = 10
 # -> MSE style
 
 from pypalettes import load_cmap
-cmap = load_cmap("facelift")
-# cmap = load_cmap("Andri")
+# cmap = load_cmap("facelift")
+cmap = load_cmap("Callanthias_australis")
 
 mse_styles = {
     'allostery_length': dict(c = cmap.colors[0], lw=3, label = rf'$L$'),
@@ -40,6 +40,28 @@ mse_styles = {
     'allostery_pressure': dict(c = cmap.colors[3], lw=3, label = rf'$P$'),
 }
 
+# -> WEIGHTS style
 
 
-
+weight_styles = {
+    'weight_allostery_length': {'plot_style' : dict(lw=3, label = rf'$L$'),
+                                'type_weights' : 'edge',
+                                'label' : r'$L$[$\mu$ m]',
+                                'base_color' : cmap.colors[0]
+    },
+    'weight_allostery_rho': {'plot_style' : dict(lw=3, label = rf'$\rho$'),
+                            'type_weights' : 'node',
+                            'label' : r'$\rho$[mM]',
+                            'base_color' : cmap.colors[1]
+    },
+    'weight_allostery_rbrt': {'plot_style' : dict(lw=3, label = rf'$R$'),
+                            'type_weights' : 'edge',
+                            'label' : 'R',
+                            'base_color' : cmap.colors[2]
+    },
+    'weight_allostery_pressure': {'plot_style' : dict(lw=3, label = rf'$P$'),
+                            'type_weights' : 'node',
[…]

### 2025-01-27 codes/plotting.py

@@ -7,6 +7,22 @@ sys.path.append(par.PACKAGE_PATH)
 import ahkab  
 import networks
 
+from matplotlib.colors import to_rgb, to_hex
+def lighten_color(base_color, factor=0.5):
+    """
+    Lightens a given color by blending it with a lighter shade of itself.
+    
+    Parameters:
+    - base_color: A HEX color or an (R, G, B) tuple in normalized [0, 1] range.
+    - factor: Float, how much to lighten the color (0 = no change, 1 = fully white).
+    
+    Returns:
+    - Lightened color as a HEX string.
+    """
+    base = to_rgb(base_color)  # Convert to RGB if it's a HEX string
+    lightened = [(1 - factor) * c + factor for c in base]  # Blend toward lighter version of itself
+    return to_hex(lightened)
+
 def plot_graph(name_graph):
 
     # GET graph data
@@ -49,46 +65,32 @@ def plot_mse(ax, fig, rule):
     ax.semilogy(x, y, **par.mse_styles[f'{rule}'])   
     
     # ax.legend(fontsize = par.legend_size)
-    ax.set_ylabel(r'Error', fontsize = par.axis_fontsize)
+    ax.set_ylabel(r'$C(w)$', fontsize = par.axis_fontsize)
     ax.set_xlabel(r'Training steps', fontsize = par.axis_fontsize)
     ax.tick_params(axis='both', labelsize=par.size_ticks)
 
 import colormaps
 from pypalettes import load_cmap
 
-def plot_weights(ax, G, training_steps, training_job, weight_type):
+def plot_weights(ax, G, training_steps, rule, training_job, weight_type):
 
     x =list(range(training_steps+1))
+    
+    dictionary = par.weight_styles[f'weight_{rule}']
 
-    if weight_type=='rho':
-        color_map = colormaps.rdpu
-        number_weights = G.number_of_nodes()
-        label = r'$\rho$[mM]'
-        label_legend = r'\rho'
-
-    if weight_type=='length':
-        color_map =load_cmap('green_material')
+    if dictionary['type_weights'] == 'edge':
         number_weights = G.number_of_edges()
-        label = r'$L$[$\mu$ m]'
-        label_legend = r'L'
-
-
-    if weight_type=='rbrt':
-        color_map = colormaps.greys
-        number_weights = G.number_of_edges()
-        label = r'$R$'
-        label_legend = r'R'
-
-
-    if weight_type=='pressure':
[…]

### 2025-01-27 codes/voltage_divider.py

@@ -5,6 +5,7 @@ import parameters as par
 import matplotlib.pyplot as plt
 import networkx as nx
 import time
+import matplotlib.gridspec as gridspec
 
 start = time.time()
 
@@ -42,21 +43,52 @@ G_pressure = G.copy(as_view=False)
 # --------- PLOT ERROR AND WEIGHTS WITH OTHER WEIGHTS ---------
 
 
-fig, ax = plt.subplots(figsize = par.figsize_1)
-plotting.plot_mse(ax, fig, f'allostery_length')
-plotting.plot_mse(ax, fig, f'allostery_rbrt')
-plotting.plot_mse(ax, fig, f'allostery_rho')
-plotting.plot_mse(ax, fig, f'allostery_pressure')
-ax.legend()
-fig.tight_layout()
-fig.savefig(f"../paper/plots/voltage_divider/mse_others.pdf")
-
-fig, ax = plt.subplots(1, 4, figsize = par.figsize_4horizontal)
-plotting.plot_weights(ax[0], G, training_steps=training_steps, training_job='allostery', weight_type='length')
-plotting.plot_weights(ax[1], G, training_steps=training_steps, training_job='allostery', weight_type='rbrt')
-plotting.plot_weights(ax[2], G, training_steps=training_steps, training_job='allostery', weight_type='rho')
-plotting.plot_weights(ax[2], G, training_steps=training_steps, training_job='allostery', weight_type='pressure')
+# fig, ax = plt.subplots(figsize = par.figsize_1)
+# plotting.plot_mse(ax, fig, f'allostery_length')
+# plotting.plot_mse(ax, fig, f'allostery_rbrt')
+# plotting.plot_mse(ax, fig, f'allostery_rho')
+# plotting.plot_mse(ax, fig, f'allostery_pressure')
 # ax.legend()
+# fig.tight_layout()
+# fig.savefig(f"../paper/plots/voltage_divider/mse_others.pdf")
+
+# fig, ax = plt.subplots(1, 4, figsize = par.figsize_4horizontal)
+# plotting.plot_weights(ax[0], G, training_steps=training_steps, training_job='allostery', weight_type='length')
+# plotting.plot_weights(ax[1], G, training_steps=training_steps, training_job='allostery', weight_type='rbrt')
[…]

### 2025-01-27 paper/paper.tex
created general network, about to start with the training.

@@
 We initialize the system with pressures $P_1 =  P_2 = 1 bar$ and ion concetration $\rho_1 = \rho_2 = 0.2 mM$ on each node, length $L_1 = L_2 = 10\mu m$ and base to tip radius ratio $R_1 = R_2 = 4$ on each edge.
-After choosing one of these four physical quantities as training parameter $\boldsymbol{w} = \brac{w_1, w_2}$, we implement the training as descibe in \cref{sec:training} that modifies it, while the other parameters are kept constant.
-In \cref{} we show that the cost function decreases of many order
+After choosing one of these four physical quantities as training parameter $\boldsymbol{w} = \brac{w_1, w_2}$, we implement the training as descibe in \cref{sec:training} that modifies them, while the other parameters are kept constant.
+In \cref{fig:mse_weights_vd} we show that the cost function decreases of many order
 
@@
     \centering
-    \includegraphics[width=0.6\columnwidth]{plots/voltage_divider/evolution_finalnw.pdf}
+    \includegraphics[width=\columnwidth]{plots/voltage_divider/mse_weights_vd.pdf}
     \caption{}
-    \label{fig:cont_disc_gen}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.6\columnwidth]{plots/voltage_divider/mse_others.pdf}
-    \caption{}
-    \label{fig:cont_disc_gen}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\columnwidth]{plots/voltage_divider/weights_others.pdf}
-    \caption{}
-    \label{fig:cont_disc_gen}
+    \label{fig:mse_weights_vd}
 \end{figure}

### 2025-01-27 codes/general_network.py

@@ -1,0 +1,34 @@
+import networks
+import training
+import plotting
+import parameters as par
+import matplotlib.pyplot as plt
+import networkx as nx
+import time
+import matplotlib.gridspec as gridspec
+
+start = time.time()
+
+# --------- INITIALIZE NETWORK ---------
+
+# -> DEFINE graph from networks module
+G = networks.random_graph(save_data=True) 
+
+# -> PLOT graph in /plots 
+fig, ax = plt.subplots()
+pos = plotting.plot_graph('random_graph')
+fig.tight_layout()
+fig.savefig(f"../plots/general_network/graph.pdf")
+
+# --------- TRAIN NETWORK WITH DIFFERENT WEIGHTS ---------
+
+training_steps = 10
+
+G_ml = G.copy(as_view=False)  
+training.train(G_ml, training_steps=training_steps, weight_type='length', delta_weight = 1e-3, learning_rate=3e-6)
+G_ml = G.copy(as_view=False)  
+# training.train(G_ml, training_steps=training_steps, weight_type='rbrt', delta_weight = 1e-3, learning_rate=1)
+G_ml = G.copy(as_view=False)  
+# training.train(G_ml, training_steps=training_steps, weight_type='rho', delta_weight = 1e-4, learning_rate=4e-4)
+G_pressure = G.copy(as_view=False)  
+# training.train(G_pressure, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=100)

### 2025-01-27 codes/networks.py

@@ -3,6 +3,7 @@ import parameters as par
 import sys
 sys.path.append(par.PACKAGE_PATH)
 import ahkab    
+import random
 
 # This module contains functions to:
 # 1 - Initialize graph parameters
@@ -77,6 +78,50 @@ def voltage_divider(save_data=False):
     # SAVE to data folder
     if save_data:
         nx.write_graphml(G, f"{par.DATA_PATH}voltage_divider.graphml")
+
+    return G
+
+# RANDOM NETWORK
+
+
+def random_graph(save_data=False, res_change=False):
+
+    # CREATE random graph with number_nodes conected by number_edges
+    number_nodes = 9
+    number_edges = 15
+    G = nx.gnm_random_graph(number_nodes, number_edges)
+
+    # DEFINE number sources and targets, then randomly select sources and targets nodes between number_nodes : sources containg source index and targets contains target indeces
+    number_sources = 3
+    number_targets = 2
+    sources = random.sample(G.nodes(), number_sources)
+    target_sampling_list = [x for x in G.nodes() if x not in sources]
+    targets = random.sample(target_sampling_list, number_targets)
+
+    volt_input = []
+    # Assign attributes nodes
+    volt_index=0
+    for node in range(len(G.nodes)):
+        if node in sources:
+            G.nodes[node]['type'] = 'source'
+            G.nodes[node]['color'] = par.color_dots[0]
+        elif node in targets:
+            G.nodes[node]['type'] = 'target'
+            G.nodes[node]['color'] = par.color_dots[1]
+        else:
+            G.nodes[node]['type'] = 'hidden'
+            G.nodes[node]['color'] = par.color_dots[2]
+
+    # INITIALIZE nodes and edges
+    voltage_input = [5, 1, 0] # node initialized here because different for differnent nw
+    voltage_desired = [3, 4]
+
+    initialize_nodes(G, voltage_input, voltage_desired)
+    initialize_edges(G)
+
+    if save_data:
+
+        nx.write_graphml(G, f"{par.DATA_PATH}random_graph.graphml")
 
     return G
 

### 2025-01-27 codes/voltage_divider.py

@@ -20,7 +20,7 @@ pos = plotting.plot_graph('voltage_divider')
 fig.tight_layout()
 fig.savefig(f"../plots/voltage_divider/graph.pdf")
 
-# --------- TRAIN NETWORK WITH PRESSURE ---------
+# --------- TRAIN NETWORK WITH DIFFERENT WEIGHTS ---------
 
 training_steps = 50
 
@@ -66,7 +66,6 @@ plotting.plot_weights(ax5, G, training_steps=training_steps, rule=f'allostery_pr
 
 # ax6 = fig.add_subplot(gs[0, 2:4])
 # plotting.plot_potential_drops_each_node(ax6, G_pressure)
-
 
 # Adjust layout and save the figure
 fig.tight_layout()

### 2025-01-28 paper/paper.tex
Started implementing regression training.

@@
-\documentclass[reprint,superscriptaddress,prb,floatfix,showkeys]{revtex4-2}
+\documentclass[reprint,superscriptaddress,prb,showkeys]{revtex4-2}
 \usepackage{empheq}
@@
 These networks typically operate in two phases: inference and backpropagation.
-The energy requirements of ANNs has grown significantly, negatively impacting the efficiency and scalability of ANNs \cite{energy_cost}.
+The energy requirements of ANNs has grown significantly, negatively impacting the efficiency and scalability of ANNs\cite{energy_cost}.
 
@@
 While the inference energy consumption has been addressed by hardware accelerators, the backpropagation still remains a problem.
-As an alternative to ANN performed strictly in-silico, physical neural networks (PNN) have been introduced, where physical processes rather than mathematical operations are trained \cite{}.
+As an alternative to ANN performed strictly in-silico, physical neural networks (PNN) have been introduced, where physical processes rather than mathematical operations are trained\cite{}.
 In fact, physical processes are often faster and consume less energy than their digital counterpart.
@@
 At the far side of the memristor, an electrical potential and pressure drop are applied.
-Overall, this results in a chemical, electrical and mechanical sensistive system.}
-    \label{fig:memristor_scheme}
+Overall, this results in a chemical, electrical and mechanical sensistive system.}\label{fig:memristor_scheme}
 \end{figure} 
@@
     \includegraphics[width=0.8\columnwidth]{plots/voltage_divider/vd_scheme.pdf}
-    \caption{}
-    \label{fig:vd_scheme}
+    \caption{}\label{fig:vd_scheme}
 \end{figure}
@@
     \includegraphics[width=\columnwidth]{plots/voltage_divider/mse_weights_vd.pdf}
-    \caption{}
-    \label{fig:mse_weights_vd}
+    \caption{}\label{fig:mse_weights_vd}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\columnwidth]{plots/voltage_divider/evolution_targets.pdf}
+    \caption{}\label{fig:evolution_targets}
+\end{figure}
+
+\cleardoublepage
+
+\subsection{Training a more general network}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\textwidth]{plots/general_network/mse_general.pdf}
+    \caption{Network to the right has inputs $[5,0]$ nad desired outputs $[3, 4]$, delta weights a third of their intial value and learning rates $1e^{-5}, 1e^{-4}, 1e^{2}$.
+The network to the right has $[5,1,0]$ and output $[3,4,2]$}\label{fig:mse_general}
 \end{figure}

### 2025-01-28 codes/general_network.py

@@ -19,24 +19,25 @@ G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
 fig, ax = plt.subplots()
 pos = plotting.plot_graph('random_graph')
 fig.tight_layout()
-fig.savefig(f"../plots/general_network/graph3.pdf")
+fig.savefig(f"../plots/general_network/graph.pdf")
 
 # --------- TRAIN NETWORK WITH DIFFERENT WEIGHTS ---------
 
 training_steps = 100
+training_type = 'allostery'
 weight_type_vec = ['length', 'rbrt', 'rho', 'pressure']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3]
 learning_rate_vec_random2 = [1e-5, 1, 1e-4, 1e2]
 learning_rate_vec_random3 = [5e-6, 1, 1e-3, 1e2]
 
 G_ml = G.copy(as_view=False)  
-# training.train(G_ml, training_steps=training_steps, weight_type='length', delta_weight = 1e-3, learning_rate=5e-6)
+training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='length', delta_weight = 1e-3, learning_rate=5e-6)
 G_ml = G.copy(as_view=False)  
-# training.train(G_ml, training_steps=training_steps, weight_type='rbrt', delta_weight = 1e-3, learning_rate=1)
+training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='rbrt', delta_weight = 1e-3, learning_rate=1)
 G_ml = G.copy(as_view=False)  
-# training.train(G_ml, training_steps=training_steps, weight_type='rho', delta_weight = 1e-4, learning_rate=1e-3)
+training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='rho', delta_weight = 1e-4, learning_rate=1e-3)
 G_pressure = G.copy(as_view=False)  
-# training.train(G_pressure, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=1e2)
+training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=1e2)
 
 # --------- PLOT ERROR AND WEIGHTS ---------
 
@@ -47,12 +48,7 @@ plotting.plot_mse(ax, fig, f'allostery_rbrt')
 plotting.plot_mse(ax, fig, f'allostery_rho')
[…]

### 2025-01-28 codes/linear_regression.py

@@ -1,0 +1,22 @@
+import networks
+import training
+import plotting
+import parameters as par
+import matplotlib.pyplot as plt
+import networkx as nx
+import time
+import matplotlib.gridspec as gridspec
+
+start = time.time()
+
+# --------- INITIALIZE NETWORK ---------
+
+# -> DEFINE graph from networks module
+# G = networks.random_graph(save_data=True) 
+G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
+
+# -> PLOT graph in /plots 
+fig, ax = plt.subplots()
+pos = plotting.plot_graph('random_graph')
+fig.tight_layout()
+fig.savefig(f"../plots/general_network/graph.pdf")

### 2025-01-28 codes/training.py

@@ -234,7 +234,7 @@ def  update_weights_parallel(G, base_error, weight_type, delta_weight, learning_
 
 # --------- TRAINING FUNCTIONS ---------
 
-def train(G, training_steps, weight_type, delta_weight, learning_rate):
+def train(G, training_type, training_steps, weight_type, delta_weight, learning_rate):
 
     # OPEN files to write results
     mse_file = open(f"{par.DATA_PATH}mse/mse_allostery_{weight_type}.txt", "w") #write error 
@@ -243,10 +243,8 @@ def train(G, training_steps, weight_type, delta_weight, learning_rate):
     else:
         potential_target_file = None     
 
-    path_patch = 'allostery' 
-
     # WRITE initial condition: intialized wieghts and intial error
-    write_weights_to_file(G, step=0, weight_type=weight_type, path_patch=path_patch)
+    write_weights_to_file(G, step=0, weight_type=weight_type, path_patch=training_type)
     
     error = cost_function(G, potential_target_file, update_initial_res=False)    #compute initial error
     error_normalization = error #define it as normalization error
@@ -262,7 +260,7 @@ def train(G, training_steps, weight_type, delta_weight, learning_rate):
 
         update_weights_parallel(G, error, weight_type, delta_weight, learning_rate)
             
-        write_weights_to_file(G, step+1, weight_type, path_patch)
+        write_weights_to_file(G, step+1, weight_type, training_type)
 
         error = cost_function(G, potential_target_file, update_initial_res=False)
 

### 2025-01-28 codes/voltage_divider.py

@@ -24,6 +24,7 @@ fig.savefig(f"../plots/voltage_divider/graph.pdf")
 # --------- TRAIN NETWORK WITH DIFFERENT WEIGHTS ---------
 
 training_steps = 50
+training_type = 'allostery'
 weight_type_vec = ['length', 'rbrt', 'rho', 'pressure']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3]
 learning_rate_vec = [3e-6, 1, 4e-4, 100]
@@ -31,7 +32,7 @@ learning_rate_vec = [3e-6, 1, 4e-4, 100]
 for weight_type_index in range(len(weight_type_vec)):
 
     G_ml = G.copy(as_view=False)  
-    training.train(G_ml, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index])
+    training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index])
 
 # --------- PLOT EVOLUTION OF TRAINED NW ---------
 
@@ -83,7 +84,7 @@ fig.savefig(f"../paper/plots/voltage_divider/evolution_finalnw.pdf")
 
 #     G_target.nodes[1]['desired'] = target_values[target_index]
 
-#     training.train(G_target, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=100)
+#     training.train(G_target, training_type=training_type, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=100)
 
 #     plotting.plot_weights(ax[1], G_target, training_steps=training_steps, rule=f'allostery_pressure', show_xlabel=True, starting_step=(target_index*training_steps))
 

### 2025-01-29 paper/paper.tex
Started adding linear regression.

@@
 
+We broaden the training capability of the network by including a linear regression task, where, in its simplest form, the network is trained to give potential output $V^{\text{out}}$ related to the input potential $V^{\text{in}}$ via a linear relationship
+\begin{equation}
+    V_{\text{out}} = \text{c} V_{\text{in}} + \text{b}.
+\label{eq:linear_relationship}
+\end{equation}
+Firstly, we generate a data set of input and output potential values, $\{ V^{in}_{i} \}_{i=1}^{}$ and $\{ V^{out}_{i} \}_{i}$ , that verify \cref{eq:linear_relationship}
+
 \section{Conclusion}

### 2025-01-29 codes/linear_regression.py

@@ -19,4 +19,33 @@ G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
 fig, ax = plt.subplots()
 pos = plotting.plot_graph('random_graph')
 fig.tight_layout()
-fig.savefig(f"../plots/general_network/graph.pdf")
+fig.savefig(f"../paper/plots/linear_regression/graph.pdf")
+
+
+training_steps = 10
+training_type = 'linear_regression'
+weight_type_vec = ['length', 'rbrt', 'rho', 'pressure']
+
+G_ml = G.copy(as_view=False)  
+# training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='length', delta_weight = 1e-3, learning_rate=5e-6)
+G_ml = G.copy(as_view=False)  
+# training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='rbrt', delta_weight = 1e-3, learning_rate=1)
+G_ml = G.copy(as_view=False)  
+# training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='rho', delta_weight = 1e-4, learning_rate=1e-3)
+G_pressure = G.copy(as_view=False)  
+training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=1e2)
+
+
+training.test_regression(G, step=2, weight_type='pressure')
+training.test_regression(G, step=5, weight_type='pressure')
+training.test_regression(G, step=10, weight_type='pressure')
+
+fig, ax = plt.subplots(1, 3, figsize=(15,5))
+plotting.plot_regression(ax[0], step=2)
+plotting.plot_regression(ax[1], step=5)
+plotting.plot_regression(ax[2], step=10)
+fig.tight_layout()
+fig.savefig(f"../paper/plots/linear_regression/snapshots.pdf")
+
+
+

### 2025-01-29 codes/networks.py

@@ -95,7 +95,7 @@ def random_graph(save_data=False, res_change=False):
 
     # DEFINE number sources and targets, then randomly select sources and targets nodes between number_nodes : sources containg source index and targets contains target indeces
     number_sources = 2
-    number_targets = 3
+    number_targets = 1
     sources = random.sample(G.nodes(), number_sources)
     target_sampling_list = [x for x in G.nodes() if x not in sources]
     targets = random.sample(target_sampling_list, number_targets)
@@ -126,6 +126,7 @@ def random_graph(save_data=False, res_change=False):
         nx.write_graphml(G, f"{par.DATA_PATH}random_graph.graphml")
 
     return G
+
 
 # 3 --------- GRAPH -> CIRCUIT ---------
 # Create a the class 'Circuit' used in the package ahkab from the desired graph.

### 2025-01-29 codes/plotting.py

@@ -6,6 +6,7 @@ import sys
 sys.path.append(par.PACKAGE_PATH)
 import ahkab  
 import networks
+import training
 
 from matplotlib.colors import to_rgb, to_hex
 def lighten_color(base_color, factor=0.5):
@@ -189,7 +190,36 @@ def plot_final_potential_vd(ax, target_values):
     # ax.set_xlabel(r'Time steps', fontsize = par.axis_fontsize)
     ax.tick_params(axis='both', labelsize=par.size_ticks)
 
+def plot_regression(ax, step):
+    
+    data = np.loadtxt(f"{par.DATA_PATH}regression_relations/relations_regression{step}.txt", unpack=True)
+    
+    x = data[0]
+    y1 = data[1]
+    
+    x_interval = np.linspace(np.min(x),np.max(x))
 
+    y1_desired = training.linear_function(x_interval)
+
+    
+    # if inp.weight_type=='rhob':
+    ax.plot(x_interval, y1_desired, **par.reg_desired_rhob, zorder=0)
+    # ax.plot(x_interval, y2_desired, **par.reg_desired2, zorder=0)
+    
+    ax.scatter(x, y1, **par.reg_output1)
+    # ax.scatter(x, y2, **par.reg_output2)
+    
+    # ax.legend()
+    ax.set_ylabel(r'$V_{out}$', fontsize = axis_fontsize)
+    ax.set_xlabel(r'$V_{in}$', fontsize = axis_fontsize)
+    # ax.set_title(f"Step {step}")
+    
+    # ax.set_xlim([-0.2, 5.2])
+    # ax.set_ylim([-0.2, 2])
+    ax.grid(ls=":")
+    ax.tick_params(axis='both', labelsize=size_ticks)
+    
+    return
 
 
     

### 2025-01-29 codes/training.py

@@ -49,6 +49,8 @@ def voltage_drop_element(circuit, result, element):
 
     return voltage_drop
 
+def linear_function(input):
+    return 0.3*input
 
 # --------- ALGORITHM FUNCTIONS ---------
 
@@ -75,7 +77,6 @@ def cost_function(G, write_potential_target_to_file=None, update_initial_res = F
     for node in G.nodes():
         target_index=0
         if G.nodes[node]['type']=='target':  
-            # print(G.nodes[node]['desired'])
             error += (G.nodes[node]['desired'] - result['tran'][f'VN{node}'][-1])**2
             target_index+=1
             
@@ -85,6 +86,16 @@ def cost_function(G, write_potential_target_to_file=None, update_initial_res = F
         write_potential_target_to_file.write(f"{result['tran'][f'VN{1}'][-1]}\n")
 
     return error    
+
+def cost_function_regression(G, dataset_input_voltage, dataset_output_voltage):
+
+    error = 0
+    for datastep in range(len(dataset_input_voltage)):
+        update_input_output_volt(G, dataset_input_voltage[datastep], dataset_output_voltage[datastep])
+        error += cost_function(G) 
+    error = error/len(dataset_input_voltage)
+
+    return error
 
 def update_weights(G,base_error, weight_type, delta_weight, learning_rate):
 
@@ -124,8 +135,6 @@ def update_weights(G,base_error, weight_type, delta_weight, learning_rate):
             else:
                 denominator = delta_weight
 
-            # print(new_error- base_error)
-
             gradients.append((new_error - base_error)/denominator)
             
         for index, edge in enumerate(G.edges()):    #Different loop cause you don't want to change edges yet
@@ -135,9 +144,18 @@ def update_weights(G,base_error, weight_type, delta_weight, learning_rate):
         
     return G
 
+# Returns two arrays with length 15: input voltage and corresponding desired output following the linear relationship
+def generate_dataset():
+
+    input_voltage = np.linspace(-5,5,10)
+
+    desired_output = linear_function(input_voltage)
+
+    return input_voltage, desired_output
+
 # FUNC----------- PARALLEL
 
-def compute_single_gradient_parallel_helper(G, weight_index, base_error, weight_type, delta_weight, stored_gradient, lock):
+def compute_single_gradient_parallel_helper(G, weight_index, training_type, base_error, weight_type, delta_weight, dataset_input_voltage, dataset_output_voltage,  stored_gradient, lock):
     
[…]

### 2025-02-10 paper/paper.tex
Starting branch to modify regression algorithm.

@@
 \end{equation}
-Firstly, we generate a data set of input and output potential values, $\{ V^{in}_{i} \}_{i=1}^{}$ and $\{ V^{out}_{i} \}_{i}$ , that verify \cref{eq:linear_relationship}
+Firstly, we generate a data set of $$ input and output potential values, $\{ V^{in}_{i} \}_{i=1}^{}$ and $\{ V^{out}_{i} \}_{i}$ , that verify \cref{eq:linear_relationship}
 

### 2025-02-10 codes/general_network.py

@@ -12,8 +12,8 @@ start = time.time()
 # --------- INITIALIZE NETWORK ---------
 
 # -> DEFINE graph from networks module
-G = networks.random_graph(save_data=True) 
-# G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
+# G = networks.random_graph(save_data=True) 
+G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
 
 # -> PLOT graph in /plots 
 fig, ax = plt.subplots()
@@ -23,7 +23,7 @@ fig.savefig(f"../plots/general_network/graph.pdf")
 
 # --------- TRAIN NETWORK WITH DIFFERENT WEIGHTS ---------
 
-training_steps = 100
+training_steps = 50
 training_type = 'allostery'
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure']
 delta_weight_vec = [1e-3, 1, 1e-4, 1e-3]
@@ -31,27 +31,45 @@ learning_rate_vec_random2 = [1e-5, 1e-6, 1e-4, 1e2]
 learning_rate_vec_random3 = [5e-6, 1e-6, 1e-3, 1e2]
 
 G_ml = G.copy(as_view=False)  
-training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='length', delta_weight = 1e-3, learning_rate=5e-6)
-G_ml = G.copy(as_view=False)  
+# training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='length', delta_weight = 1e-3, learning_rate=1e-5)
+# G_ml = G.copy(as_view=False)  
 # training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='radius_base', delta_weight = 1e-3, learning_rate=1)
-G_ml = G.copy(as_view=False)  
+# G_ml = G.copy(as_view=False)  
 # training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='rho', delta_weight = 1e-4, learning_rate=1e-3)
-G_pressure = G.copy(as_view=False)  
-# training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=1e2)
+G_ml = G.copy(as_view=False)  
+# training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=3e1)
[…]

### 2025-02-10 codes/linear_regression.py

@@ -12,8 +12,8 @@ start = time.time()
 # --------- INITIALIZE NETWORK ---------
 
 # -> DEFINE graph from networks module
-# G = networks.random_graph(save_data=True) 
-G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
+G = networks.random_graph(save_data=True) 
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
 
 # -> PLOT graph in /plots 
 fig, ax = plt.subplots()
@@ -21,24 +21,18 @@ pos = plotting.plot_graph('random_graph')
 fig.tight_layout()
 fig.savefig(f"../paper/plots/linear_regression/graph.pdf")
 
-
-training_steps = 10
+training_steps = 20
 training_type = 'linear_regression'
-weight_type_vec = ['length', 'rbrt', 'rho', 'pressure']
 
 G_ml = G.copy(as_view=False)  
 # training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='length', delta_weight = 1e-3, learning_rate=5e-6)
-G_ml = G.copy(as_view=False)  
-# training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='rbrt', delta_weight = 1e-3, learning_rate=1)
-G_ml = G.copy(as_view=False)  
-# training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='rho', delta_weight = 1e-4, learning_rate=1e-3)
 G_pressure = G.copy(as_view=False)  
-training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=1e2)
+training.train(G_pressure, training_type=training_type, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=2e3)
 
 
-training.test_regression(G, step=2, weight_type='pressure')
-training.test_regression(G, step=5, weight_type='pressure')
+training.test_regression(G, step=0, weight_type='pressure')
 training.test_regression(G, step=10, weight_type='pressure')
+training.test_regression(G, step=19, weight_type='pressure')
 
 fig, ax = plt.subplots(1, 3, figsize=(15,5))
 plotting.plot_regression(ax[0], step=2)

### 2025-02-10 codes/networks.py

@@ -89,8 +89,8 @@ def voltage_divider(save_data=False, voltage_desired = [4]):
 def random_graph(save_data=False, res_change=False):
 
     # CREATE random graph with number_nodes conected by number_edges
-    number_nodes = 10
-    number_edges = 15
+    number_nodes = 7
+    number_edges = 12
     G = nx.gnm_random_graph(number_nodes, number_edges)
 
     # DEFINE number sources and targets, then randomly select sources and targets nodes between number_nodes : sources containg source index and targets contains target indeces
@@ -115,8 +115,8 @@ def random_graph(save_data=False, res_change=False):
             G.nodes[node]['color'] = par.color_dots[2]
 
     # INITIALIZE nodes and edges
-    voltage_input = [5, 0] # node initialized here because different for differnent nw
-    voltage_desired = [3, 4, 2]
+    voltage_input = [5, 0, 0] # node initialized here because different for differnent nw
+    voltage_desired = [3, 4]
 
     initialize_nodes(G, voltage_input, voltage_desired)
     initialize_edges(G)

### 2025-02-10 codes/parameters.py

@@ -39,4 +39,8 @@ mse_styles = {
     'allostery_pressure': dict(marker = 'o', c = cmap.colors[3], lw=1, label = rf'$P$', ylabel_weights = r'$P$[bar]'),
 }
 
+reg_desired = dict(c = 'lightblue', lw=3, label = rf'$V_1^D$')
+reg_output = dict(c = 'mediumblue', marker='o', label = rf'$V_1$')
+
+
 

### 2025-02-10 codes/plotting.py

@@ -69,7 +69,7 @@ def plot_mse(ax, fig, rule, show_xlabel=True, saved_graph=None):
 
     style = par.mse_styles[f'{rule}']
     ax.plot(x, y, color = style['c'], marker = style['marker'], lw = style['lw'], label = style['label'])
-    ax.set_yscale('log')   
+    # ax.set_yscale('log')   
     
     # ax.legend(fontsize = par.legend_size)
     ax.set_ylabel(r'$C(w)$', fontsize = par.axis_fontsize)
@@ -195,7 +195,7 @@ def plot_final_potential_vd(ax, target_values):
 
 def plot_regression(ax, step):
     
-    data = np.loadtxt(f"{par.DATA_PATH}regression_relations/relations_regression{step}.txt", unpack=True)
+    data = np.loadtxt(f"{par.DATA_PATH}relations_regression/relations_regression{step}.txt", unpack=True)
     
     x = data[0]
     y1 = data[1]
@@ -206,21 +206,21 @@ def plot_regression(ax, step):
 
     
     # if inp.weight_type=='rhob':
-    ax.plot(x_interval, y1_desired, **par.reg_desired_rhob, zorder=0)
+    ax.plot(x_interval, y1_desired, **par.reg_desired, zorder=0)
     # ax.plot(x_interval, y2_desired, **par.reg_desired2, zorder=0)
     
-    ax.scatter(x, y1, **par.reg_output1)
+    ax.scatter(x, y1, **par.reg_output)
     # ax.scatter(x, y2, **par.reg_output2)
     
     # ax.legend()
-    ax.set_ylabel(r'$V_{out}$', fontsize = axis_fontsize)
-    ax.set_xlabel(r'$V_{in}$', fontsize = axis_fontsize)
+    ax.set_ylabel(r'$V_{out}$', fontsize = par.axis_fontsize)
+    ax.set_xlabel(r'$V_{in}$', fontsize = par.axis_fontsize)
     # ax.set_title(f"Step {step}")
     
     # ax.set_xlim([-0.2, 5.2])
     # ax.set_ylim([-0.2, 2])
     ax.grid(ls=":")
-    ax.tick_params(axis='both', labelsize=size_ticks)
+    ax.tick_params(axis='both', labelsize=par.size_ticks)
     
     return
 

### 2025-02-10 codes/training.py

@@ -147,7 +147,7 @@ def update_weights(G,base_error, weight_type, delta_weight, learning_rate):
 # Returns two arrays with length 15: input voltage and corresponding desired output following the linear relationship
 def generate_dataset():
 
-    input_voltage = np.linspace(-5,5,10)
+    input_voltage = np.linspace(0.1,5,18)
 
     desired_output = linear_function(input_voltage)
 
@@ -276,7 +276,6 @@ def update_input_output_volt(G, input_voltage, desired_voltage):
 
 def train(G, training_type, training_steps, weight_type, delta_weight, learning_rate):
 
-
     # OPEN files to write results
     mse_file = open(f"{par.DATA_PATH}mse/mse_allostery_{weight_type}.txt", "w") #write error 
     if G.name == 'voltage_divider': 
@@ -300,7 +299,8 @@ def train(G, training_type, training_steps, weight_type, delta_weight, learning_
 
     error_normalization = error #define it as normalization error
 
-    mse_file.write(f"{error/error_normalization}\n")
+    # mse_file.write(f"{error/error_normalization}\n")
+    mse_file.write(f"{error}\n")
 
     print('Step:', 0, error)
     
@@ -321,6 +321,8 @@ def train(G, training_type, training_steps, weight_type, delta_weight, learning_
 
         print('Step:', step+1, error)
         mse_file.write(f"{error/error_normalization}\n")
+        mse_file.write(f"{error}\n")
+
 
     mse_file.close()
     if G.name == 'voltage_divider':

### 2025-02-10 codes/voltage_divider.py

@@ -26,54 +26,52 @@ fig.savefig(f"../plots/voltage_divider/graph.pdf")
 training_steps = 50
 training_type = 'allostery'
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure']
-# weight_type_vec = ['radius_base']
 delta_weight_vec = [1e-3, 1, 1e-4, 1e-3]
-# delta_weight_vec = [1]
 learning_rate_vec = [3e-6, 3e-6, 4e-4, 100]
-# learning_rate_vec = [2e-6]
 
-for weight_type_index in range(len(weight_type_vec)):
+# for weight_type_index in range(len(weight_type_vec)):
+for weight_type_index in range(1):
 
     G_ml = G.copy(as_view=False)  
-    # training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index])
+    training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index])
 
 # --------- PLOT EVOLUTION OF TRAINED NW ---------
 
-fig, ax = plt.subplots(figsize = par.figsize_1)
-plotting.plot_potential_each_node(ax, G_ml)
-fig.tight_layout()
-fig.savefig(f"../paper/plots/voltage_divider/evolution_finalnw.pdf")
+# fig, ax = plt.subplots(figsize = par.figsize_1)
+# plotting.plot_potential_each_node(ax, G_ml)
+# fig.tight_layout()
+# fig.savefig(f"../paper/plots/voltage_divider/evolution_finalnw.pdf")
 
 # --------- PLOT ERROR AND WEIGHTS WITH OTHER WEIGHTS ---------
 
-fig = plt.figure(figsize=(12, 8))
-gs = gridspec.GridSpec(2, 3, height_ratios=[1, 1])
+# fig = plt.figure(figsize=(12, 8))
+# gs = gridspec.GridSpec(2, 3, height_ratios=[1, 1])
 
-ax1 = fig.add_subplot(gs[0, 0:2]) 
-plotting.plot_mse(ax1, fig, f'allostery_pressure', show_xlabel = False)
[…]

### 2025-03-04 paper/paper.tex
Woeking on pressure and rho.

--- 2025-01-29 paper/paper.tex
@@
 However, we consider only the pressure and potential contributions to the total fluid flow, $Q = Q_P + Q_V$, assuming the diffusive flow to be negligible.
-The resulting fluid flow generates non-trivial ion concentration profiles which, in turn, directly infulences the channel's conductance $g$.
+The resulting fluid flow generates non-trivial ion concentration profiles which, in turn, directly infulence the channel's conductance $g$.
 %It has already been shown that, for $\Delta P = 0$, the channel shows current rectification, thus working as a diode \cite{}, due to concentration polarization.
 
-In the steady-state, the channel is exposed to constant chemical, pressure and electrical signal, the corresponding conductance $g_{\infty}\brac{\boldsymbol{\Delta}}$ depends on the three stimuli $\boldsymbol{\Delta}= (\boldsymbol{\Delta})$ and is determined by the ion concentration profiles according to
+In the steady-state, the channel is exposed to constant chemical, pressure and electrical signal, the corresponding conductance $g_{\infty}\brac{\boldsymbol{\Delta}}$ depends on the three stimuli $\boldsymbol{\Delta}= (\Delta V, \Delta P, \Delta \rho)$ and is determined by the ion concentration profiles according to
 \[
@@
 \end{equation}
-with $\boldsymbol{\Delta}(t) = \brac{\Delta V\brac{t},\Delta P\brac{t}, \Delta \rho\brac{t}}$
+with $\boldsymbol{\Delta}(t) = \brac{\Delta V\brac{t},\Delta P\brac{t}, \Delta \rho\brac{t}}$.
 As in Ref.
@@
 Due to the fact that the conductance depends on the history of the signals applied, this system is called memristor.
-Aside from the direct dependence of the conductance on the external stimuli $\boldsymbol{\Delta}$, there is an implicit dependence on the geometricl properties such as lenght $L$ and radius ratio $R_b/R_t$ that we choose to consider.
+Aside from the direct dependence of the conductance on the external stimuli, there is an implicit dependence on the geometrical properties such as lenght $L$ and radius ratio $R_b/R_t$ that we choose to consider.
 
@@
 
-A voltage divider is an electrical circuit made of two resistances connected in series, that returns a fraction of the input voltage.
+A voltage divider is an electrical circuit made of three nodes connected in series by two resistances, that returns a fraction of the input voltage.
 Given the simplicity of its structure, we use it as an initial playground for the training algorithm described above.
-Specifically, we choose the lenghts of the memristor channels as the weights, to be trained such that giving $V_1 = 5V$ and $V_3 = 0V$ as inputs, we get $V_2 = 4V$ as output.
+Specifically, we replace the resistances with memristor channels, to be trained such that giving $V_1 = 5V$ and $V_3 = 0V$ as inputs, we get $V_2 = 4V$ as output.
 In \cref{fig:vd_scheme} a schematic of the memristor voltage divider is shown.
@@
 \end{equation}
-Firstly, we generate a data set of input and output potential values, $\{ V^{in}_{i} \}_{i=1}^{}$ and $\{ V^{out}_{i} \}_{i}$ , that verify \cref{eq:linear_relationship}
+% Firstly, we generate a data set of $$ input and output potential values, $\{ V^{in}_{i} \}_{i=1}^{}$ and $\{ V^{out}_{i} \}_{i}$ , that verify \cref{eq:linear_relationship}
 

### 2025-03-04 codes/linear_regression.py

@@ -14,27 +14,32 @@ start = time.time()
 
 # -> DEFINE graph from networks module
 # G = networks.three_inout(save_data=True) 
-# G = networks.random_graph(save_data=True) 
+G = networks.random_graph(save_data=True) 
 # G = networks.voltage_divider(save_data=True) 
-G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
 
 # a = networks.compute_regression_coefficients(G)
 # print('Coefficient a:', a)
 
-G.nodes['3']['type']  = 'source'
-G.nodes['3']['color'] = par.color_dots[0]
-G.nodes['3']['constant_source']  = True
-G.nodes['3']['voltage']  = 3
+# G.nodes['3']['type']  = 'source'
+# G.nodes['3']['color'] = par.color_dots[0]
+# G.nodes['3']['constant_source']  = True
+# G.nodes['3']['voltage']  = 1
 
-G.add_edge('6','2')
-G.add_edge('6','4')
-G.add_edge('4','5')
-G.add_edge('6','7')
-# G.remove_edge('3', '4')
-# G.remove_edge('2', '9')
+# G.add_edge('6','2')
+# G.add_edge('6','4')
+# G.add_edge('4','5')
+# G.add_edge('6','7')
+
+# G.remove_node('7')
+# G.remove_node('9')
+
+mapping = {old_label: new_label for new_label, old_label in enumerate(sorted(G.nodes()))}
+
+# Apply the relabeling
+G = nx.relabel_nodes(G, mapping)
+
 networks.initialize_edges(G)
-
-
 
 # for edge in G.edges():
 #     print(edge)
@@ -49,35 +54,42 @@ pos = plotting.plot_graph(G)
 fig.tight_layout()
 fig.savefig(f"../paper/plots/regression/graph.pdf", transparent=True)
 
-for edge in G.edges():
-    G.edges[edge]['resistance'] = 100
-
-training_steps = 100
+training_steps = 1
 training_type = 'regression'
 
-data = np.loadtxt(f"{par.DATA_PATH}weights/regression/length/length100.txt", unpack=True)
-weight_vec = data[1]
+# data = np.loadtxt(f"{par.DATA_PATH}weights/regression/rho/rho266.txt", unpack=True)
+# weight_vec = data[1]
+# print(weight_vec)
 
[…]

### 2025-03-04 codes/networks.py

@@ -12,7 +12,7 @@ import random
 
 # 1 --------- INITIALIZE GRAPH PARAMETERS ---------
 
-def initialize_nodes(G, voltage_input, voltage_desired):
+def initialize_nodes(G, voltage_input=None, voltage_desired=None):
 
     # Initialize every node with the same values of pressure = initial_pressure and rho = initial_rho
     initial_rho = 0.2

### 2025-03-04 codes/training.py

@@ -174,7 +174,7 @@ def update_weights(G, training_type, base_error, weight_type, delta_weight, lear
             if training_type == 'allostery':
                 error = cost_function(G_increment)  
             else:
-                error = cost_function_regression(G_increment, weight_type, dataset_input_voltage, dataset_output_voltage)
+                error = cost_function_regression(G_increment, weight_type, dataset_input_voltage, dataset_output_voltage, datastep, error_type='training')
 
             if weight_type == 'pressure':
                 denominator = delta_weight*1e5
@@ -182,6 +182,7 @@ def update_weights(G, training_type, base_error, weight_type, delta_weight, lear
                 denominator = delta_weight
                 
             gradients.append((error - base_error)/denominator)
+            print(node, G.nodes[node][f'{weight_type}'], error, base_error, (error - base_error), (error - base_error)/delta_weight)
 
         for node in G.nodes():
 
@@ -433,7 +434,7 @@ def  update_weights_parallel(G, training_type, base_error, weight_type, delta_we
         # batch_size = 1
         number_of_weights = G.number_of_nodes()
     else:
-        batch_size = int(G.number_of_edges()/4)
+        batch_size = int(G.number_of_edges()/2)
         # batch_size = G.number_of_edges()
         number_of_weights = G.number_of_edges()
 
@@ -536,9 +537,9 @@ def train(G, training_type, training_steps, weight_type, delta_weight, learning_
     # LOOP over training steps
     for step in range(training_steps): 
 
-        # update_weights(G, training_type, error, weight_type, delta_weight, learning_rate, dataset_input_voltage, dataset_output_voltage, step)
+        update_weights(G, training_type, error, weight_type, delta_weight, learning_rate, dataset_input_voltage, dataset_output_voltage, step)
 
-        update_weights_parallel(G, training_type, error, weight_type, delta_weight, learning_rate, dataset_input_voltage, dataset_output_voltage, step)
+        # update_weights_parallel(G, training_type, error, weight_type, delta_weight, learning_rate, dataset_input_voltage, dataset_output_voltage, step)
 
         # update_resistances(G, training_type, dataset_input_voltage, dataset_output_voltage)
             

### 2025-03-26 paper/paper.tex
Geometry to modify

@@
 
-We initialize the system with pressures $P_1 =  P_2 = 1 bar$ and ion concetration $\rho_1 = \rho_2 = 0.2 mM$ on each node, length $L_1 = L_2 = 10\mu m$ and base to tip radius ratio $R_1 = R_2 = 4$ on each edge.
-After choosing one of these four physical quantities as training parameter $\boldsymbol{w} = \brac{w_1, w_2}$, we implement the training as descibe in \cref{sec:training} that modifies them, while the other parameters are kept constant.
-In \cref{fig:mse_weights_vd} we show that the cost function decreases of many order
+We initialize the system with pressures $P_1 =  P_2 = 1 bar$ and ion concetration $\rho_1 = \rho_2 = 0.2 mM$ on each node, length $L_1 = L_2 = 10\mu m$ and base radius  $R_{b1} = R_{b2} = 200 nm$ on each edge.
+After choosing one of these four physical quantities as training parameter $\boldsymbol{w} = \brac{w_1, w_2}$, we implement the training as descibed in \cref{sec:training} that modifies them, while the other parameters are kept constant.
+In \cref{fig:mse_weights_vd} we show that the cost function normalized to its initial value decreases of many order of magnitude during the training for each of the choosen weight.
+The values of the choosen set of weights simultaneouly changes from the initial condition, as shown in Figures [], adjusting the behaviour of the network to the desired one.
+In fact, if the values of a choosen type of weights at the end of the training are imposed to the netowork together with the voltage imputs, the network will autonomously realx to a staedy state that coincides with the desired state.
+To clarify this point, the inset in Figure shows the relaxation of the voltage ivier
 

### 2025-03-26 codes/linear_regression.py

@@ -14,9 +14,11 @@ start = time.time()
 
 # -> DEFINE graph from networks module
 # G = networks.random_graph(save_data=True) 
-# G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
-G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
+G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_rigthbases.graphml')
+
+# G.add_
 
 # -> PLOT graph in /plots 
 fig, ax = plt.subplots()
@@ -24,18 +26,18 @@ pos = plotting.plot_graph(G)
 fig.tight_layout()
 fig.savefig(f"../paper/plots/regression/graph.pdf", transparent=True)
 
-# --------- TRAIN NETWORK ---------
 
-training_steps = 30    # choose
+# --------- TRAIN NETWORK ---------
+training_steps = 100    # choose
 training_type = 'regression'    # choose
 
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
-learning_rate_vec = [1e-6, 1e-5, 8e-3, 100, 100]
+learning_rate_vec = [1e-5, 1e-5, 8e-3, 100, 100]
 
 weight_type_index = 0   # choose
 
-training.train(G, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index])
+# training.train(G, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index])
 
 # --------- PLOT ERROR, WEIGHTS & RESISTANCE ---------
 
@@ -53,16 +55,16 @@ fig.savefig(f"../paper/plots/regression/mse.pdf", transparent=True)
 
 # --------- TEST REGRESSION AND PLOT RESULT ---------
 
-# training.test_regression(G, step=0, weight_type='length')
-# training.test_regression(G, step=int(training_steps/2), weight_type='length')
[…]

### 2025-03-26 codes/networks.py

@@ -114,8 +114,8 @@ def random_graph(save_data=False, res_change=False):
     # CREATE random graph with number_nodes conected by number_edges
     number_nodes = 7
     number_edges = 12
-    G = nx.gnm_random_graph(number_nodes, number_edges, directed=True)
-    # G = nx.connected_watts_strogatz_graph(8, 4, 0.3)
+    # G = nx.gnm_random_graph(number_nodes, number_edges, directed=True)
+    G = nx.connected_watts_strogatz_graph(8, 5, 0.3)
 
     # G = nx.house_graph()
     # G = nx.grid_2d_graph(3, 3)
@@ -222,10 +222,6 @@ def circuit_from_graph(G, type):
         # An edge = (u,v), the nodes are then called 'n u' and 'n v', u = edge[0], ...
 
         if type == 'memristors':
-            # print(f'pressure node {edge[0]}', G.nodes[edge[0]]['pressure'])
-            # print(f'pressure node {edge[1]}',G.nodes[edge[1]]['pressure'])
-            # print(f'pressure differece', G.nodes[edge[0]]['pressure']-G.nodes[edge[1]]['pressure'])
-            # print(index, edge[0], edge[1])
 
             circuit.add_mysistor(f'R{index+1}', f'n{edge[0]}', f'n{edge[1]}', value = G.edges[edge]["conductance"], rho_b=G.nodes[edge[0]]['rho'], length_channel = G.edges[edge]['length']*1e-6, radius_base = G.edges[edge]['radius_base']*1e-9, pressure=(G.nodes[edge[0]]['pressure']-G.nodes[edge[1]]['pressure'])*1e5, delta_rho = (G.nodes[edge[0]]['rho']-G.nodes[edge[1]]['rho']))
 

### 2025-03-26 codes/plotting.py

@@ -112,8 +112,8 @@ def plot_weights(ax, G, training_steps, rule, show_xlabel=True, starting_step = 
     
     style = par.weight_styles[f'{weight_type}']
     base_color = style['c']
-    palette = [lighten_color(base_color, factor = i * color_factor) for i in range(number_weights)]
-    # palette = plt.get_cmap('tab20')
+    # palette = [lighten_color(base_color, factor = i * color_factor) for i in range(number_weights)]
+    palette = plt.get_cmap('tab20')
       
     # GET data: data/training_job/weight_type contains files weight_type{step} with the list of weights per step
     for weight_indx in range(number_weights):
@@ -125,7 +125,8 @@ def plot_weights(ax, G, training_steps, rule, show_xlabel=True, starting_step = 
             weight.append(y[weight_indx])
 
         label_without_weightindex = style['label'][1:-1]
-        ax.plot(x, weight, color=palette[weight_indx], marker = style['marker'], lw = style['lw'], label = rf'${{{label_without_weightindex}}}_{{{weight_indx+1}}}$')
+        # ax.plot(x, weight, color=palette[weight_indx], marker = style['marker'], lw = style['lw'], label = rf'${{{label_without_weightindex}}}_{{{weight_indx+1}}}$')
+        ax.plot(x, weight, color=palette(weight_indx), marker = style['marker'], lw = style['lw'], label = rf'${{{label_without_weightindex}}}_{{{weight_indx+1}}}$')
         # ax.plot(x, weight, marker = style['marker'], lw = style['lw'], label = rf'${{{label_without_weightindex}}}_{{{weight_indx+1}}}$')
         
     label = style['ylabel_weights']

### 2025-03-26 codes/training.py

@@ -75,11 +75,6 @@ def cost_function(G, weight_type, update_initial_res = False, write_potential_ta
     resistance_vec = result[1]
     result = result[0]
 
-    # print(result['tran'].keys())
-    # print(result['tran']['VN0'][-1])
-    # print(result['tran']['VN1'][-1])
-    # print(result['tran']['VN2'][-1])
-
     # UPDATE the value of the initial conductance to the last in the tran simulation to speed up (in a voltage divider 5 steps speeds of 0.01s giving same results)
     if update_initial_res:
         for index, edge in enumerate(G.edges()):
@@ -97,6 +92,8 @@ def cost_function(G, weight_type, update_initial_res = False, write_potential_ta
                 error += (G.nodes[node]['desired'] - result['tran'][f'VN{node}'][-1])**2
 
             target_index+=1
+
+    # error = error/target_index
             
     # WRITE last element potential drop each edge (useful in the voltage divider case, otherwise too many)
     if G.name == 'voltage_divider' and write_potential_target_to_file is not None:
@@ -110,8 +107,6 @@ def cost_function(G, weight_type, update_initial_res = False, write_potential_ta
         for edge_index in range(len(G.edges())):
             write_memr_resistances.write(f"{resistance_vec[-1][edge_index]} \t")
         write_memr_resistances.write("\n")
-
-
 
     return error    
 
@@ -476,7 +471,6 @@ def train(G, training_type, training_steps, weight_type, delta_weight, learning_
     if training_type == 'regression':
         dataset_input_voltage, dataset_output_voltage = generate_dataset(0)
         testset_input_voltage, testset_output_voltage = generate_dataset(20, random = False)
-        # print(dataset_input_voltage, testset_input_voltage)
 
     # COMPUTE initial error
     if training_type == 'allostery':
@@ -536,28 +530,21 @@ def test_regression(G, step, weight_type):
             
     reg_file = open(f"{par.DATA_PATH}relations_regression/relations_regression{step}.txt", "w") 
 
-
     testset_input_voltage, testset_output_voltage = generate_dataset(20, random = False)
 
     error = 0
-    for datastep in range(len(testset_input_voltage[0])):
+    for datastep in range(len(testset_input_voltage)):
 
         update_input_output_volt(G, testset_input_voltage, testset_output_voltage, datastep)
 
-        if weight_type == 'resistance':
[…]

### 2025-03-27 codes/linear_regression.py
Added reshuffle function for memr direction

@@ -14,25 +14,44 @@ start = time.time()
 
 # -> DEFINE graph from networks module
 # G = networks.random_graph(save_data=True) 
-G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
+G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_rigthbases.graphml')
 
-G.nodes['0']['type']  = 'source'
-G.nodes['0']['color'] = par.color_dots[0]
-G.nodes['0']['constant_source']  = True
-G.nodes['0']['voltage']  = 1
+# G.nodes['0']['type']  = 'source'
+# G.nodes['0']['color'] = par.color_dots[0]
+# G.nodes['0']['constant_source']  = True
+# G.nodes['0']['voltage']  = 1
 
 # G = nx.DiGraph(Gdata)
 
-G.add_edge('1','5')
-G.add_edge('1','6')
-G.add_edge('0','4')
-G.add_edge('2','5')
-G.remove_edge('4', '2')
-G.remove_edge('5', '7')
-G.remove_edge('7', '6')
-G.remove_edge('0', '2')
+# G.add_edge('1','7')
+# G.add_edge('5','6')
+# G.add_edge('6','4')
+# G.add_edge('3','5')
+# G.remove_edge('4', '2')
+# G.remove_edge('5', '7')
+# G.remove_edge('7', '6')
+# G.remove_edge('0', '2')
+# networks.initialize_edges(G)
+
+# G = networks.to_directed_graph(G)
+# nx.write_graphml(G, f"{par.DATA_PATH}random_graph_shuffled.graphml")
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_suffled.graphml')
+
+G.nodes['3']['type']  = 'source'
+G.nodes['3']['color'] = par.color_dots[0]
+G.nodes['3']['constant_source']  = True
+G.nodes['3']['voltage']  = 3
+
+G.add_edge('6','2')
+G.add_edge('6','4')
+G.add_edge('4','5')
+G.add_edge('6','7')
+
+# G.remove_edge('3', '4')
+# G.remove_edge('2', '9')
 networks.initialize_edges(G)
 
[…]

### 2025-03-27 codes/networks.py

@@ -13,7 +13,27 @@ import random
 
 # 1 --------- INITIALIZE GRAPH PARAMETERS ---------
 
-def initialize_nodes(G, voltage_input=None, voltage_desired=None):
+def initialize_nodes(G, sources, targets, voltage_input=None, voltage_desired=None):
+
+    # Assign attributes nodes
+    constantsource_index=0
+    for node in list(G.nodes()):
+        # print(node)
+        if node in sources:
+            G.nodes[node]['type'] = 'source'
+            G.nodes[node]['color'] = par.color_dots[0]
+            if constantsource_index < (len(sources)-1):
+                G.nodes[node]['constant_source'] = True
+                constantsource_index += 1
+            else:
+                G.nodes[node]['constant_source'] = False
+
+        elif node in targets:
+            G.nodes[node]['type'] = 'target'
+            G.nodes[node]['color'] = par.color_dots[1]
+        else:
+            G.nodes[node]['type'] = 'hidden'
+            G.nodes[node]['color'] = par.color_dots[2]
 
     # Initialize every node with the same values of pressure = initial_pressure and rho = initial_rho
     initial_rho = 0.2
@@ -113,65 +133,23 @@ def voltage_divider(save_data=False, voltage_desired = [4]):
 def random_graph(save_data=False, res_change=False):
 
     # CREATE random graph with number_nodes conected by number_edges
-    number_nodes = 7
+    number_nodes = 8
     number_edges = 12
-    # G = nx.gnm_random_graph(number_nodes, number_edges, directed=True)
-    G_structure = nx.connected_watts_strogatz_graph(8, 5, 0.3)
-    print(G_structure.edges())
-
-    G = nx.DiGraph()
-    for edge in G_structure.edges():
-        direction = random.random()
-        if direction>0.5:
-            G.add_edge(edge[0], edge[1])
-        else:
-            G.add_edge(edge[1], edge[0])
-    for node in G_structure.nodes():
-        G.add_node(node)
-            
-
-    # G = nx.house_graph()
-    # G = nx.grid_2d_graph(3, 3)
-    # G = nx.convert_node_labels_to_integers(G)
-    # G = nx.complete_graph(5)
+    G = nx.gnm_random_graph(number_nodes, number_edges, directed=True)
+    # G = nx.connected_watts_strogatz_graph(8, 5, 0.3)
 
[…]

### 2025-03-27 codes/training.py

@@ -402,8 +402,8 @@ def  update_weights_parallel(G, training_type, base_error, weight_type, delta_we
         number_of_weights = G.number_of_edges()
 
     # Check if numb_nodes is a multiple of batch_size
-    if number_of_weights % batch_size != 0:
-        raise ValueError(f"number_of_weights ({number_of_weights}) must be a multiple of batch_size ({batch_size}).")
+    # if number_of_weights % batch_size != 0:
+    #     raise ValueError(f"number_of_weights ({number_of_weights}) must be a multiple of batch_size ({batch_size}).")
 
     # Initialize gradient vector
     init_gradient = np.zeros((number_of_weights), dtype = np.float64)  
@@ -415,12 +415,23 @@ def  update_weights_parallel(G, training_type, base_error, weight_type, delta_we
     # Create bridge to a nupy vector 
     stored_gradient = to_numpy_array(shared_gradient, init_gradient.shape)
 
+    core_multiple = int(number_of_weights/12)
+    if core_multiple<0:
+        batch_size = number_of_weights
+    else:
+        batch_size = 12
+
     lock = mp.Lock()
     # execute in batches
     for i in range(0, number_of_weights, batch_size):
+
+        endpoint_batch = i + batch_size
+        if endpoint_batch>number_of_weights:
+            endpoint_batch = number_of_weights
+
         # execute all tasks in a batch
         processes = [mp.Process(target = compute_single_gradient_parallel_helper, 
-                                args=(G, p, training_type, base_error, weight_type, delta_weight, dataset_input_voltage, dataset_output_voltage, step,  stored_gradient, lock)) for p in range(i, i + batch_size)]
+                                args=(G, p, training_type, base_error, weight_type, delta_weight, dataset_input_voltage, dataset_output_voltage, step,  stored_gradient, lock)) for p in range(i, endpoint_batch)]
 
         # start all processes
         for process in processes:

### 2025-03-28 paper/paper.tex
Added reshuffle function for memr direction
Pressure not training regression

@@
 The values of the choosen set of weights simultaneouly changes from the initial condition, as shown in Figures [], adjusting the behaviour of the network to the desired one.
-In fact, if the values of a choosen type of weights at the end of the training are imposed to the netowork together with the voltage imputs, the network will autonomously realx to a staedy state that coincides with the desired state.
-To clarify this point, the inset in Figure shows the relaxation of the voltage ivier
+In fact, if the values of a choosen type of weights at the end of the training are imposed to the netowork together with the voltage inputs, the network will autonomously realx to a staedy state that coincides with the desired state.
+To exemplify this point, the inset in Figure shows the physical relaxation of the voltage divider when the trained values of pressure, which correspond to the three values in the last training step, are imposed on the nodes together with the constant inputs voltages.
+The inset shows that the output voltage $V_2$ autonomously relaxes to the desired value of $V_D=3V$ in a time scale characteristic of the memristor.
 

### 2025-03-28 codes/general_network.py

@@ -14,7 +14,8 @@ start = time.time()
 # -> DEFINE graph from networks module
 # G = networks.random_graph(save_data=True) 
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
-G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
+G = nx.read_graphml(f'{par.DATA_PATH}random_graph_verynice.graphml')
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
 
 G = nx.reverse(G, copy=True)
 
@@ -22,6 +23,7 @@ G = nx.reverse(G, copy=True)
 # voltage_desired = [3, 4]
 
 # networks.initialize_nodes(G, voltage_input, voltage_desired)
+networks.initialize_edges(G)
 
 # -> PLOT graph in /plots 
 fig, ax = plt.subplots()
@@ -39,14 +41,14 @@ learning_rate_vec_random2 = [1e-5, 1e-6, 1e-4, 1e2]
 learning_rate_vec_random3 = [5e-6, 1e-6, 1e-3, 1e2]
 
 # G_ml = G.copy(as_view=False)  
-training.train(G, training_type=training_type, training_steps=training_steps, weight_type='length', delta_weight = 1e-3, learning_rate=1e-5)
+# training.train(G, training_type=training_type, training_steps=training_steps, weight_type='length', delta_weight = 1e-3, learning_rate=1e-5)
 # G_ml = G.copy(as_view=False)  
 # training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='radius_base', delta_weight = 1e-3, learning_rate=1e-6)
 # G_ml = G.copy(as_vie
 # w=False)  
 # training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='rho', delta_weight = 1e-4, learning_rate=5e-3)
 # G_ml = G.copy(as_view=False)  
-# training.train(G, training_type=training_type, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=1e2)
+training.train(G, training_type=training_type, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=1e2)
 
 # --------- PLOT ERROR AND WEIGHTS ---------
 

### 2025-03-28 codes/linear_regression.py

@@ -15,21 +15,27 @@ start = time.time()
 # -> DEFINE graph from networks module
 # G = networks.random_graph(save_data=True) 
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
-G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
+G = nx.read_graphml(f'{par.DATA_PATH}random_graph_verynice.graphml')
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_rigthbases.graphml')
 
-G.nodes['3']['type']  = 'source'
-G.nodes['3']['color'] = par.color_dots[0]
-G.nodes['3']['constant_source']  = True
-G.nodes['3']['voltage']  = 3
+# G.nodes['3']['type']  = 'source'
+# G.nodes['3']['color'] = par.color_dots[0]
+# G.nodes['3']['constant_source']  = True
+# G.nodes['3']['voltage']  = 3
 
-G.add_edge('6','2')
-G.add_edge('6','4')
-G.add_edge('4','5')
-G.add_edge('6','7')
+# G.add_edge('6','2')
+
+# G.add_edge('6','4')
+# G.add_edge('4','5')
+# G.add_edge('6','7')
 
 networks.initialize_edges(G)
+# G = networks.to_directed_graph(G)
+# nx.write_graphml(G, f"{par.DATA_PATH}random_graph_shuffled.graphml")
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_shuffled.graphml')
+
 
 # -> PLOT graph in /plots 
 fig, ax = plt.subplots()
@@ -38,22 +44,23 @@ fig.tight_layout()
 fig.savefig(f"../paper/plots/regression/graph.pdf", transparent=True)
 
 # --------- TRAIN NETWORK ---------
-training_steps = 0    # choose
+training_steps = 100    # choose
 training_type = 'regression'    # choose
 
 
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
-learning_rate_vec = [1e-5, 1e-5, 8e-3, 100, 100]
[…]

### 2025-03-28 codes/networks.py

@@ -133,8 +133,8 @@ def voltage_divider(save_data=False, voltage_desired = [4]):
 def random_graph(save_data=False, res_change=False):
 
     # CREATE random graph with number_nodes conected by number_edges
-    number_nodes = 8
-    number_edges = 12
+    number_nodes = 14
+    number_edges = 22
     G = nx.gnm_random_graph(number_nodes, number_edges, directed=True)
     # G = nx.connected_watts_strogatz_graph(8, 5, 0.3)
 
@@ -230,7 +230,7 @@ def to_directed_graph(G_structure):
     voltage_desired = []
     for edge in G_structure.edges():
         direction = random.random()
-        if direction>0.5:
+        if direction>0.2:
             G.add_edge(edge[0], edge[1])
         else:
             G.add_edge(edge[1], edge[0])

### 2025-03-28 codes/training.py

@@ -55,7 +55,7 @@ def regression_function1(input1, input2):
 def regression_function2(input1, inpu2):
     return 0.25*input1 + 0.1*inpu2 
 def regression_function(input):
-    return 0.6*input 
+    return 0.2*input 
 
 # --------- ALGORITHM FUNCTIONS ---------
 

### 2025-03-28 paper/paper.tex
Trying different geometries but not working

@@
     \includegraphics[width=\columnwidth]{plots/voltage_divider/mse_weights_vd.pdf}
-    \caption{}\label{fig:mse_weights_vd}
+    \caption{(a) Behaviour of the cost function during the training of the voltage divider.
+Different colors indicate that the training is done with a specific choise of training weights, as indiacted in the legend.
+(b) Pressures imposed on the three nodes of the voltage divider during training.
+The inset shows the relaxation to the steady state of the output voltage $V_2$ to the desired value $V_D$ when the pressures imposed are the values obtained in the last training step, and the input nodes are stimulated with fixed voltage.
+(c) Ion concentration desnities imposed on the three nodes of the voltage divider during training.
+(d) Length of the memristors during training.
+(e) Base radius of the memristors during training.}\label{fig:mse_weights_vd}
 \end{figure}
+
+Twos
 

### 2025-03-28 codes/general_network.py

@@ -14,8 +14,8 @@ start = time.time()
 # -> DEFINE graph from networks module
 # G = networks.random_graph(save_data=True) 
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
-G = nx.read_graphml(f'{par.DATA_PATH}random_graph_verynice.graphml')
-# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_verynice.graphml')
+G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
 
 G = nx.reverse(G, copy=True)
 
@@ -48,7 +48,7 @@ learning_rate_vec_random3 = [5e-6, 1e-6, 1e-3, 1e2]
 # w=False)  
 # training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type='rho', delta_weight = 1e-4, learning_rate=5e-3)
 # G_ml = G.copy(as_view=False)  
-training.train(G, training_type=training_type, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=1e2)
+training.train(G, training_type=training_type, training_steps=training_steps, weight_type='pressure', delta_weight = 1e-3, learning_rate=5e2)
 
 # --------- PLOT ERROR AND WEIGHTS ---------
 

### 2025-03-28 codes/linear_regression.py

@@ -13,9 +13,9 @@ start = time.time()
 # --------- INITIALIZE NETWORK ---------
 
 # -> DEFINE graph from networks module
-# G = networks.random_graph(save_data=True) 
+G = networks.random_graph(save_data=True) 
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
-G = nx.read_graphml(f'{par.DATA_PATH}random_graph_verynice.graphml')
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_verynice.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_rigthbases.graphml')
@@ -26,14 +26,16 @@ G = nx.read_graphml(f'{par.DATA_PATH}random_graph_verynice.graphml')
 # G.nodes['3']['voltage']  = 3
 
 # G.add_edge('6','2')
-
 # G.add_edge('6','4')
 # G.add_edge('4','5')
-# G.add_edge('6','7')
+# G.add_edge('1','4')
 
-networks.initialize_edges(G)
+
+G = nx.reverse(G, copy=True)
 # G = networks.to_directed_graph(G)
-# nx.write_graphml(G, f"{par.DATA_PATH}random_graph_shuffled.graphml")
+
+# networks.initialize_edges(G)
+nx.write_graphml(G, f"{par.DATA_PATH}random_graph_shuffled.graphml")
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_shuffled.graphml')
 
 
@@ -44,15 +46,15 @@ fig.tight_layout()
 fig.savefig(f"../paper/plots/regression/graph.pdf", transparent=True)
 
 # --------- TRAIN NETWORK ---------
-training_steps = 100    # choose
+training_steps = 80    # choose
 training_type = 'regression'    # choose
 
 
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
-learning_rate_vec = [3e-5, 1e-5, 1e-2, 1e2, 100]
+learning_rate_vec = [1e-5, 1e-5, 1e-2, 3e2, 100]
 
-weight_type_index = 3   # choose
+weight_type_index = 0   # choose
 
[…]

### 2025-03-28 codes/networks.py

@@ -133,8 +133,8 @@ def voltage_divider(save_data=False, voltage_desired = [4]):
 def random_graph(save_data=False, res_change=False):
 
     # CREATE random graph with number_nodes conected by number_edges
-    number_nodes = 14
-    number_edges = 22
+    number_nodes = 10
+    number_edges = 21
     G = nx.gnm_random_graph(number_nodes, number_edges, directed=True)
     # G = nx.connected_watts_strogatz_graph(8, 5, 0.3)
 

### 2025-03-28 codes/training.py

@@ -510,7 +510,7 @@ def train(G, training_type, training_steps, weight_type, delta_weight, learning_
             # print(node, G.nodes[node]['constant_source'])
         if counter_inputs == 1:
             dataset_input_voltage, dataset_output_voltage = generate_dataset_single(0)
-            testset_input_voltage, testset_output_voltage = generate_dataset_single(20, random = False)
+            testset_input_voltage, testset_output_voltage = generate_dataset_single(5, random = False)
             # print(dataset_input_voltage)
         else:
             dataset_input_voltage, dataset_output_voltage = generate_dataset(training_steps)

### 2025-03-31 paper/paper.tex
Radius base1

@@
 
-\subsection{Training a Voltage Divider}
+\subsection{Training a Memristor Voltage Divider}
 
@@
 
-Twos
+In order to investigate the adaptability of the system, we tested it with a set of three consequent desired voltages $V_D=\{1V, 3V, 4V\}$.
+In \cref{fig:evolution_targets} we show how the output voltgage $V_2$ subsequently adapts to the desired voltages during the training of the pressures in the nodes, the evolution of which can be seen in \cref{fig:evolution_targets}.
+It is evident that the system can be retrained at any stage to a new desired objective making it reusable.
+Any other weight type can be chosen, depending on the necessity.
 
@@
     \includegraphics[width=0.8\columnwidth]{plots/voltage_divider/evolution_targets.pdf}
-    \caption{}\label{fig:evolution_targets}
+    \caption{(a) The trainiang of a memristor voltage divider to a set of desired voltage outputs $V_D = {1V, 3V, 4V}$, indicated by dashed light purple lines.
+The output voltage $V_2$, indicated by dark purple dots, adapts to the desired output during the training.
+The input voltages $V_1$ and $V_3$ are constant at $5V$ and $0V$ respectively.
+(b) The dots with different shades of gray show the values of pressures, chosen as weights, imposed on the three nodes during training.}\label{fig:evolution_targets}
 \end{figure}
 
-\cleardoublepage
+\subsection{Training a memristor network}
 
-\subsection{Training a more general network}
+To generalize the training objective to a more general objective, we consider memrisotr networks with bigger networks with different topologies.
+Physically, reaching a desired input-output voltage mapping in a general electric circuit can be useful to adress desired voltage outputs in specific points of the circuit for variuous electronic purpuses.
 

### 2025-03-31 codes/linear_regression.py

@@ -14,23 +14,25 @@ start = time.time()
 
 # -> DEFINE graph from networks module
 # G = networks.random_graph(save_data=True) 
-# G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
+G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_verynice.graphml')
-G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_rigthbases.graphml')
 
-G.nodes['3']['type']  = 'source'
-G.nodes['3']['color'] = par.color_dots[0]
-G.nodes['3']['constant_source']  = True
-G.nodes['3']['voltage']  = 3
+# G.nodes['3']['type']  = 'source'
+# G.nodes['3']['color'] = par.color_dots[0]
+# G.nodes['3']['constant_source']  = True
+# G.nodes['3']['voltage']  = 3
 
-G.add_edge('6','2')
-G.add_edge('6','4')
-G.add_edge('4','5')
-G.add_edge('6','7')
+# G.add_edge('6','2')
+# G.add_edge('6','4')
+# G.add_edge('4','5')
+# G.add_edge('6','7')
 
-networks.initialize_edges(G)
+# G.remove_edge('1','2')
+
+# networks.initialize_edges(G)
 
 # G = nx.reverse(G, copy=True)
 # G = networks.to_directed_graph(G)
@@ -39,6 +41,10 @@ networks.initialize_edges(G)
 # nx.write_graphml(G, f"{par.DATA_PATH}random_graph_shuffled.graphml")
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_shuffled.graphml')
 
+# data = np.loadtxt(f"{par.DATA_PATH}weights/regression/radius_base/radius_base70.txt", unpack=True)
+# data = data[1]
+# for edge_index, edge in enumerate(G.edges()):
+#     G.edges[edge]['radius_base'] = data[edge_index]
 
 # -> PLOT graph in /plots 
 fig, ax = plt.subplots()
@@ -47,7 +53,7 @@ fig.tight_layout()
[…]

### 2025-03-31 codes/networks.py

@@ -134,18 +134,18 @@ def random_graph(save_data=False, res_change=False):
 
     # CREATE random graph with number_nodes conected by number_edges
     number_nodes = 10
-    number_edges = 21
+    number_edges = 20
     G = nx.gnm_random_graph(number_nodes, number_edges, directed=True)
     # G = nx.connected_watts_strogatz_graph(8, 5, 0.3)
 
     # DEFINE number sources and targets, then randomly select sources and targets nodes between number_nodes : sources containg source index and targets contains target indeces
-    number_sources = 2
+    number_sources = 3
     number_targets = 1
     sources = random.sample(G.nodes(), number_sources)
     target_sampling_list = [x for x in G.nodes() if x not in sources]
     targets = random.sample(target_sampling_list, number_targets)
 
-    voltage_input = [0, 5, 2] # node initialized here because different for differnent nw
+    voltage_input = [0, 3, 2] # node initialized here because different for differnent nw
     voltage_desired = [3, 4]
 
     # INITIALIZE nodes and edges

### 2025-03-31 codes/training.py

@@ -56,6 +56,7 @@ def regression_function2(input1, inpu2):
     return 0.25*input1 + 0.1*inpu2 
 def regression_function(input):
     return 0.2*input + 0.3
+    # return np.sqrt(input) 
 
 # --------- ALGORITHM FUNCTIONS ---------
 

### 2025-04-01 paper/paper.tex
Now not working for length :/

@@
     \includegraphics[width=\textwidth]{plots/general_network/mse_general.pdf}
-    \caption{Network to the right has inputs $[5,0]$ nad desired outputs $[3, 4]$, delta weights a third of their intial value and learning rates $1e^{-5}, 1e^{-4}, 1e^{2}$.
+    \caption{Network to the right has inputs $[5,0]$ and desired outputs $[3, 4]$, delta weights a third of their intial value and learning rates $1e^{-5}, 1e^{-4}, 1e^{2}$.
 The network to the right has $[5,1,0]$ and output $[3,4,2]$}\label{fig:mse_general}
@@
 \begin{equation}
-    V_{\text{out}} = \text{c} V_{\text{in}} + \text{b}.
+    V_{\text{out}} = \text{a} V_{\text{in}} + \text{b}.
 \label{eq:linear_relationship}
 \end{equation}
-% Firstly, we generate a data set of $$ input and output potential values, $\{ V^{in}_{i} \}_{i=1}^{}$ and $\{ V^{out}_{i} \}_{i}$ , that verify \cref{eq:linear_relationship}
+We generate two sets of data, a training test $\{ V_{\text{in}}, V_{\text{out}} }_{i=1}^{}$
 

### 2025-04-01 codes/linear_regression.py

@@ -14,25 +14,25 @@ start = time.time()
 
 # -> DEFINE graph from networks module
 # G = networks.random_graph(save_data=True) 
-G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_verynice.graphml')
-# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
+G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_rigthbases.graphml')
 
-# G.nodes['3']['type']  = 'source'
-# G.nodes['3']['color'] = par.color_dots[0]
-# G.nodes['3']['constant_source']  = True
-# G.nodes['3']['voltage']  = 3
+G.nodes['3']['type']  = 'source'
+G.nodes['3']['color'] = par.color_dots[0]
+G.nodes['3']['constant_source']  = True
+G.nodes['3']['voltage']  = 3
 
-# G.add_edge('6','2')
-# G.add_edge('6','4')
-# G.add_edge('4','5')
-# G.add_edge('6','7')
+G.add_edge('6','2')
+G.add_edge('6','4')
+G.add_edge('4','5')
+G.add_edge('6','7')
 
 # G.remove_edge('1','2')
 
-# networks.initialize_edges(G)
+networks.initialize_edges(G)
 
 # G = nx.reverse(G, copy=True)
 # G = networks.to_directed_graph(G)
@@ -41,7 +41,7 @@ G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
 # nx.write_graphml(G, f"{par.DATA_PATH}random_graph_shuffled.graphml")
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_shuffled.graphml')
 
-# data = np.loadtxt(f"{par.DATA_PATH}weights/regression/radius_base/radius_base70.txt", unpack=True)
+# data = np.loadtxt(f"{par.DATA_PATH}weights/regression/radius_base/radius_base100.txt", unpack=True)
 # data = data[1]
 # for edge_index, edge in enumerate(G.edges()):
 #     G.edges[edge]['radius_base'] = data[edge_index]
[…]

### 2025-04-01 codes/networks.py

@@ -133,8 +133,8 @@ def voltage_divider(save_data=False, voltage_desired = [4]):
 def random_graph(save_data=False, res_change=False):
 
     # CREATE random graph with number_nodes conected by number_edges
-    number_nodes = 10
-    number_edges = 20
+    number_nodes = 8
+    number_edges = 16
     G = nx.gnm_random_graph(number_nodes, number_edges, directed=True)
     # G = nx.connected_watts_strogatz_graph(8, 5, 0.3)
 
@@ -145,7 +145,7 @@ def random_graph(save_data=False, res_change=False):
     target_sampling_list = [x for x in G.nodes() if x not in sources]
     targets = random.sample(target_sampling_list, number_targets)
 
-    voltage_input = [0, 3, 2] # node initialized here because different for differnent nw
+    voltage_input = [0, 2, 2] # node initialized here because different for differnent nw
     voltage_desired = [3, 4]
 
     # INITIALIZE nodes and edges

### 2025-04-01 codes/training.py

@@ -55,7 +55,7 @@ def regression_function1(input1, input2):
 def regression_function2(input1, inpu2):
     return 0.25*input1 + 0.1*inpu2 
 def regression_function(input):
-    return 0.2*input + 0.3
+    return 0.2*input + 0.5
     # return np.sqrt(input) 
 
 # --------- ALGORITHM FUNCTIONS ---------

### 2025-04-03 paper/paper.tex
Satrting making final graph

@@
 \end{equation}
-We generate two sets of data, a training test $\{ V_{\text{in}}, V_{\text{out}} }_{i=1}^{}$
+We generate two sets of data, a training test $\{ V_{\text{in}}, V_{\text{out}} \}_{i=1}^{T}$ and a test set $\{ V_{\text{in}}, V_{\text{out}} \}_{i=1}^{Te}$.
+To create the test set, a random number in the interval $[1, 4]V$ is created and fed to equation \cref{eq:linear_relationship}
 

### 2025-04-03 codes/linear_regression.py

@@ -12,6 +12,10 @@ start = time.time()
 
 # --------- INITIALIZE NETWORK ---------
 
+# Using graphs:
+# regression_working: wokring nw for length not directed with 3V extra source
+# regression_working_rho: wokring nw for length directed with 6V extra source, working for rho training
+
 # -> DEFINE graph from networks module
 # G = networks.random_graph(save_data=True) 
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
@@ -20,33 +24,17 @@ G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_rigthbases.graphml')
 
-G.nodes['3']['type']  = 'source'
-G.nodes['3']['color'] = par.color_dots[0]
-G.nodes['3']['constant_source']  = True
-G.nodes['3']['voltage']  = 6
-
-G.add_edge('6','2')
-G.add_edge('6','4')
-G.add_edge('4','5')
-G.add_edge('6','7')
-
-G = networks.to_directed_graph(G, shuffle=True)
-# G.remove_edge('4','7')
-# G.remove_edge('6','7')
-# G.remove_edge('3','9')
-# G.add_edge('7','4')
-# G.add_edge('7','6')
-# G.add_edge('9','3')
 
 
+G = nx.read_graphml(f'{par.DATA_PATH}regression_working.graphml')
 networks.initialize_edges(G)
+# G = networks.to_directed_graph(G, shuffle=False)
 
-# G = networks.to_directed_graph(G)
-# G = nx.reverse(G, copy=True)
 
-# networks.initialize_edges(G)
 # nx.write_graphml(G, f"{par.DATA_PATH}random_graph_shuffled.graphml")
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_shuffled.graphml')
+# G = nx.read_graphml(f'{par.DATA_PATH}regression_working_rho.graphml')
+G.nodes['3']['voltage']  = 6
 
 # data = np.loadtxt(f"{par.DATA_PATH}weights/regression/radius_base/radius_base100.txt", unpack=True)
 # data = data[1]
@@ -60,15 +48,15 @@ fig.tight_layout()
 fig.savefig(f"../paper/plots/regression/graph.pdf", transparent=True)
[…]

### 2025-04-03 codes/networks.py

@@ -243,7 +243,14 @@ def to_directed_graph(G_structure, shuffle = False):
 
     edges = [edge for edge in G_structure.edges()]
     if shuffle:
-        np.random.shuffle(edges)
+        for edge_index in range(len(edges)):
+            direction = random.random()
+            if direction>0.2:
+                edges[edge_index] = (edges[edge_index][0], edges[edge_index][1])
+            else:
+                # print('changing')
+                edges[edge_index] = (edges[edge_index][1], edges[edge_index][0])
+
     G.add_edges_from(edges)
 
     initialize_edges(G)

### 2025-04-03 codes/training.py

@@ -640,8 +640,7 @@ def test_regression(G, step, weight_type):
         testset_input_voltage, testset_output_voltage = generate_dataset_single(20, random = False)
     else:
         testset_input_voltage, testset_output_voltage = generate_dataset_single(20, random = False)
-
-
+        
     error = 0
     for datastep in range(len(testset_input_voltage[0])):
 

### 2025-04-03 paper/paper.tex
Increases test error points

--- 2025-04-01 paper/paper.tex
@@
 \end{equation}
-We generate two sets of data, a training test $\{ V_{\text{in}}, V_{\text{out}} }_{i=1}^{}$
+We generate two sets of data, a training test $ \{ V_{\text{in}}, V_{\text{out}} \}_{i=1}^{T}$ and a test set $\{ V_{\text{in}}, V_{\text{out}} \}_{i=1}^{Te}$.
+To create the test set, a random number in the interval $[1V, 4V]$ is created and fed to equation \cref{eq:linear_relationship}, giving a set of outputs that satifiy the desired relationship.
+At each step of the training algorithm above presented, a pair of input and output voltages is selected from the training set, and used
 

### 2025-04-03 codes/linear_regression.py

@@ -20,7 +20,7 @@ start = time.time()
 # G = networks.random_graph(save_data=True) 
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_verynice.graphml')
-G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_rigthbases.graphml')
 
@@ -34,7 +34,7 @@ networks.initialize_edges(G)
 # nx.write_graphml(G, f"{par.DATA_PATH}random_graph_shuffled.graphml")
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_shuffled.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}regression_working_rho.graphml')
-G.nodes['3']['voltage']  = 6
+G.nodes['3']['voltage']  = 3
 
 # data = np.loadtxt(f"{par.DATA_PATH}weights/regression/radius_base/radius_base100.txt", unpack=True)
 # data = data[1]
@@ -51,10 +51,12 @@ fig.savefig(f"../paper/plots/regression/graph.pdf", transparent=True)
 training_steps = 300    # choose
 training_type = 'regression'    # choose
 
+print(G.edges())
+print(G.nodes())
 
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
-learning_rate_vec = [1e-6, 1e-5, 1e-3, 3e2, 1e3]
+learning_rate_vec = [1e-5, 1e-5, 1e-3, 3e2, 1e3]
 
 weight_type_index = 0   # choose
 

### 2025-04-03 codes/training.py

@@ -513,7 +513,7 @@ def train(G, training_type, training_steps, weight_type, delta_weight, learning_
             # print(node, G.nodes[node]['constant_source'])
         if counter_inputs == 1:
             dataset_input_voltage, dataset_output_voltage = generate_dataset_single(0)
-            testset_input_voltage, testset_output_voltage = generate_dataset_single(5, random = False)
+            testset_input_voltage, testset_output_voltage = generate_dataset_single(20, random = False)
             # print(dataset_input_voltage)
         else:
             dataset_input_voltage, dataset_output_voltage = generate_dataset(training_steps)

### 2025-04-03 paper/paper.tex
Writing regression on paper

--- 2025-04-01 paper/paper.tex
@@
 \end{equation}
-We generate two sets of data, a training test $\{ V_{\text{in}}, V_{\text{out}} }_{i=1}^{}$
+We generate two sets of data, a training test $ \{ V_{\text{in}}, V_{\text{out}} \}_{i=1}^{T}$ and a test set $\{ V_{\text{in}}, V_{\text{out}} \}_{i=1}^{Te}$.
+To create the test set, a set random values belonging to the interval $[1V, 4V]$ is created and fed to equation \cref{eq:linear_relationship}, giving a set of outputs that satifiy the desired relationship.
+At each step of the training, a pair of input and output voltages is selected from the training set, and used as input voltage and desired output in the algorithm.
 

### 2025-04-03 codes/linear_regression.py

@@ -51,9 +51,6 @@ fig.savefig(f"../paper/plots/regression/graph.pdf", transparent=True)
 training_steps = 300    # choose
 training_type = 'regression'    # choose
 
-print(G.edges())
-print(G.nodes())
-
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
 learning_rate_vec = [1e-5, 1e-5, 1e-3, 3e2, 1e3]

### 2025-04-03 codes/check_random_graph.py
Added old network definintion

@@ -73,25 +73,25 @@ fig.savefig(f"../paper/plots/regression/graph.pdf", transparent=True)
 # G.nodes['7']['rho'] += 1
 # print(G.nodes['9']['rho'])
 
-output_voltage = result['tran']['VN5'][-1]
+# output_voltage = result['tran']['VN5'][-1]
 
-# Feedforward -> reach steady state and get ouputs
-circuit = networks.circuit_from_graph(G, type='memristors') 
-tran_analysis = ahkab.new_tran(tstart=0, tstop=tstop, tstep=1e-3, x0=None)
-result = ahkab.run(circuit, an_list=tran_analysis) 
-resistances_vec = result[1]
-# print(resistances_vec)
-result = result[0]
-print(result['tran'].keys())
-print(result['tran']['VN0'][-1])
-print(result['tran']['VN1'][-1])
-print(result['tran']['VN2'][-1])
-print(result['tran']['VN3'][-1])
-print(result['tran']['VN4'][-1])
-print(result['tran']['VN5'][-1])
-print(result['tran']['VN6'][-1])
-print(result['tran']['VN7'][-1])
-print(result['tran']['VN8'][-1])
+# # Feedforward -> reach steady state and get ouputs
+# circuit = networks.circuit_from_graph(G, type='memristors') 
+# tran_analysis = ahkab.new_tran(tstart=0, tstop=tstop, tstep=1e-3, x0=None)
+# result = ahkab.run(circuit, an_list=tran_analysis) 
+# resistances_vec = result[1]
+# # print(resistances_vec)
+# result = result[0]
+# print(result['tran'].keys())
+# print(result['tran']['VN0'][-1])
+# print(result['tran']['VN1'][-1])
+# print(result['tran']['VN2'][-1])
+# print(result['tran']['VN3'][-1])
+# print(result['tran']['VN4'][-1])
+# print(result['tran']['VN5'][-1])
+# print(result['tran']['VN6'][-1])
+# print(result['tran']['VN7'][-1])
+# print(result['tran']['VN8'][-1])
 
 
-print(output_voltage - result['tran']['VN5'][-1])
+# print(output_voltage - result['tran']['VN5'][-1])

### 2025-04-03 codes/linear_regression.py

@@ -20,21 +20,31 @@ start = time.time()
 # G = networks.random_graph(save_data=True) 
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_verynice.graphml')
-# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
+G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}random_rigthbases.graphml')
 
+G.nodes['3']['type']  = 'source'
+G.nodes['3']['color'] = par.color_dots[0]
+G.nodes['3']['constant_source']  = True
+G.nodes['3']['voltage']  = 3
 
+G.add_edge('6','2')
+G.add_edge('6','4')
+G.add_edge('4','5')
+G.add_edge('6','7')
 
-G = nx.read_graphml(f'{par.DATA_PATH}regression_working.graphml')
 networks.initialize_edges(G)
+
+# G = nx.read_graphml(f'{par.DATA_PATH}regression_working.graphml')
+# networks.initialize_edges(G)
 # G = networks.to_directed_graph(G, shuffle=False)
 
 
 # nx.write_graphml(G, f"{par.DATA_PATH}random_graph_shuffled.graphml")
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_shuffled.graphml')
 # G = nx.read_graphml(f'{par.DATA_PATH}regression_working_rho.graphml')
-G.nodes['3']['voltage']  = 3
+# G.nodes['3']['voltage']  = 3
 
 # data = np.loadtxt(f"{par.DATA_PATH}weights/regression/radius_base/radius_base100.txt", unpack=True)
 # data = data[1]

### 2025-04-06 paper/paper.tex
Added old network definintion
Found working rho graph, started writing automated code, changed mse plotting.

--- 2025-04-03 paper/paper.tex
@@
 
-Artificial neural networks (ANNs) have become central to many technological advancements, achieving remarkable success in tasks ranging from image recognition to natural language processing.
+Modern computing algortihms are able to efficiently perform complicated nuemrical and symbolic operations, but their sequential structure limits their performance on more perceptual tasks.
+Inspired by the architecture and the functioning of the human brain that performs tasks via distributed and parallel fashion, artificial neural network (ANN) algorithms outreached traditional computing achieving remarkable success in challenging tasks ranging from image recognition to natural language processing and became central to many technological advancements in the field of artificial intelligence.
+
+Recent advances in AI systems have been powered by the silicon-based computing power of the Graphics Processing Units (GPUs) and by an unprecedented abundance of data.
+With a clear trend of larger ANN models, their the energy requirements have grown significantly, negatively impacting their efficiency and scalability\cite{energy_cost_ml1, energy_cost_ml2}.
 These networks typically operate in two phases: inference and backpropagation.
-The energy requirements of ANNs has grown significantly, negatively impacting the efficiency and scalability of ANNs\cite{energy_cost}.
 
@@
 We generate two sets of data, a training test $ \{ V_{\text{in}}, V_{\text{out}} \}_{i=1}^{T}$ and a test set $\{ V_{\text{in}}, V_{\text{out}} \}_{i=1}^{Te}$.
-To create the test set, a random number in the interval $[1V, 4V]$ is created and fed to equation \cref{eq:linear_relationship}, giving a set of outputs that satifiy the desired relationship.
-At each step of the training algorithm above presented, a pair of input and output voltages is selected from the training set, and used
+To create the test set, a set of a number of training steps of random values is sampled from the interval $[1V, 4V]$ is created and fed to equation \cref{eq:linear_relationship}, giving a set of outputs that satifiy the desired relationship.
+With a similar approach, the test set is constituted by $20$ input points equally spaced in the sampling interval, and output voltages that satisfy \cref{eq:linear_relationship}.
+Notice that the two sets contain different elements.
 
+The training algorithm presented in \cref{sec:training} can be slightly adapted to function for this training objective.
+At each step of the training, a pair of input and output voltages is selected from the training set, and used as input voltage and desired output in the algorithm above.
+In order to evaluate how well the algorithm is performing, the testset is evaluated at every step of the training by computing the test cost function.
+If the trained weight set after certain training step is $\boldsymbol{w}$, we define this function as
+\[
+C_{t}\left( \boldsymbol{w} \right) = \sum_{j=1}^{Te}\brac{V_{out}\brac{\boldsymbol{w}} - V_j^D}^2,
+\]
+which considers the difference between the voltage measured in the output node when the impoing the $j-$th input voltage of the test set and the desired output of the same test point, for every point of the set.
+
+\cleardoublepage
 \section{Conclusion}

### 2025-04-06 codes/brute_force_exploration.py

@@ -1,0 +1,56 @@
+import networks
+import training
+import plotting
+import parameters as par
+import matplotlib.pyplot as plt
+import networkx as nx
+import time
+import matplotlib.gridspec as gridspec
+import numpy as np
+import sys
+
+start = time.time()
+
+new = int(sys.argv[1])
+graph_id = str(sys.argv[2])
+
+training_steps = 300   # choose
+training_type = 'regression'
+
+weight_type_vec = ['length', 'radius_base', 'rho', 'pressure']
+delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3]
+learning_rate_vec = [1e-6, 5e-6, 1e-3, 3e2]
+
+weight_type_index = 2   # choose
+
+
+#i = 29
+#graph_id = str(i).zfill(4)
+
+
+
+if new == 1:
+    print("New graph generated")
+    # -> DEFINE graph from networks module
+    G = networks.random_graph(number_nodes=8, number_edges=16, save_data=True) 
+else:
+    print(f"Reusing graph {graph_id}")
+    G = nx.read_graphml(f'{par.DATA_PATH_RAW}G{graph_id}.graphml')
+
+
+G_prior = nx.read_graphml(f'{par.DATA_PATH_RAW}G{graph_id}.graphml')
+def run_mutations(G_prior, graph_id, n_mut = 100):
+    for i in range(n_mut):
+        G_mutated = networks.to_directed_graph(G_prior, shuffle=True)
+        try:
+            for weight_index in range(len(weight_type_vec)):
+                training.train_buffer(G_mutated, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate= learning_rate_vec[weight_type_index])
+                
+        except:
+            print("Mutated graph not valid")
+            continue
+
+
+
+
+

### 2025-04-06 codes/linear_regression.py

@@ -12,44 +12,22 @@ start = time.time()
 
 # --------- INITIALIZE NETWORK ---------
 
+# -> DEFINE graph from networks module
+# G = networks.random_graph(save_data=True) 
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
+
 # Using graphs:
 # regression_working: wokring nw for length not directed with 3V extra source
 # regression_working_rho: wokring nw for length directed with 6V extra source, working for rho training
 
-# -> DEFINE graph from networks module
-# G = networks.random_graph(save_data=True) 
-# G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
-# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_verynice.graphml')
-G = nx.read_graphml(f'{par.DATA_PATH}random_graph_working.graphml')
-# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_small_work.graphml')
-# G = nx.read_graphml(f'{par.DATA_PATH}random_rigthbases.graphml')
+G = nx.read_graphml(f'{par.DATA_PATH}regression_working.graphml')
 
-G.nodes['3']['type']  = 'source'
-G.nodes['3']['color'] = par.color_dots[0]
-G.nodes['3']['constant_source']  = True
-G.nodes['3']['voltage']  = 3
-
-G.add_edge('6','2')
-G.add_edge('6','4')
-G.add_edge('4','5')
-G.add_edge('6','7')
-
-networks.initialize_edges(G)
-
-# G = nx.read_graphml(f'{par.DATA_PATH}regression_working.graphml')
-# networks.initialize_edges(G)
-# G = networks.to_directed_graph(G, shuffle=False)
-
-
+# G = networks.to_directed_graph(G, shuffle=True)
 # nx.write_graphml(G, f"{par.DATA_PATH}random_graph_shuffled.graphml")
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph_shuffled.graphml')
-# G = nx.read_graphml(f'{par.DATA_PATH}regression_working_rho.graphml')
-# G.nodes['3']['voltage']  = 3
 
-# data = np.loadtxt(f"{par.DATA_PATH}weights/regression/radius_base/radius_base100.txt", unpack=True)
-# data = data[1]
-# for edge_index, edge in enumerate(G.edges()):
-#     G.edges[edge]['radius_base'] = data[edge_index]
[…]

### 2025-04-06 codes/networks.py

@@ -131,13 +131,10 @@ def voltage_divider(save_data=False, voltage_desired = [4]):
 
 # RANDOM NETWORK
  
-def random_graph(save_data=False, res_change=False):
+def random_graph(number_nodes=8, number_edges=16, save_data=False, res_change=False):
 
     # CREATE random graph with number_nodes conected by number_edges
-    number_nodes = 8
-    number_edges = 16
     G = nx.gnm_random_graph(number_nodes, number_edges, directed=True)
-    # G = nx.connected_watts_strogatz_graph(8, 5, 0.3)
 
     # DEFINE number sources and targets, then randomly select sources and targets nodes between number_nodes : sources containg source index and targets contains target indeces
     number_sources = 3

### 2025-04-06 codes/parameters.py

@@ -1,6 +1,7 @@
 # --------- PATHS ---------
 
 DATA_PATH = '../data/'
+DATA_PATH_RAW = '../data/raw/'
 PLOT_PATH = '../plots/'
 PACKAGE_PATH = '/home/monicaconte/nica/phd/Projects/Efficient_ML_Memristor_Network/codes/ahkab'
 # PACKAGE_PATH = '/Users/monicaconte/PhD/Projects/Contrastive_Learning_Memristors/Learning_Neural_Networks_true/codes/ahkab'

### 2025-04-06 codes/plotting.py

@@ -64,16 +64,12 @@ def plot_graph(G, weight_type = None):
 def plot_mse(ax, fig, weight_type, show_xlabel=True, saved_graph=None):
     
     if saved_graph==None:
-        y = np.loadtxt(f"{par.DATA_PATH}mse/mse_{weight_type}.txt", unpack=True)
+        data = np.loadtxt(f"{par.DATA_PATH}mse/mse_{weight_type}.txt", unpack=True)
     else:
         y = np.loadtxt(f"{par.DATA_PATH}mse/{saved_graph}/mse_{weight_type}.txt", unpack=True)
 
-    x = range(0,len(y))
-
-    # text = rule.split('_')
-    # weight_type = text[1]
-    if weight_type == 'radius':
-        weight_type = 'radius_base'
+    x = data[0]
+    y = data[1]
 
     style = par.weight_styles[f'{weight_type}']
     ax.plot(x, y, color = style['c'], marker = style['marker'], lw = style['lw'], label = style['label'])
@@ -142,11 +138,17 @@ def plot_weights(ax, G, training_steps, rule, show_xlabel=True, starting_step = 
 
 def plot_memristor_resistances(ax, G):
 
-    ydata = np.loadtxt(f"{par.DATA_PATH}memristor_resistances.txt", unpack=True)
-    x = np.array(range(len(ydata[0])))
+    circuit = networks.circuit_from_graph(G, type='memristors') 
+    analysis = ahkab.new_tran(tstart=0, tstop=0.1, tstep=1e-3, x0=None)
+
+    # DEFINE a transient analysis (analysis of the circuit over time)
+    result = ahkab.run(circuit, an_list=analysis) #returns two arrays: resistance over time of the memristors, voltages over time in the nodes
+    resistances = result[0]
+    print(resistances)
+    x = np.array(range(len(resistances[0])))
 
     for edge_index in range(len(G.edges())):
-        y = ydata[edge_index]
+        y = [resistances[edge_index][time_index] for time_index in range(len(resistances))]
         ax.plot(x, y, **par.memr_resistances_style, label = rf'$R_{{{edge_index+1}}}$') 
     ax.legend()
 

### 2025-04-06 codes/training.py

@@ -3,6 +3,7 @@ import networks
 import multiprocessing as mp
 import numpy as np
 import sys
+import statistics
 sys.path.append(par.PACKAGE_PATH)
 import ahkab 
 
@@ -120,7 +121,6 @@ def update_input_output_volt(G, input_voltage, desired_voltage, datastep=None):
                 G.nodes[node]['voltage'] = input_voltage[input_index]
             else:
                 G.nodes[node]['voltage'] = input_voltage[input_index][datastep]
-                print("Input", input_voltage[input_index][datastep])
 
 
             # if datastep == 0:
@@ -137,7 +137,6 @@ def update_input_output_volt(G, input_voltage, desired_voltage, datastep=None):
                 G.nodes[node]['desired'] = desired_voltage[output_index]
             else:
                 G.nodes[node]['desired'] = desired_voltage[output_index][datastep]
-                print("Output", desired_voltage[output_index][datastep])
 
 
             # if datastep == 0:
@@ -157,7 +156,6 @@ def cost_function_regression(G, weight_type, dataset_input_voltage, dataset_outp
         for datastep in range(len(dataset_input_voltage[0])):
             update_input_output_volt(G, dataset_input_voltage, dataset_output_voltage, datastep)
             error += cost_function(G, weight_type) 
-            print(error)
         error = error/len(dataset_input_voltage[0])
 
     return error
@@ -515,12 +513,85 @@ def train(G, training_type, training_steps, weight_type, delta_weight, learning_
             # print(node, G.nodes[node]['constant_source'])
         if counter_inputs == 1:
             dataset_input_voltage, dataset_output_voltage = generate_dataset_single(0)
-            testset_input_voltage, testset_output_voltage = generate_dataset_single(20, random = False)
+            testset_input_voltage, testset_output_voltage = generate_dataset_single(5, random = False)
             # print(dataset_input_voltage)
         else:
             dataset_input_voltage, dataset_output_voltage = generate_dataset(training_steps)
 
-    print(testset_input_voltage, testset_output_voltage)
+    # COMPUTE initial error
+    if training_type == 'allostery':
+        error = cost_function(G, weight_type, potential_target_file, update_initial_res=False) 
+        print('Step:', 0, error)
+        error_normalization = error #define it as normalization error
+        mse_file.write(f"{0}\t{error/error_normalization}\n")
+
+    else:
[…]

### 2025-04-07 paper/paper.tex
First sketch of plot regression is ready

@@
 With a clear trend of larger ANN models, their the energy requirements have grown significantly, negatively impacting their efficiency and scalability\cite{energy_cost_ml1, energy_cost_ml2}.
-These networks typically operate in two phases: inference and backpropagation.
-
-% ## Physical Neural Networks ##
-% - what they are, what is the scope (physical instead of math training)
-% - advantages: faster, computations are less energy demanding.
-
-While the inference energy consumption has been addressed by hardware accelerators, the backpropagation still remains a problem.
-As an alternative to ANN performed strictly in-silico, physical neural networks (PNN) have been introduced, where physical processes rather than mathematical operations are trained\cite{}.
-In fact, physical processes are often faster and consume less energy than their digital counterpart.
-
-% ## PNN algorithms in literature ##
+With the rapid increase in computation requirements of AI training and the slower improvemnts in computing hardware traditionally predicted by Moore's Law, the necessity of new computing paradigms became more relevant.
+As an alternative to ANN performed strictly in-silico, physical neural networks (PNN) have been introduced, where physical processes rather than mathematical operations are trained\cite{trainingphysicalneuralnetworks}.
+Since physical processes can be faster and more energetically efficient than their digital representation, this direction constitutes a promosing research direction to address this issue.
 

### 2025-04-07 codes/brute_force_exploration.py

@@ -18,16 +18,9 @@ training_steps = 300   # choose
 training_type = 'regression'
 
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure']
+weight_symbol_vec = ['L', 'Rb', 'rho', 'P']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3]
 learning_rate_vec = [1e-6, 5e-6, 1e-3, 3e2]
-
-weight_type_index = 2   # choose
-
-
-#i = 29
-#graph_id = str(i).zfill(4)
-
-
 
 if new == 1:
     print("New graph generated")

### 2025-04-07 codes/linear_regression.py

@@ -10,6 +10,8 @@ import numpy as np
 
 start = time.time()
 
+graph_id = 'G00010002'
+
 # --------- INITIALIZE NETWORK ---------
 
 # -> DEFINE graph from networks module
@@ -20,64 +22,68 @@ start = time.time()
 # regression_working: wokring nw for length not directed with 3V extra source
 # regression_working_rho: wokring nw for length directed with 6V extra source, working for rho training
 
-G = nx.read_graphml(f'{par.DATA_PATH}regression_working.graphml')
+# G = nx.read_graphml(f'{par.DATA_PATH}regression_working.graphml')
 
-# G = networks.to_directed_graph(G, shuffle=True)
-# nx.write_graphml(G, f"{par.DATA_PATH}random_graph_shuffled.graphml")
-# G = nx.read_graphml(f'{par.DATA_PATH}random_graph_shuffled.graphml')
+DATA_PATH = f'{par.DATA_PATH}regression{graph_id}/'
+G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 
-# G = nx.read_graphml(f'{par.DATA_PATH}regression_working_rho.graphml')
-G.nodes['3']['voltage']  = 3
+# print(G.nodes['3']['voltage'])
+
+# G.nodes['3']['voltage'] = 3
+
+# --------- TRAIN NETWORK ---------
+training_steps = 400   # choose
+training_type = 'regression'    # choose
+
+weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
+delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
+learning_rate_vec = [1e-6, 2e-6, 1e-3, 1e2, 1e3]
+constant_source = [11, 6, 3, 3]
+
+weight_type_index = 1   # choose
+G.nodes['3']['voltage'] = constant_source[weight_type_index]
+
+training.train(G, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index], save_final_graph=True, write_weights=True)
+
+# --------- PLOT GRAPH ---------
 
 # -> PLOT graph in /plots 
 fig, ax = plt.subplots()
 pos = plotting.plot_graph(G)
 fig.tight_layout()
-fig.savefig(f"../paper/plots/regression/graph.pdf", transparent=True)
[…]

### 2025-04-07 codes/parameters.py

@@ -43,6 +43,14 @@ weight_styles = {
 
 memr_resistances_style = dict(marker = 'o', markersize=3, lw=1)
 
+regression_styles = {
+    'length': dict(marker = 'o', c = cmap.colors[0], lw=1, label = rf'$L$'),
+    'length_des': dict(c = 'lightpink', lw=4, label = rf'$V^D$'),
+    'rho': dict(marker = 'o', c = cmap.colors[1], lw=1, label = rf'$\rho$'),
+    'radius_base': dict(marker = 'o', c = cmap.colors[2], lw=1, label = rf'$R_b$'),
+    'pressure': dict(marker = 'o', c = cmap.colors[3], lw=1, label = rf'$P$')
+}
+
 reg_desired = dict(c = 'lightblue', lw=3, label = rf'$V_1^D$')
 reg_output = dict(c = 'mediumblue', marker='o', label = rf'$V_1$')
 

### 2025-04-07 codes/plotting.py

@@ -61,12 +61,9 @@ def plot_graph(G, weight_type = None):
 
     return  
 
-def plot_mse(ax, fig, weight_type, show_xlabel=True, saved_graph=None):
+def plot_mse(ax, fig, graph_id, training_type, weight_type, show_xlabel=True):
     
-    if saved_graph==None:
-        data = np.loadtxt(f"{par.DATA_PATH}mse/mse_{weight_type}.txt", unpack=True)
-    else:
-        y = np.loadtxt(f"{par.DATA_PATH}mse/{saved_graph}/mse_{weight_type}.txt", unpack=True)
+    data = np.loadtxt(f"{par.DATA_PATH}{training_type}{graph_id}/mse/mse_{weight_type}.txt", unpack=True)
 
     x = data[0]
     y = data[1]
@@ -84,15 +81,10 @@ def plot_mse(ax, fig, weight_type, show_xlabel=True, saved_graph=None):
 import colormaps
 from pypalettes import load_cmap
 
-def plot_weights(ax, G, training_steps, rule, show_xlabel=True, starting_step = 0):
+def plot_weights(ax, G, training_steps, training_type, weight_type, show_xlabel=True, starting_step = 0):
 
     x =list(range(starting_step, starting_step + training_steps+1))
     
-    text = rule.split('_')
-    training_job = text[0]
-    weight_type = text[1]
-    if weight_type == 'radius':
-        weight_type = 'radius_base'
     if weight_type == 'pressure' or weight_type == 'rho':
         number_weights = G.number_of_nodes()
     else:
@@ -116,7 +108,7 @@ def plot_weights(ax, G, training_steps, rule, show_xlabel=True, starting_step = 
 
         weight = []
         for step in range(training_steps+1):
-            data = np.loadtxt(f"{par.DATA_PATH}weights/{training_job}/{weight_type}/{weight_type}{step}.txt", unpack=True)
+            data = np.loadtxt(f"{par.DATA_PATH}{training_type}{G.graph['name']}/weights/{weight_type}/{weight_type}{step}.txt", unpack=True)
             y = data[1]
             weight.append(y[weight_indx])
 
@@ -217,32 +209,27 @@ def plot_final_potential_vd(ax, target_values):
     # ax.set_xlabel(r'Time steps', fontsize = par.axis_fontsize)
     ax.tick_params(axis='both', labelsize=par.size_ticks)
 
[…]

### 2025-04-07 codes/regression_plots_paper.py

@@ -1,0 +1,48 @@
+import parameters as par
+import networkx as nx
+import numpy as np
+import matplotlib.pyplot as plt
+import ahkab  
+import networks
+import training
+import plotting
+import matplotlib.gridspec as gridspec
+
+
+graph_id = 'G00010001'
+DATA_PATH = f'{par.DATA_PATH}regression{graph_id}/'
+G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
+training_steps = 400
+training_type = 'regression'
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+
+fig = plt.figure(figsize=(12, 8), constrained_layout=True)
+outer = gridspec.GridSpec(2, 1, height_ratios=[1, 1], figure=fig)
+
+# First row: 2 columns
+top = gridspec.GridSpecFromSubplotSpec(1, 2, subplot_spec=outer[0])
+
+ax2 = fig.add_subplot(top[0, 1])
+plotting.plot_mse(ax2, fig, graph_id, training_type, f'length')
+plotting.plot_mse(ax2, fig, graph_id, training_type, f'radius_base')
+plotting.plot_mse(ax2, fig, graph_id, training_type, f'rho')
+plotting.plot_mse(ax2, fig, graph_id, training_type, f'pressure')
+ax2.legend(fontsize = par.legend_size)
+
+bottom = gridspec.GridSpecFromSubplotSpec(1, 3, subplot_spec=outer[1])
+ax3 = fig.add_subplot(bottom[0, 0])
+plotting.plot_regression(ax3, graph_id, 'length', step=0)
+ax3.legend(fontsize = par.legend_size)
+
+ax4 = fig.add_subplot(bottom[0, 1])
+plotting.plot_regression(ax4, graph_id, 'length', 50)
+ax4.legend(fontsize = par.legend_size)
+
+ax5 = fig.add_subplot(bottom[0, 2])
+plotting.plot_regression(ax5, graph_id, 'length', step=training_steps)
+ax5.legend(fontsize = par.legend_size)
+
+
+# fig.tight_layout()
+fig.savefig(f"../paper/plots/regression/G00010001.pdf")

### 2025-04-07 codes/training.py

@@ -10,9 +10,9 @@ import ahkab
 
 # --------- WRITE RESULTS TO FILES ---------
 
-def write_weights_to_file(G, step, weight_type, path_patch):
+def write_weights_to_file(G, DATA_PATH, step, weight_type):
 
-    file = open(f"{par.DATA_PATH}weights/{path_patch}/{weight_type}/{weight_type}{step}.txt", "w")
+    file = open(f"{DATA_PATH}weights/{weight_type}/{weight_type}{step}.txt", "w")
     
     for index, edge in enumerate(G.edges()): 
         if weight_type=='length' or weight_type=='radius_base' or weight_type=='resistance':
@@ -492,17 +492,19 @@ def  update_weights_parallel(G, training_type, base_error, weight_type, delta_we
 
 # --------- TRAINING FUNCTIONS ---------
 
-def train(G, training_type, training_steps, weight_type, delta_weight, learning_rate, save_final_graph=False):
+def train(G, training_type, training_steps, weight_type, delta_weight, learning_rate, save_final_graph=False, write_weights = False, graph_id=None):
 
     # OPEN files to write results
-    mse_file = open(f"{par.DATA_PATH}mse/mse_{weight_type}.txt", "w") #write error 
+    DATA_PATH = f"{par.DATA_PATH}{training_type}{G.graph['name']}/"
+    mse_file = open(f"{DATA_PATH}mse/mse_{weight_type}.txt", "w") #write error 
     if G.name == 'voltage_divider': 
         potential_target_file = open(f"{par.DATA_PATH}potential_targets/potential_targets{G.nodes[1]['desired']}.txt", "w") #write potential target during training (for voltage divider)  
     else:
         potential_target_file = None     
 
-    # WRITE initial condition: intialized wieghts and intial error
-    write_weights_to_file(G, step=0, weight_type=weight_type, path_patch=training_type)
+    if write_weights:
+        # WRITE initial condition: intialized wieghts and intial error
+        write_weights_to_file(G, DATA_PATH, step=0, weight_type=weight_type)
 
     dataset_input_voltage=[]
     dataset_output_voltage=[]
@@ -533,10 +535,6 @@ def train(G, training_type, training_steps, weight_type, delta_weight, learning_
         error_normalization = test_error #define it as normalization error
         mse_file.write(f"{0}\t{test_error/error_normalization}\n")
 
-
-    # mse_file.write(f"{error}\n")
-
-    
     # LOOP over training steps
     for step in range(training_steps): 
 
[…]

### 2025-04-09 paper/paper.tex
Preparing graphs to show and proove ......
General graph found - working also for regression it seems.

@@
 Since physical processes can be faster and more energetically efficient than their digital representation, this direction constitutes a promosing research direction to address this issue.
+
+Applications of PNN have been explored in fields ranging from optics\cite{}, to electronics\cite{}
+and to fluidic and mecanical systems\cite{}, amongs others.
 
@@
 To generalize the training objective to a more general objective, we consider memrisotr networks with bigger networks with different topologies.
-Physically, reaching a desired input-output voltage mapping in a general electric circuit can be useful to adress desired voltage outputs in specific points of the circuit for variuous electronic purpuses.
+Reaching a desired input-output voltage mapping in a generic electric circuit can be useful to adress desired voltage outputs in specific points of the circuit for variuous electronic purpuses.
 

### 2025-04-09 codes/general_network.py

@@ -37,7 +37,7 @@ G = nx.read_graphml(f'{DATA_PATH}G00030001.graphml')
 G.remove_edge('2', '3')
 G.remove_edge('2', '6')
 G.add_edge('7', '2')
-G.add_edge('7', '6')
+G.add_edge('7', '0')
 networks.initialize_edges(G)
 nx.write_graphml(G, f'{DATA_PATH}{graph_id}.graphml')
 
@@ -57,7 +57,7 @@ weight_type_vec = ['length', 'radius_base', 'rho', 'pressure']
 delta_weight_vec = [1e-3, 1, 1e-4, 1e-3]
 learning_rate_vec = [5e-6, 5e-6, 1e-3, 1e2]
 
-for weight_type_index in [0,1,2]:
+for weight_type_index in [3]:
     
     G_train = G.copy(as_view=False)
 

### 2025-04-09 codes/linear_regression.py

@@ -10,7 +10,7 @@ import numpy as np
 
 start = time.time()
 
-graph_id = 'G00010002'
+graph_id = 'G00040001'
 
 # --------- INITIALIZE NETWORK ---------
 
@@ -26,10 +26,21 @@ graph_id = 'G00010002'
 
 DATA_PATH = f'{par.DATA_PATH}regression{graph_id}/'
 G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
+G.nodes['4']['type'] = 'hidden'
+G.nodes['4']['color'] = 'silver'
+G.graph['name'] = graph_id
+nx.write_graphml(G, f'{DATA_PATH}{graph_id}.graphml')
 
 # print(G.nodes['3']['voltage'])
 
 # G.nodes['3']['voltage'] = 3
+# --------- PLOT GRAPH ---------
+
+# -> PLOT graph in /plots 
+fig, ax = plt.subplots()
+pos = plotting.plot_graph(G)
+fig.tight_layout()
+fig.savefig(f"{DATA_PATH}graph.pdf", transparent=True)
 
 # --------- TRAIN NETWORK ---------
 training_steps = 400   # choose
@@ -37,25 +48,19 @@ training_type = 'regression'    # choose
 
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
-learning_rate_vec = [1e-6, 1e-6, 5e-4, 4e2, 1e3]
+learning_rate_vec = [1e-6, 1e-6, 5e-5, 10, 1e3]
 constant_source = [3, 3, 4, 3]
 
-weight_type_index = 3   # choose
+weight_type_index = 0   # choose
 
-for weight_type_index in [2]:
+for weight_type_index in [1,2,3]:
+    # print(f'{DATA_PATH}')
     
     G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
-    G.nodes['3']['voltage'] = constant_source[weight_type_index]
+    G.nodes['5']['voltage'] = constant_source[weight_type_index]
 
     training.train(G, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index], save_final_graph=True, write_weights=True)
 
[…]

### 2025-04-11 paper/paper.tex
Result regression for lemgth

@@
 
-Applications of PNN have been explored in fields ranging from optics\cite{}, to electronics\cite{}
-and to fluidic and mecanical systems\cite{}, amongs others.
+Applications of PNNs have been explored across diverse fields, including optics \cite{optics1}, electronics \cite{electronics1}, and fluidic and mechanical systems \cite{}, among others.
+Many existing training algorithms rely entirely on in silico methods, which often face challenges when transferring the learned model to real physical devices.
+To address this, hybrid training approaches have been proposed, where the inference phase is executed physically while the backward phase is computed numerically.
+Other methods, based on coupled learning, implement local learning rules at the level of each connection or edge.
+However, these approaches still face the need for two identical physical systems to apply different boundary conditions.
+In this work, we propose a novel algorithm in which both inference and backpropagation are carried out through physical processes, specifically leveraging the natural relaxation dynamics of the system in response to external stimuli and weight modifications.
 
-% ## Our networks and our algorithm ##
-
-Not only, but physical neural networks make the similarity with the human brain more evident, opening the doors to the development of an artificial brain.
-For this, we choose to work with networks whose constructing elements are memristors living in aqueous solution and that respond to electrical, chemical and mechanical stimuli at the same time.
-
-Fluidic channels are emerging as a promising technology in the field of neuromorphic computing due to their ability to emulate synaptic functions.
-These nanoscale devices can store information through conductance changes.
-Their unique properties make them suitable for implementing artificial neural networks and other types of electrical networks.
-
-In recent years, machine learning algorithms have increasingly been applied to memristor networks to train specific input-output relations.
-These algorithms typically modify the dynamics of the memristors to achieve desired computational tasks.
+A key advantage of PNNs is their ability to more closely emulate certain functional aspects of biological neural systems.
+One of the defining features of the brain is its capacity to process and integrate multiple types of stimuli—such as electrical, chemical, and mechanical inputs—simultaneously.
+This multimodal responsiveness is believed to contribute significantly to the brain’s efficiency and adaptability \cite{}.
+Inspired by this, we focus on neural networks constructed from memristive elements.
+Specifically, we utilize ionic microfluidic channels in aqueous solutions\cite{Rene_IonicNeuromorphic}, which exhibit the unique ability to respond concurrently to diverse physical stimuli.
+This characteristic is central to the operation of our proposed training algorithm.
 
@@
 
-The paper is roganized as follows.
+The paper is organized as follows.
 Section 2 reviews related work on memristor networks, machine learning algorithms, and physical learning methods.
@@
 
-To generalize the training objective to a more general objective, we consider memrisotr networks with bigger networks with different topologies.
+To generalize the training objective to a more general objective, we consider memrisotr network built from a bigger network geometry.
+\cref{fig:mse_general}(a) shows a three-input and two-output network, that we train to give $[3V, 4V]$ in the output nudes, when $[0V, 2V, 5V]$ are given as input.
 Reaching a desired input-output voltage mapping in a generic electric circuit can be useful to adress desired voltage outputs in specific points of the circuit for variuous electronic purpuses.
+[...]
 
@@
     \centering
-    \includegraphics[width=\textwidth]{plots/general_network/mse_general.pdf}
-    \caption{Network to the right has inputs $[5,0]$ and desired outputs $[3, 4]$, delta weights a third of their intial value and learning rates $1e^{-5}, 1e^{-4}, 1e^{2}$.
-The network to the right has $[5,1,0]$ and output $[3,4,2]$}\label{fig:mse_general}
+    \includegraphics[width=0.5\textwidth]{plots/general_network/mse_general.pdf}
+    \caption{(a) Generic network with $9$ nodes and $15$ edges with inputs $[V_{2}, V_{4}, V_{9}] = [0V, 2V, 5V]$ and desired outputs $[V_{5}^D, V_{7}^D] = [3V, 4V]$, delta weights a third of their intial value and learning rates $[0.001, 1, 0.0001, 0.001]$.
+(b) Cost funtion during training of generic graph for input-output mapping task.
+The different colors indicate different weight choise.}\label{fig:mse_general}
 \end{figure}
 
-\cleardoublepage
+The result of the training is presented in \cref{fig:mse_general}(b), which shows how the cost function responds to the wieght updates performed in the algorithm, for each of the four different weights.
+All of the possible different choices of weight result in a trained set that decreases the initial error of many orders of magnitudes.
+
+% \cleardoublepage
 \subsection{Linear Regression}
@@
 At each step of the training, a pair of input and output voltages is selected from the training set, and used as input voltage and desired output in the algorithm above.
-In order to evaluate how well the algorithm is performing, the testset is evaluated at every step of the training by computing the test cost function.
+In order to evaluate how well the algorithm is performing, the testset is evaluated by computing the test cost function.
 If the trained weight set after certain training step is $\boldsymbol{w}$, we define this function as

### 2025-04-11 codes/linear_regression.py

@@ -10,7 +10,7 @@ import numpy as np
 
 start = time.time()
 
-graph_id = 'G00010002'
+graph_id = 'G00010001'
 DATA_PATH = f'{par.DATA_PATH}regression{graph_id}/'
 
 # --------- INITIALIZE NETWORK ---------
@@ -42,24 +42,26 @@ fig.tight_layout()
 fig.savefig(f"{DATA_PATH}graph.pdf", transparent=True)
 
 # --------- TRAIN NETWORK ---------
-training_steps = 300   # choose
+training_steps = 400   # choose
 training_type = 'regression'    # choose
 
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
-learning_rate_vec = [6e-7, 2e-6, 1e-4, 60, 1e3]
-constant_source = [11, 8, 8, 8]
+learning_rate_vec = [5e-7, 1e-6, 7e-4, 1e2, 1e3]
+constant_source = [11, 3, 3, 3]
 
 weight_type_index = 0   # choose
 
-for weight_type_index in [0,1,2,3]:
+for weight_type_index in [0]:
     # print(f'{DATA_PATH}')
     
     # G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
-    G = nx.read_graphml(f'{DATA_PATH}G00010002.graphml')
-    G.nodes['5']['voltage'] = constant_source[weight_type_index]
+    # G = nx.read_graphml(f'{DATA_PATH}G00010002.graphml')
+    G = nx.read_graphml(f'{DATA_PATH}G00010001.graphml')
+    # G = nx.read_graphml(f'{DATA_PATH}G00010003.graphml')
+    G.nodes['3']['voltage'] = constant_source[weight_type_index]
 
-    training.train(G, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index], save_final_graph=True, write_weights=True)
+    # training.train(G, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index], save_final_graph=True, write_weights=True)
 
 
 

### 2025-04-11 codes/plotting.py

@@ -219,6 +219,7 @@ def plot_regression(ax, graph_id, weight_type, step):
     
     x = data[0]
     y1 = data[1]
+    print(y1)
     
     x_interval = np.linspace(np.min(x),np.max(x))
     y1_desired = training.regression_function(x_interval)

### 2025-04-11 codes/regression_plots_paper.py

@@ -9,7 +9,7 @@ import plotting
 import matplotlib.gridspec as gridspec
 
 
-graph_id = 'G00010002'
+graph_id = 'G00010001'
 DATA_PATH = f'{par.DATA_PATH}regression{graph_id}/'
 G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 training_steps = 400
@@ -32,15 +32,15 @@ ax2.legend(fontsize = par.legend_size)
 
 bottom = gridspec.GridSpecFromSubplotSpec(1, 3, subplot_spec=outer[1])
 ax3 = fig.add_subplot(bottom[0, 0])
-plotting.plot_regression(ax3, graph_id, 'rho', step=0)
+plotting.plot_regression(ax3, graph_id, 'length', step=0)
 ax3.legend(fontsize = par.legend_size)
 
 ax4 = fig.add_subplot(bottom[0, 1])
-plotting.plot_regression(ax4, graph_id, 'rho', int(training_steps/2))
+plotting.plot_regression(ax4, graph_id, 'length', int(50))
 ax4.legend(fontsize = par.legend_size)
 
 ax5 = fig.add_subplot(bottom[0, 2])
-plotting.plot_regression(ax5, graph_id, 'rho', step=training_steps)
+plotting.plot_regression(ax5, graph_id, 'length', step=400)
 ax5.legend(fontsize = par.legend_size)
 
 

### 2025-04-11 codes/training.py

@@ -556,7 +556,7 @@ def train(G, training_type, training_steps, weight_type, delta_weight, learning_
         else:
             dataset_input_voltage, dataset_output_voltage = generate_dataset_single(0)
             error = cost_function_regression(G, weight_type, dataset_input_voltage, dataset_output_voltage, step +1, error_type='training')
-            if step % 15 == 0:
+            if step % 10 == 0:
                 test_error = cost_function_regression(G, weight_type, testset_input_voltage, testset_output_voltage, 0, error_type='test')
                 print('Step:', step+1, test_error)
                 mse_file.write(f"{step+1}\t{test_error/error_normalization}\n")

### 2025-04-11 paper/paper.tex
Version paper bf col

@@
 
+Since the task is more demanding than a single input-output mapping, we generate a bigger network, with more degrees of freedom.
+\cref{fig:lin_regr1}(a) shows the selected graph for the regression task, it has $20$ edges and $10$ nodes, three of which are inputs and one is an output.
+Of three input nodes, tone is set to ground $V_0 = 0$, and one to a constant value to enable the training of a linear function with an off-set.
+For the training objective, we decide to train the network to fit the line $V_{out} = 0.2 V_{in} + 0.3$ in the votage range [1V,5V].
+
+The performance of the algorithm for this task is shown in \cref{fig:lin_regr2}(b), where the learning rates for the different weights has been fine tuned in such a way that the algorithm does not overshoot, spoling the training, but it is not too slow either.
+From the behaviour of the cost function, we can see that the choice of the weight type has a decisive impact on the training of the network for a complex task.
+In fact, training the length results in a successful training, while training pressure in the nodes is extrimely inefficient.
+For a visual interpretation of the regression cost funtion, \cref{fig:lin_regr1}(c) shows the status of the training at three different training steps.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{plots/regression/G00010001.pdf}
+    \caption{}\label{fig:lin_regr1}
+\end{figure}
+
+Keeping the same geometry, we inverted the direction of some of the memristors, indicated in \cref{fig:lin_regr2}(a).
+The resulting performance, \cref{fig:lin_regr2}(b), shows how the topology of the network directly infulences the trainability of a specific kind of weight.
+In fact, the concentration at the node seems to be preferrable to be trained in this configuration.
+As for the length, \cref{fig:lin_regr2}, shows how te network responds to the test set in three different moments of the training.
+
+\begin{itemize}
+    \item Explain why the direction of memristors is important.
+    \item Note that the edges which were changed are connected to inputs or outputs — this indicates their importance.
+    \item Pressure is always trained very little; comment on why it is more difficult to train. (Consider including a graph of $g_{\infty}$ for positive and negative potentials.)
+    \item Due to the many possible combinations and degrees of freedom, small networks require a more efficient search strategy. (Propose using genetic algorithms.)
+\end{itemize}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{plots/regression/G00010002.pdf}
+    \caption{}\label{fig:lin_regr2}
+\end{figure}
+
 \cleardoublepage

### 2025-04-11 codes/linear_regression.py

@@ -10,7 +10,7 @@ import numpy as np
 
 start = time.time()
 
-graph_id = 'G00010001'
+graph_id = 'G00010002'
 DATA_PATH = f'{par.DATA_PATH}regression{graph_id}/'
 
 # --------- INITIALIZE NETWORK ---------
@@ -24,6 +24,7 @@ DATA_PATH = f'{par.DATA_PATH}regression{graph_id}/'
 # regression_working_rho: wokring nw for length directed with 6V extra source, working for rho training
 
 G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
+print(G.edges())
 # G.add_edge('1','7')
 # networks.initialize_edges(G)
 # G = networks.to_directed_graph(G, shuffle=True)
@@ -56,12 +57,12 @@ for weight_type_index in [0]:
     # print(f'{DATA_PATH}')
     
     # G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
-    # G = nx.read_graphml(f'{DATA_PATH}G00010002.graphml')
-    G = nx.read_graphml(f'{DATA_PATH}G00010001.graphml')
+    G = nx.read_graphml(f'{DATA_PATH}G00010002.graphml')
+    # G = nx.read_graphml(f'{DATA_PATH}G00010001.graphml')
     # G = nx.read_graphml(f'{DATA_PATH}G00010003.graphml')
     G.nodes['3']['voltage'] = constant_source[weight_type_index]
 
-    # training.train(G, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index], save_final_graph=True, write_weights=True)
+    training.train(G, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index], save_final_graph=True, write_weights=True)
 
 
 

### 2025-05-19 plots/importance_ginfinity_dynamics/document/appendix.tex
Finished showing that dynamics matters

% \documentclass[reprint,superscriptaddress,prb,floatfix,showkeys]{revtex4-2}
\documentclass[10.5pt]{article}
\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage{braket}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{tgpagella}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{float}
\usepackage{tikz}
\usetikzlibrary{lindenmayersystems}
\usepackage[usestackEOL]{stackengine}
\newtheorem{theorem}{Theorem}[section]
\usepackage{appendix}
\usepackage[capitalise]{cleveref}
\usepackage{imakeidx}
\usetikzlibrary{calc}
\usepackage[normalem]{ulem}
\usepackage[capitalise]{cleveref}

\newcommand{\brac}[1]{\left(#1 \right)} %nice brackets
\newcommand{\bk}[1]{\langle #1 \rangle} 
\newcommand{\m}{\text{m}} %m index
\newcommand{\M}{\text{M}} %m index
\newcommand{\N}{\text{N}} %n index
\newcommand{\n}{\text{n}} %n index
\renewcommand{\a}{\textbf{\text{a}}} %a index

\linespread{1.2}

    \usepackage{geometry}
    \geometry{
     a4paper,
     left=22mm,
     right=22mm,
     top=25mm,
     bottom=30mm,
     }

\title{Learning in Memristive Neural Networks}
\date{}
\begin{document}
% \captionsetup{width=0.93\textwidth}

% \maketitle

[A change in the chosen weight of a memristor directly influences the functional form of $g_{\infty}(\boldsymbol{\Delta})$. In turn, this functional form guides the evolution toward a steady state that aligns with the desired one. It is important to note that the entire functional form is significant, not just the steady-state value of the potential drop and the corresponding conductance, as explained in Appendix A.] -> add in paper

\section*{Dynamical evolution to the steady state}
In this section, we explain more in depth the relaxation toward a steady-state of a memristor network. Specifically, we want to emphasise that in a network where the applied voltage is constant at the input nodes, the dynamical dependence on the steady-state conductance is fundamental to reach desired values of potential drops.

For simplicity, we consider a voltage divider, as shown in \cref{fig:app_vd}, where we set $\Delta P = 0$ and $\Delta \rho = 0$. 
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\columnwidth]{../plots/app_vd.pdf}
    \caption{}
    \label{fig:app_vd}
\end{figure} 
Therefore, the dynamical evolution of the conductance of each memristor discretized in time-steps $\Delta t$, shown in its general form in Eq. (2), reduces to
\begin{equation}
    g_{\m}\brac{t + \Delta t} = g_{\m}\brac{t} +
     \frac{g_{\m,\infty}\brac{\Delta V_{\m}(t)}-g_{\m}\brac{t}}{\tau}\Delta t,
\label{eq:conduct}
\end{equation}
with initial condition $g_{\m}(t=0)=g_0$. At each time-step, the potential drop $\Delta V_{m}(t)$ across each memristor is calculated using Kirchoff's law, that reduces to the expressions
\begin{equation}
    \Delta V_1(t) = \frac{5 g_2(t)}{g_1(t)+g_2(t)}, \ \ \ \ \ \ \ \Delta V_2(t) = \frac{5 g_1(t)}{g_1(t)+g_2(t)},
    \label{eq:potentials}
\end{equation}
found by minimizing the power dissipated by the resistances with respect to the free potential $\partial P/\partial V_2=0$.

The algorithm works as follows:

\begin{itemize}

    \item At time $t=0$, the potentials $\Delta V_1(t=0)$ and $\Delta V_2(t=0)$ are computed from \cref{eq:potentials} using the initial condition $g_1(t=0)=g_2(t=0)=g_0$.
    \item In the following time-step $t=\Delta t$, the potentials $\Delta V_1(t=0)$ and $\Delta V_2(t=0)$ are used to compute conductances $g_{\m}(\Delta t)$ using \cref{eq:conduct}.
    \item The previous step is iterated, and the system reaches the steady-state when $g_{\m}(t)=g_{\m,\infty}(t)$.

\end{itemize}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\columnwidth]{../plots/grid_initial_condition.pdf}
    \caption{Relaxation toward the steady
    state when $g_{1,\infty}(V)=g_{2,\infty}(V)$.}
    \label{fig:memristor_network}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\columnwidth]{../plots/grid_trained.pdf}
    \caption{Relaxation toward the steady state when the system has been trained to give $V_2 = 4V$. The training sets the two different functional forms of $g_{\infty}$ seen in the right figure.}
    \label{fig:memristor_network}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\columnwidth]{../plots/grid_trained_change_func.pdf}
    \caption{We consider the trained system in Figure 3, but we define the funtion $g_{1, \infty}$ such that it passes througth the steady state point (triangle in Figure 3), now indicated with a red cross, but with a different functional form. Due to the different functinal form, the system reaches a steady state that doesn't coincide with the desired in Figure 3.}
    \label{fig:memristor_network}
\end{figure}

\end{document}

### 2025-05-19 codes/check_vd.py

@@ -11,21 +11,31 @@ import ahkab
 
 start = time.time()
 
-def plot_ginfty(ax, circuit, mysistor_id, potential_vec=False, result=None):
+def plot_ginfty(ax, circuit, mysistor_id, potential_vec=False, result=None, steady_state_point = None, change_func=False):
 
     if potential_vec == True:
         
-        potential_vec = np.linspace(-5, 5)
+        potential_vec = np.linspace(0, 5)
         mysistor = ahkab.Circuit.get_elem_by_name(circuit, part_id=mysistor_id)
         g_infinity = []
         for potential in potential_vec:
-            g_infinity.append(ahkab.transient.g_infinity_func(potential, 0, 0, mysistor)*mysistor.g_0)
-        ax.plot(potential_vec, g_infinity, **par.g_infinity_style[f'{mysistor_id}'])
+            if change_func and mysistor_id=='M1':
+                g_infinity_value = ahkab.transient.g_infinity_func(potential, 0, 0, mysistor, change_func=True)*mysistor.g_0
+            else:
+                g_infinity_value = ahkab.transient.g_infinity_func(potential, 0, 0, mysistor)*mysistor.g_0
+            g_infinity.append(g_infinity_value)
+        ax.plot(potential_vec, g_infinity, **par.g_infinity_style[f'{mysistor_id}'], zorder=0)
         
+        mysistor_index = int(mysistor_id[-1])-1
+        ax.scatter(steady_state_point[mysistor_index][0], steady_state_point[mysistor_index][1], **par.steady_state_point[f'{mysistor_id}'], zorder=1)
+
+        if change_func and mysistor_id=='M1':
+            ax.scatter(1, 12.394654281291412, marker='x', color = 'red', s = 150, label = 'desired')
+            
         ax.set_ylabel(r'$g_{\infty}[pS]$', fontsize = par.axis_fontsize)
         ax.set_xlabel(r'V[V]', fontsize = par.axis_fontsize)
         ax.tick_params(axis='both', labelsize=par.size_ticks)
-        ax.legend(fontsize = par.legend_size)
+        ax.legend(fontsize = par.legend_size, loc = 'upper right')
         
     else:
         deltav = 0 
[…]

### 2025-05-19 codes/parameters.py

@@ -74,6 +74,11 @@ conductances_style = {
     
 }
 
+steady_state_point = {    
+    'M1': dict(marker = '^', c = 'darkcyan', s=200, edgecolors= 'blue' , label=r'steady state $M_1$'),
+    'M2': dict(marker = 'o', c = 'lightblue', s=200, edgecolors= 'blue', label=r'steady state $M_2$')
+    }
+
 g_infinity_style = {
     'M1': dict(c = 'mediumaquamarine', lw=5, label=r'$g_{\infty}^{M_1}$'),
     'M2': dict(c = 'dodgerblue', lw=2, label=r'$g_{\infty}^{M_2}$')

### 2025-05-27 paper/paper.tex
Finished conclusions papre, working on plots for regression. Lost graph G001002?

--- 2025-04-11 paper/paper.tex
@@
 
-The PNN we consider is an electrical network make of nodes connected by resistive elements.
-As resistive elements, we consider conical microfluidic channels that are schematically represented in \cref{fig:memristor_scheme}.
+The PNN we consider is an electrical network made of nodes connected by resistive elements.
+As resistive elements, we consider conical microfluidic channels, schematically represented in \cref{fig:memristor_scheme}.
 \begin{figure}[h]
@@
 \end{figure} 
-An azimuthally symmetric conical channel connects two reservoirs that contain an incompressible aqueous 1:1 electrolyte with viscosity $\eta=1.01mPa s$ containing ions with diffusion coefficients $D = 1.75\mu m^2 ms^{-1}$ and charge $\pm e$ with $e$ the proton charge.
-The cone has a base radius of $R_b = 200$nm, a tip radius of $R_t=50$nm and has a length $L = 10\mu$m, which sets it in the long channel limit where entrance and exit effects can be neglected.
+An azimuthally symmetric conical channel connects two reservoirs that contain an incompressible aqueous 1:1 electrolyte with viscosity $\eta=1.01mPa s$ containing ions with diffusion coefficients $D = 1.75\mu m^2 ms^{-1}$ and charge $\pm e$, with $e$ the proton charge.
+The cone has a base radius of $R_b = 200$nm, a tip radius of $R_t=50$nm and has length $L = 10\mu$m, which sets it in the long channel limit, where entrance and exit effects can be neglected.
 The walls of the channel are homogeneously charged and generate a surface potential $\psi_0$ that attracts the opposite-sign ions present in the solution due to the dissociation of the electrolyte.
@@
 Meanwhile, the pressure drop $\Delta P = P_b - P_t$, given by the difference between the base and the tip pressure, induces a Poiseuille-like flow $Q_P = (\pi R_b^3 R_t^3/8L\eta\langle R^2\rangle)\Delta P$.
-Finally, the ions experience a concentration gradient $\Delta \rho = \rho_b - \rho_t$, defined by the difference between the ion concentration in the reservoir connected to the base of the channel, $\rho_b$, and the concentration at the tip, $\rho_t$.
+Finally, the ions experience a concentration gradient $\Delta \rho = \rho_b - \rho_t$, defined by the difference between the ion concentration in the reservoir connected to the base of the channel, $\rho_b$, and the concentration in the reservoir connected to the tip, $\rho_t$.
 Consequently, a diffusive fluid flow arises.
@@
 Due to the fact that the conductance depends on the history of the signals applied, this system is called memristor.
-Aside from the direct dependence of the conductance on the external stimuli, there is an implicit dependence on the geometrical properties such as lenght $L$ and radius ratio $R_b/R_t$ that we choose to consider.
+Aside from the direct dependence of the conductance on external stimuli, there is also an implicit dependence on geometrical properties, such as length $L$ and base radius $R_b$, that we address in this work.
 
@@
 Nonetheless, we notice that solving the dynamical equations is needed due to the dynamical change in the conductance of the memristors that, in turn, results in time-dependent potential drops across them.
+A more detailed illustration of the algorithm that solves the circuit, along with an analysis of the relaxation to the steady state of the memristor network, is provided in \cref{app:dyn_evol_steady_state}.
 
@@
 For example, we may select an external stimulus, such as the imposed pressure or the density at each node.
-Alternatively, we can choose the length or radius ratio between the base and tip of the channel.
+Alternatively, we can choose the length or base radius of the channel.
 The training process is carried out by iterating a scheme, illustrated in \cref{fig:training_scheme}, which consists of two phases: a forward pass and a backward pass.
 
-In the feedforward phase, the network is fed with specific electric potential in the input nodes.
+In the feedforward phase, the network is fed with specific electric potentials in the input nodes.
 Following both circuit laws and memristor's dynamics, the network reaches a steady state where electrical potentials can be measured in the output nodes.
 Clearly, the output of the network depends on the set of weights imposed on the network $\boldsymbol{w}$, regardless them being node or edge defined.
-The value of the outputs can be used to quantify the status of the network, meaning that it indicated how far the answer of the network is from the desired one.
+The value of the outputs can be used to quantify the status of the network, meaning how much its answer differs from the desired one.
 Specifically, we define a cost function that computes the difference squared between the voltage in the output nodes and the values of desired voltages
@@
 C\left( \boldsymbol{w} \right) = \sum_{i \in \Lambda} \brac{V_i\brac{\boldsymbol{w}} - V_i^D}^2,
+\label{eq:cost_func}
 \]
-where $\Lambda$ represents the set of indeces belonging to the output nodes, $V_i\brac{\boldsymbol{w}}$ the voltage measured in the output nodes and $V^D$ is a vector containing the values of desired output nodes.
+where $\Lambda$ represents the set of indeces belonging to the output nodes, $V_i\brac{\boldsymbol{w}}$ the voltage measured on the output nodes and $V^D$ is a vector containing the values of desired output nodes.
 
@@
 Moreover, also the backward pass we use can be translated to a physical event since involves performing the forward pass a number of time as the number of the weights.
-Once the cost functions are determined, only the simple algebric calculations of \cref{eq:weight_update} are left to be computed.
-We peopse this method as a hybrid physical and in-silico training algorithm also as a future experimental approach to the probelm.
+Once the gradient of the cost function is determined and stored, only the simple algebric calculations of \cref{eq:weight_update} are left to be computed.
+We propose this method as a hybrid physical and in-silico training algorithm, as a future experimental approach to the probelm.
 
@@
 The values of the choosen set of weights simultaneouly changes from the initial condition, as shown in Figures [], adjusting the behaviour of the network to the desired one.
-In fact, if the values of a choosen type of weights at the end of the training are imposed to the netowork together with the voltage inputs, the network will autonomously realx to a staedy state that coincides with the desired state.
+If the values of a choosen type of weight at the end of the training are imposed to the netowork together with the voltage inputs, the network will autonomously realx to a staedy state that coincides with the desired state.
 To exemplify this point, the inset in Figure shows the physical relaxation of the voltage divider when the trained values of pressure, which correspond to the three values in the last training step, are imposed on the nodes together with the constant inputs voltages.
-The inset shows that the output voltage $V_2$ autonomously relaxes to the desired value of $V_D=3V$ in a time scale characteristic of the memristor.
+The inset shows that the output voltage $V_2$ autonomously relaxes to the desired value of $V_D=4V$ in a time scale characteristic of the memristor.
 
@@
 
-In order to investigate the adaptability of the system, we tested it with a set of three consequent desired voltages $V_D=\{1V, 3V, 4V\}$.
+In order to investigate the adaptability of the algorithm, we trained the system with a set of three consequent desired voltages $V_D=\{1V, 3V, 4V\}$.
 In \cref{fig:evolution_targets} we show how the output voltgage $V_2$ subsequently adapts to the desired voltages during the training of the pressures in the nodes, the evolution of which can be seen in \cref{fig:evolution_targets}.
@@
 
-To generalize the training objective to a more general objective, we consider memrisotr network built from a bigger network geometry.
-\cref{fig:mse_general}(a) shows a three-input and two-output network, that we train to give $[3V, 4V]$ in the output nudes, when $[0V, 2V, 5V]$ are given as input.
-Reaching a desired input-output voltage mapping in a generic electric circuit can be useful to adress desired voltage outputs in specific points of the circuit for variuous electronic purpuses.
-[...]
+To generalize the training objective, we consider a memristor network constructed with a more complex geometry.
+\cref{fig:mse_general}(a) illustrates a network with three input nodes and two output nodes.
+The network is trained to produce output voltages of $[3,V, 4,V]$ when provided with input voltages of $[0,V, 2,V, 5,V]$.
+Reaching a desired input-output voltage mapping in a generic electric circuit can be useful for variuous electronic purpuses \cite{voltage_controlled_oscillator, onchip_powerdistributed}.
 
@@
 (b) Cost funtion during training of generic graph for input-output mapping task.
-The different colors indicate different weight choise.}\label{fig:mse_general}
+The different colors indicate different weight choice.}\label{fig:mse_general}
 \end{figure}
@@
 
-We broaden the training capability of the network by including a linear regression task, where, in its simplest form, the network is trained to give potential output $V^{\text{out}}$ related to the input potential $V^{\text{in}}$ via a linear relationship
+We broaden the training capability of the network by including a linear regression task, where, in its simplest form, the network is trained to give potential output $V_{\text{out}}$ in a certain node of the network, related to the input potential $V_{\text{in}}$ via a linear relationship
 \begin{equation}
@@
 \end{equation}
-We generate two sets of data, a training test $ \{ V_{\text{in}}, V_{\text{out}} \}_{i=1}^{T}$ and a test set $\{ V_{\text{in}}, V_{\text{out}} \}_{i=1}^{Te}$.
-To create the test set, a set of a number of training steps of random values is sampled from the interval $[1V, 4V]$ is created and fed to equation \cref{eq:linear_relationship}, giving a set of outputs that satifiy the desired relationship.
-With a similar approach, the test set is constituted by $20$ input points equally spaced in the sampling interval, and output voltages that satisfy \cref{eq:linear_relationship}.
-Notice that the two sets contain different elements.
+We generate two sets of data, a training set $ \{ V_{\text{in}}^{(j)}, V_{\text{out}}^{(j)} \}_{j=1}^{N_{\text{train}}}$ and a test set $ \{ V_{\text{in}}^{(j)}, V_{\text{out}}^{(j)} \}_{j=1}^{N_{\text{test}}}$, where $N_{\text{train}}$ and $N_{\text{train}}$ denote the number of training and test samples, respectively.
+To create the training set, a sequence of input voltages is randomly sampled from the interval $[1V, 4V]$, and the corresponding output voltages are computed using equation \cref{eq:linear_relationship}, ensuring that the input-output pairs satisfy the desired relationship.
+The test set is constructed in a similar way, but uses $N_{\text{test}}=20$ input values that are evenly spaced within the same interval.
+Their corresponding outputs are also computed using equation \cref{eq:linear_relationship}.
+Note that the training and test sets contain different input values.
 
-The training algorithm presented in \cref{sec:training} can be slightly adapted to function for this training objective.
-At each step of the training, a pair of input and output voltages is selected from the training set, and used as input voltage and desired output in the algorithm above.
-In order to evaluate how well the algorithm is performing, the testset is evaluated by computing the test cost function.
-If the trained weight set after certain training step is $\boldsymbol{w}$, we define this function as
+The training algorithm described in \cref{sec:training} can be slightly adapted to support this training objective.
+At each training step, an input-output voltage pair is selected from the training set and used as the input voltage and target output in the algorithm.
+This differs from the original algorithm, where the same input-output pair was presented at every step.
+
+Therefore, at each training step $ j \in[1, N_{\text{train}}] $, the cost function used to compute the gradient in \cref{eq:gradient_cost_func} is adapted to
 \[
-C_{t}\left( \boldsymbol{w} \right) = \sum_{j=1}^{Te}\brac{V_{out}\brac{\boldsymbol{w}} - V_j^D}^2,
+C_j(\boldsymbol{w}) = \left[ V_{\text{out}}(\boldsymbol{w}) - V_{\text{out}}^{(j)} \right]^2,
 \]
-which considers the difference between the voltage measured in the output node when the impoing the $j-$th input voltage of the test set and the desired output of the same test point, for every point of the set.
+where $ V_{\text{out}}(\boldsymbol{w}) $ is the measured output voltage for the selected input, and $ V_{\text{out}}^{(j)} $ is the corresponding target output in the training set.
+This expression corresponds to a simplified version of \cref{eq:cost_func} for the case of a single output node.
+
+To evaluate how well the algorithm performs during training, we compute the \emph{test cost function} $ C_{\text{test}} $ over the entire test set.
+If $ \boldsymbol{w} $ denotes the weight vector at a given training step, the test cost is defined as
+\[
+C_{\text{test}}\left( \boldsymbol{w} \right) = \sum_{j=1}^{N_{\text{test}}} \left[ V_{\text{out}}(\boldsymbol{w}) - V_{\text{out}}^{(j)} \right]^2,
+\]
+which sums the squared differences between the measured and target output voltages at each test point.
+For each input $V_{\text{in}}^{(j)}$ in the test set, the voltage $ V_{\text{out}}(\boldsymbol{w}) $ is the output produced by the network with weights $ \boldsymbol{w} $, while $ V_{\text{out}}^{(j)} $ is the desired output.
+This test cost is used for performance evaluation and is not involved in the training process.
+
+Since the task is more demanding than a single input-output mapping, we use a larger network with more degrees of freedom.
+\cref{fig:lin_regr1}(a) shows the graph selected for the regression task.
+It consists of 20 edges and 10 nodes, three of which are inputs and one is an output.
+Among the three input nodes, one is set to ground and another to a constant value, in order to enable the training of a linear function with an offset.
+For the training objective, we aim to train the network to fit the line $V_{\text{out}} = 0.2 V_{\text{in}} + 0.3$ over the input voltage range $[1V, 5V]$.
+
+The performance of the algorithm on this task is shown in \cref{fig:lin_regr2}(b), where the learning rates for the different weights have been fine-tuned to prevent overshooting while still maintaining comparable convergence speed.
+From the behavior of the cost function, it is evident that the choice of weight type has a decisive impact on the network’s ability to learn a complex task.
+Specifically, training the lengths of the channles on the edges results in successful convergence, whereas training the node pressures proves to be extremely inefficient.
+For a visual interpretation of the regression cost function, \cref{fig:lin_regr1}(c) shows the state of the training at three different time steps.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{plots/regression/G00010001.pdf}
+    \caption{}\label{fig:lin_regr1}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{plots/regression/G00010002.pdf}
+    \caption{}\label{fig:lin_regr2}
+\end{figure}
+
+To study the influence of memristor orientation on training performance, we retained the same network geometry but inverted the orientation of some memristors, as shown in \cref{fig:lin_regr2}(a).
+Specifically, if in the original configuration the base of a memristor pointed to one node and the tip to another, we reversed this direction.
+
+This modification significantly affects the behavior of the network.
+As shown in \cref{fig:lin_regr2}(b), the new orientation alters the trainability of different weight types: in this configuration, training node concentration leads to better performance, while training edge length becomes less efficient.
+The underlying reason is that inverting the orientation of a channel also inverts the sign of the external stimulus applied to it, since the stimuli are defined node-wise and the difference is always taken as "base minus tip."
+
+This reversal changes both the shape and the conductivity range over which the function $g_{\infty}(\boldsymbol{\Delta})$ is defined, thereby limiting or enabling the conductivity values the channel can attain.
+A network with well-oriented channels can therefore access conductivity ranges that make the training solvable, while a poorly oriented network may be constrained to regions where solutions are not found.
+To exemplify this point, Figure~(X) of Ref.~(Y) shows $g_{\infty}$ as a function of pressure for positive and negative potential drops, assuming a zero concentration drop.
+The plot reveals two completely disjoint conductivity ranges depending on the sign of the potential drop, which explains why training on pressure alone may be challenging.
+This highlights the need for deeper exploration of network geometry when selecting the type of weight to train.
+In this regard, we observe that the edges whose orientation was inverted are directly connected to either the input or the output nodes.
+This suggests that particular attention should be given to these edges in future explorations, as they may have a bigger impact on trainability.
+As for the length-based training, \cref{fig:lin_regr2}(c) illustrates how the network responds to the test set at three different stages of the training process.
+
+Bigger networks have more degrees of freedom, and should allow for a bigger range of exploration of a solution.
+However, the experimantal realization would become more challenging.
+In this work, we show that an adequate geometry for a specific training goal can be sufficent to make a small network trainable.
+A deper analysis on the influence of geometry on the trainabiliy is needed in the research contest of physical learning and can be explored in future research.
+
+Larger networks offer more degrees of freedom and can, in principle, enable broader exploration of the solution space.
+However, their experimental realization becomes increasingly complex.
+In this work, we showed that an appropriately chosen geometry adapted to a specific training objective can be sufficient to make even a small networks trainable.
+A deeper analysis of the role of geometry in determining trainability is still needed in the context of physical learning.
+
+\section{Conclusions}
+
+We proposed a physical neural network composed of nodes connected by aqueous memristors.
+These devices exhibit conductance that responds to external stimuli of various physical natures, such as electrical, mechanical, and chemical.
+Additionally, their conductivity is sensitive to changes in the geometric parameters of their channel-like structure.
+
+Our motivation for using these devices lies in the ability to exploit these dependencies to control the conductance of each memristor in the network.
+This enables us to manipulate an input electrical signal in a programmable way, according to a specific computational objective.
+
+To this end, we developed a training algorithm that targets one of the physical parameters influencing conductivity and treats it as the analog of a weight in a standard machine learning framework.
+The electrical signal is used as both input and output, while other types of signals or geometric dependencies are used to adjust the network during training.
+
+The training process consists of two phases.
+The first is an inference phase, in which input voltages are applied to the system and the circuit is allowed to physically relax to a steady state.
+At this point, the output voltages can be read.
+Ideally, these outputs should match a predefined set of target values reflecting the training goal.
+In the second phase, the update phase, the weights are adjusted to minimize a cost function based on the difference between the actual and desired outputs.
+By iteratively applying this procedure, the network is gradually tuned to achieve the desired input-output behavior.
+
+The inference phase is entirely physical, as the system evolves naturally to its steady-state response when inputs are applied.
+In contrast, the update phase is only partially physical.
+The weight update relies on estimating the gradient of the cost function using a finite-differences method, following a steepest descent rule.
+Specifically, each weight is perturbed slightly, and the resulting change in the cost function is computed.
+The gradient is then approximated by taking the difference in cost between the perturbed and unperturbed configurations, divided by the magnitude of the perturbation.
+While an external computer is required to store and coordinate the gradients for each weight, the values themselves can be obtained through physical measurements of the system's output under the two conditions.
+This structure allows for a mostly physical implementation of learning, with digital support.
+
+As a first simple application, we tested the algorithm on a voltage divider, training the network to produce a specific fraction of the input voltage at the output node.
+The training was successful across all four selected weight types: pressure drop, concentration gradient across the memristor, length of the memristor, and its base radius.After selecting a particular weight type, we further demonstrated that the network, once trained to achieve a specific objective, could be retrained to a different target with similar training speed.
+This result indicates that the algorithm is both adaptive to new training objectives and largely independent of the initial weight configuration.
+
+Training larger and more complex memristor networks is also feasible with the algorithm we proposed.
+We demonstrated that a network composed of 9 nodes and 15 edges can be successfully trained for input-output voltage mapping using all the weight types considered.
+
+We then challenged a more complex network, with 10 nodes and 20 edges, to perform a linear regression task with an offset.
+In this setting, we observed that the trainability of the network using a specific weight type strongly depends on the network's geometry.
+First, we showed that different geometries yield different final training accuracies when using the same weight type.
+Then, keeping the geometry fixed, we demonstrated that the orientation of the memristors also plays a crucial role: reversing the direction of just three memristors connected to either input or output nodes improved the training precision when using concentration as the trained weight by three orders of magnitude.
+
+Given that the expressiveness of deep neural networks grows exponentially with depth\cite{big_neuralnet1, big_neuralnet2}, we interpret the limitations encountered in training linear regression tasks as a consequence of the small size of the network.
+However, small-scale networks are experimentally attractive, and in such cases, a training error of a few orders of magnitude may be acceptable.
+A key challenge for scaling such networks lies in the physical control of individual weights, especially when the weight type involves mechanical or geometric parameters.
+Emerging technologies in microfluidics, soft robotics, and programmable matter may provide practical tools to overcome these limitations and scale the network while preserving control.
+
+The core intention behind the algorithm is to enable a physically realizable neural network that requires minimal computational resources to operate.
+Thanks to the multiple physical dependencies of memristors, such as electrical, chemical, mechanical and geometrical factors, the algorithm supports a wide range of possible weight types.
+This flexibility makes it highly adaptable to various experimental scenarios, depending on which parameters are most accessible or controllable in a given setup.
+[..
+examples of realizable system, cite literature].
 
 \cleardoublepage
-\section{Conclusion}
+\appendix
 
-\appendix
+[A change in the chosen weight of a memristor directly influences the functional form of $g_{\infty}(\boldsymbol{\Delta})$.
+In turn, this functional form guides the evolution toward a steady state that aligns with the desired one.
+It is important to note that the entire functional form is significant, not just the steady-state value of the potential drop and the corresponding conductance, as explained in Appendix A.] -> add in paper
+
+\section{Dynamical evolution to the steady state \label{app:dyn_evol_steady_state}}
+In this section, we explain more in depth the relaxation toward a steady-state of a memristor network.
+Specifically, we want to emphasise that in a network where the applied voltage is constant at the input nodes, the dynamical dependence on the steady-state conductance is fundamental to reach desired values of potential drops.
+
+For simplicity, we consider a voltage divider, as shown in \cref{fig:app_vd}, where we set $\Delta P = 0$ and $\Delta \rho = 0$. 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\columnwidth]{plots/appendixA/app_vd.pdf}
+    \caption{}
+    \label{fig:app_vd}
+\end{figure} 
+Therefore, the dynamical evolution of the conductance of each memristor discretized in time-steps $\Delta t$, shown in its general form in Eq. (2), reduces to
+\begin{equation}
+    g_{\m}\brac{t + \Delta t} = g_{\m}\brac{t} +
+     \frac{g_{\m,\infty}\brac{\Delta V_{\m}(t)}-g_{\m}\brac{t}}{\tau}\Delta t,
+\label{eq:conduct}
+\end{equation}
+with initial condition $g_{\m}(t=0)=g_0$. At each time-step, the potential drop $\Delta V_{m}(t)$ across each memristor is calculated using Kirchoff's law, that reduces to the expressions
+\begin{equation}
+    \Delta V_1(t) = \frac{5 g_2(t)}{g_1(t)+g_2(t)}, \ \ \ \ \ \ \ \Delta V_2(t) = \frac{5 g_1(t)}{g_1(t)+g_2(t)},
+    \label{eq:potentials}
+\end{equation}
+found by minimizing the power dissipated by the resistances with respect to the free potential $\partial P/\partial V_2=0$.
+
+The algorithm works as follows:
+
+\begin{itemize}
+
+    \item At time $t=0$, the potentials $\Delta V_1(t=0)$ and $\Delta V_2(t=0)$ are computed from \cref{eq:potentials} using the initial condition $g_1(t=0)=g_2(t=0)=g_0$.
+    \item In the following time-step $t=\Delta t$, the potentials $\Delta V_1(t=0)$ and $\Delta V_2(t=0)$ are used to compute conductances $g_{\m}(\Delta t)$ using \cref{eq:conduct}.
+    \item The previous step is iterated, and the system reaches the steady-state when $g_{\m}(t)=g_{\m,\infty}(t)$.
+
+\end{itemize}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\columnwidth]{plots/appendixA/grid_initial_condition.pdf}
+    \caption{Relaxation toward the steady
+    state when $g_{1,\infty}(V)=g_{2,\infty}(V)$.}
+    \label{fig:memristor_network}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\columnwidth]{plots/appendixA/grid_trained.pdf}
+    \caption{Relaxation toward the steady state when the system has been trained to give $V_2 = 4V$. The training sets the two different functional forms of $g_{\infty}$ seen in the right figure.}
+    \label{fig:memristor_network}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\columnwidth]{plots/appendixA/grid_trained_change_func.pdf}
+    \caption{We consider the trained system in Figure 3, but we define the funtion $g_{1, \infty}$ such that it passes througth the steady state point (triangle in Figure 3), now indicated with a red cross, but with a different functional form.
+Due to the different functinal form, the system reaches a steady state that doesn't coincide with the desired in Figure 3.}
+    \label{fig:memristor_network}
+\end{figure}
 

### 2025-05-27 codes/check_vd.py

@@ -145,8 +145,6 @@ def plot_analysis_relaxation_ingrid(circuit, potentials_vec, resistances_vec, ph
     
     # Plot potential  
     plot_potentialdiff(ax_bottom, potentials_vec)
-    fig.tight_layout()
-    plt.savefig(f"../plots/importance_ginfinity_dynamics/plots/potential_drops_{phase}.pdf")
     
     # Plot g_infty as func of potential
     plot_ginfty(ax_left, circuit, 'M1', potential_vec=True, steady_state_point=steady_state_point, change_func=change_func)
@@ -170,8 +168,6 @@ def plot_analysis_relaxation_ingrid(circuit, potentials_vec, resistances_vec, ph
     
     fig.tight_layout()
     plt.savefig(f"../plots/importance_ginfinity_dynamics/plots/grid_{phase}.pdf")
-   
-   
    
    
 # -> DEFINE graph from networks module
@@ -199,6 +195,7 @@ tran_analysis = ahkab.new_tran(tstart=0, tstop=0.02, tstep=1e-3, x0=None, use_st
 result = ahkab.run(circuit_trained, an_list=tran_analysis) 
 potentials_vec = result[0]
 resistances_vec = result[1]
+resistances_vec_trained = resistances_vec
 
 plot_analysis_relaxation(circuit_trained, potentials_vec, resistances_vec, 'trained')
 
@@ -217,3 +214,37 @@ plot_analysis_relaxation(circuit_trained, potentials_vec, resistances_vec, 'trai
 
 plot_analysis_relaxation_ingrid(circuit_trained, potentials_vec, resistances_vec, 'trained_change_func')
 
+# ANALYSIS WHEN TRAINED ginfinity INITIAL CONDITION FOR LENGTH 
+
+G_updated_initial_cond = G.copy(as_view=False)
+for edge_index, edge in enumerate(G_updated_initial_cond.edges()):
+    G_updated_initial_cond.edges[edge]["resistance"] = resistances_vec_trained[-1][edge_index]
+    print(resistances_vec[-1][edge_index])
+
+circuit_updated_initial_cond = networks.circuit_from_graph(G_updated_initial_cond, type='memristors') 
+
+tran_analysis = ahkab.new_tran(tstart=0, tstop=0.02, tstep=1e-4, x0=None, change_func = True, use_step_control=False)
+result = ahkab.run(circuit_updated_initial_cond, an_list=tran_analysis) 
[…]

### 2025-05-27 codes/linear_regression.py

@@ -10,26 +10,28 @@ import numpy as np
 
 start = time.time()
 
-graph_id = 'G00050001'
+graph_id = 'G00010002'
 DATA_PATH = f'{par.DATA_PATH}regression{graph_id}/'
 
 # --------- INITIALIZE NETWORK ---------
 
 # -> DEFINE graph from networks module
-G = networks.random_graph(save_data=True) 
+# G = networks.random_graph(save_data=True) 
 # G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
+G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 
 # Using graphs:
 # regression_working: wokring nw for length not directed with 3V extra source
 # regression_working_rho: wokring nw for length directed with 6V extra source, working for rho training
 
-# G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 # print(G.edges())
 # G.add_edge('1','7')
 # networks.initialize_edges(G)
 # G = networks.to_directed_graph(G, shuffle=True)
 G.graph['name'] = graph_id
+print(G.graph['name'])
 nx.write_graphml(G, f'{DATA_PATH}{graph_id}.graphml')
+print(G.edges())
 
 # print(G.nodes['3']['voltage'])
 
@@ -43,59 +45,56 @@ fig.tight_layout()
 fig.savefig(f"{DATA_PATH}graph.pdf", transparent=True)
 
 # --------- TRAIN NETWORK ---------
-training_steps = 100   # choose
+training_steps = 400   # choose
 training_type = 'regression'    # choose
 
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
-learning_rate_vec = [5e-7, 1e-6, 7e-4, 1e2, 1e3]
-constant_source = [3, 3, 3, 3]
+learning_rate_vec = [1e-6, 1e-6, 1e-4, 2e2, 1e3]
+constant_source = [3, 3, 7, 3]
 
 weight_type_index = 0   # choose
 
-# for weight_type_index in [0,1,2,3]:
-#     # print(f'{DATA_PATH}')
+for weight_type_index in [2]:
     
-#     # G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
[…]

### 2025-05-27 codes/networks.py

@@ -213,8 +213,6 @@ def circuit_from_graph(G, type):
 
         if type == 'memristors':
 
-            # print(edge, G.nodes[edge[0]]['rho'], G.nodes[edge[0]]['rho']-G.nodes[edge[1]]['rho'])
-
             circuit.add_mysistor(f'M{index+1}', f'n{edge[0]}', f'n{edge[1]}', value = G.edges[edge]["resistance"], rho_b=G.nodes[edge[0]]['rho'], length_channel = G.edges[edge]['length']*1e-6, radius_base = G.edges[edge]['radius_base']*1e-9, pressure=(G.nodes[edge[0]]['pressure']-G.nodes[edge[1]]['pressure'])*1e5, delta_rho = (G.nodes[edge[0]]['rho']-G.nodes[edge[1]]['rho']))
 
         else:

### 2025-05-27 codes/parameters.py

@@ -46,15 +46,14 @@ memr_resistances_style = dict(marker = 'o', markersize=3, lw=1)
 # REGRESSION TRAINING
 
 regression_styles = {
-    'length': dict(marker = 'o', c = cmap.colors[0], lw=1, label = rf'$L$'),
-    'length_des': dict(c = 'lightpink', lw=4, label = rf'$V^D$'),
+    'length': dict(marker = 'o', s=5, c = cmap.colors[0], lw=0.6, label = rf'$L$'),
+    'length_des': dict(c = 'lightpink', lw=2, label = rf'$V^D$'),
     'rho': dict(marker = 'o', c = cmap.colors[1], lw=1, label = rf'$\rho$'),
     'rho_des': dict(c = 'moccasin', lw=4, label = rf'$V^D$'),
     'radius_base': dict(marker = 'o', c = cmap.colors[2], lw=1, label = rf'$R_b$'),
     'radius_base_des': dict(c = 'yellow', lw=4, label = rf'$V^D$'),
     'pressure': dict(marker = 'o', c = cmap.colors[3], lw=1, label = rf'$P$'),
     'pressure_des': dict(c = 'green', lw=4, label = rf'$V^D$')
-    
 }
 
 reg_desired = dict(c = 'lightblue', lw=3, label = rf'$V_1^D$')

### 2025-05-27 codes/plotting.py

@@ -232,8 +232,8 @@ def plot_regression(ax, graph_id, weight_type, step):
     
     ax.scatter(x, y1, **style)
     
-    ax.set_ylabel(r'$V_{out}$', fontsize = par.axis_fontsize)
-    ax.set_xlabel(r'$V_{in}$', fontsize = par.axis_fontsize)
+    ax.set_ylabel(r'$V_{out}$', fontsize = (par.axis_fontsize-7))
+    ax.set_xlabel(r'$V_{in}$', fontsize = (par.axis_fontsize-7))
     
     ax.grid(ls=":")
     ax.tick_params(axis='both', labelsize=par.size_ticks)

### 2025-05-27 codes/regression_plots_paper.py

@@ -9,7 +9,7 @@ import plotting
 import matplotlib.gridspec as gridspec
 
 
-graph_id = 'G00010001'
+graph_id = 'G00010002'
 DATA_PATH = f'{par.DATA_PATH}regression{graph_id}/'
 G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 training_steps = 400
@@ -46,3 +46,33 @@ ax5.legend(fontsize = par.legend_size)
 
 # fig.tight_layout()
 fig.savefig(f"../paper/plots/regression/{graph_id}.pdf")
+
+
+fig = plt.figure(figsize=(13, 6.5), constrained_layout=True)
+outer = gridspec.GridSpec(1, 2, width_ratios=[1, 2], figure=fig)
+
+# Right column for MSE plot
+ax2 = fig.add_subplot(outer[0, 1])
+plotting.plot_mse(ax2, fig, graph_id, training_type, 'length')
+plotting.plot_mse(ax2, fig, graph_id, training_type, 'radius_base')
+plotting.plot_mse(ax2, fig, graph_id, training_type, 'rho')
+plotting.plot_mse(ax2, fig, graph_id, training_type, 'pressure')
+ax2.legend(fontsize=par.legend_size)
+
+# Add inset axes inside ax2
+inset_ax1 = ax2.inset_axes([0.07, 0.5, 0.2, 0.2])  # [x0, y0, width, height]
+plotting.plot_regression(inset_ax1, graph_id, 'length', step=0)
+# inset_ax1.set_title("Step 0", fontsize=(par.size_ticks-7))
+inset_ax1.tick_params(axis='both', labelsize=(par.size_ticks-7))
+
+inset_ax2 = ax2.inset_axes([0.55, 0.6, 0.2, 0.2])
+plotting.plot_regression(inset_ax2, graph_id, 'length', step=50)
+# inset_ax2.set_title("Step 50", fontsize=(par.size_ticks-7))
+inset_ax2.tick_params(axis='both', labelsize=(par.size_ticks-7))
+
+inset_ax3 = ax2.inset_axes([0.7, 0.1, 0.2, 0.2])
+plotting.plot_regression(inset_ax3, graph_id, 'length', step=400)
+# inset_ax3.set_title("Step 400", fontsize=(par.size_ticks-7))
+inset_ax3.tick_params(axis='both', labelsize=(par.size_ticks-7))
+
+fig.savefig(f"../paper/plots/regression/{graph_id}_newformat.pdf")

### 2025-05-27 codes/training.py

@@ -538,9 +538,9 @@ def train(G, training_type, training_steps, weight_type, delta_weight, learning_
     # LOOP over training steps
     for step in range(training_steps): 
 
-        update_weights(G, training_type, error, weight_type, delta_weight, learning_rate, dataset_input_voltage, dataset_output_voltage, step)
+        # update_weights(G, training_type, error, weight_type, delta_weight, learning_rate, dataset_input_voltage, dataset_output_voltage, step)
 
-        # update_weights_parallel(G, training_type, error, weight_type, delta_weight, learning_rate, dataset_input_voltage, dataset_output_voltage, step)
+        update_weights_parallel(G, training_type, error, weight_type, delta_weight, learning_rate, dataset_input_voltage, dataset_output_voltage, step)
 
         # update_resistances(G, training_type, dataset_input_voltage, dataset_output_voltage)
         if write_weights:

### 2025-05-28 paper/paper.tex
Working on Appendix paper. Here not yet eliminaed the list instead for pseudocode.

@@
 \usepackage{amssymb}
+
+\usepackage{listings}
+
+\lstset{
+    basicstyle=\ttfamily\small,
+    keywordstyle=\color{blue},
+    commentstyle=\color{gray},
+    columns=fullflexible,
+    frame=single,
+    breaklines=true,
+    captionpos=b,
+    numbers=left,
+    numberstyle=\tiny\color{gray},
+    escapeinside={(*@}{@*)}
+}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 
@@
 
-As in a traditional algorithm for an ANN, the core mechanism of the training is to modify the weights associated to the connections of the network such that it maps specific inputs to desired outputs.
-In the case of the electrical network at hand, the training algorithm is designed to output desired voltage values in the output nodes, applying specific voltage values in the input nodes.
+We developed a training algorithm that makes use of the physical dependencies of memristor conductivity on both external stimuli and geometric properties to implement a physical neural network.
+These dependencies allow us to interpret such physical parameters as tunable weights, analogous to standard artificial neural networks, and to encode learning directly into the physical structure of the system.
+As in traditional ANNs, the goal of the training algorithm is to modify these weights so that the network maps a given set of inputs to a corresponding set of desired outputs.
+In the case of the memristor network considered here, training aims to produce specific voltage values at designated output nodes, given fixed voltage inputs at the input nodes.
 \begin{figure}[!h]
@@
 \end{figure} 
-\begin{figure*}[t] 
-    \centering
-    \includegraphics[width=\textwidth]{plots/training/training_scheme.pdf}
-    \caption{}
-    \label{fig:training_scheme}
-\end{figure*}
-Recalling that the dynamics of the memristors we consider depends on both external stimuli and geometrical properties, we have several possibilities for defining the weights of the network.
-However, there is a fundamental distinction between these two categories: external stimuli are applied to the nodes, while geometrical properties are defined edge-wise.
-Consequently, we distinguish between a training algorithm where the weights are defined on the nodes, as in \cref{fig:two_types_weights}(a), and one where the weights are defined on the edges, see \cref{fig:two_types_weights}(b).
+Crucially, the physical quantities that influence memristor conductance fall into two distinct categories: external stimuli, such as pressure or concentration, that are applied to the nodes, and geometric parameters, such as channel length or base radius, that are defined on the edges.
+As a result, we distinguish between two types of training strategies: \emph{node-defined weight training}, as illustrated in \cref{fig:two_types_weights}(a), and \emph{edge-defined weight training}, as shown in \cref{fig:two_types_weights}(b).
+
+A modification to any of these weights affects the network's behavior by altering the functional form of the memristor’s steady-state conductance, $g_{\infty}(\boldsymbol{\Delta})$, which depends on the local potential, pressure, and concentration drops across the device.
+Importantly, the \emph{entire functional shape} of $g_{\infty}$ plays a role in determining the network’s dynamics and ultimate steady state, as illustrated in \cref{app:dyn_evol_steady_state}.
+
 In this work, we focus on training a single property as the weight, while keeping all other parameters fixed as initially defined.
@@
 The training process is carried out by iterating a scheme, illustrated in \cref{fig:training_scheme}, which consists of two phases: a forward pass and a backward pass.
-
-In the feedforward phase, the network is fed with specific electric potentials in the input nodes.
+\begin{figure*}[t] 
+    \centering
+    \includegraphics[width=\textwidth]{plots/training/training_scheme.pdf}
+    \caption{Scheme representing the two phases of the training algorithm, they are iteraitvely performed for a selected number of training steps.}
+    \label{fig:training_scheme}
+\end{figure*}
+In the forward phase, the network is fed with specific electric potentials in the input nodes.
 Following both circuit laws and memristor's dynamics, the network reaches a steady state where electrical potentials can be measured in the output nodes.
@@
 
-In the training algortihm, we first initialize the system with the memristor parameters specified in \cref{sec:memristor_network} and with some initial pressure and concentration values at each node.
+In the training algortihm, we first initialize the system with the memristor parameters specified in \cref{sec:memristor_network}, an initial pressure of $1bar$ and concentration of $0.2mM$ at each node.
 With the knowledge of input and desired output voltage values, it is possible to performe the first forward pass, from which we obtain the cost function $C\brac{\boldsymbol{w}}$, that we store since it is needed in the computation its gradient.
@@
 We compute each entry of the gradient in \cref{eq:gradient_cost_func} by selecting the corresponding weight, a node or an edge parameter, increment its value of $\Delta w$ and applying a forward step to obtain the corresponding entry of $C\brac{\boldsymbol{w}+\boldsymbol{\Delta w}}$.
-With the stored value of $C\brac{\boldsymbol{w}}$, we are able to compute the gradient in \cref{eq:gradient_cost_func} and use it to eventually calculate the weight update in \cref{eq:weight_update}.
+With the stored value of $C\brac{\boldsymbol{w}}$, we are able to compute the gradient in \cref{eq:gradient_cost_func} and use it to calculate the weight update in \cref{eq:weight_update}.
 
@@
 
-[A change in the chosen weight of a memristor directly influences the functional form of $g_{\infty}(\boldsymbol{\Delta})$.
-In turn, this functional form guides the evolution toward a steady state that aligns with the desired one.
-It is important to note that the entire functional form is significant, not just the steady-state value of the potential drop and the corresponding conductance, as explained in Appendix A.] -> add in paper
+\section{Dynamical evolution to the steady state \label{app:dyn_evol_steady_state}}
 
-\section{Dynamical evolution to the steady state \label{app:dyn_evol_steady_state}}
-In this section, we explain more in depth the relaxation toward a steady-state of a memristor network.
-Specifically, we want to emphasise that in a network where the applied voltage is constant at the input nodes, the dynamical dependence on the steady-state conductance is fundamental to reach desired values of potential drops.
+In this section, we provide a more detailed explanation of how a memristor network relaxes to its steady state.
+Alongside outlining the algorithm used to solve the circuit, we highlight the importance of the dependence on the functional form of the steady-state conductance, which itself is determined by the values of the weights.
+Selecting appropriate weights shapes the  staedy-state conductance function in such a way that the network naturally relaxes to a steady state aligned with the training objective.
 
-For simplicity, we consider a voltage divider, as shown in \cref{fig:app_vd}, where we set $\Delta P = 0$ and $\Delta \rho = 0$. 
+For simplicity, we consider the voltage divider shown in \cref{fig:app_vd}, where the memristors are labeled as $ \m_1 $, connecting node 2 to node 1, and $ \m_2 $, connecting node 3 to node 2.
+We also denote the corresponding potential drops across each memristor as $ \Delta V_1 = V_2 - V_1$ and $ \Delta V_2  = V_3 - V_2$, respectively.
+To simplify, we set both the pressure difference ($ \Delta P $) and concentration difference ($ \Delta \rho $) to zero.
+In this example, we choose the channel length as the training weight.
+
 \begin{figure}[H]
@@
     \includegraphics[width=0.5\columnwidth]{plots/appendixA/app_vd.pdf}
-    \caption{}
+    \caption{Schematical representation of a memristor voltage divider.
+Two memristors, \( M_1 \) and \( M_2 \), connect two input nodes (green dots) with fixed voltages of \( 0\,\mathrm{V} \) and \( 5\,\mathrm{V} \), respectively, to a single output node (purple dot).
+Each memristor is subject to one external stimulus: the electric potential difference between the nodes it connects.
+    }
     \label{fig:app_vd}
 \end{figure} 
-Therefore, the dynamical evolution of the conductance of each memristor discretized in time-steps $\Delta t$, shown in its general form in Eq. (2), reduces to
+The dynamical evolution of the conductance of each memristor, discretized in time-steps of size $\Delta t$, reduces to the update rule:
 \begin{equation}
-    g_{\m}\brac{t + \Delta t} = g_{\m}\brac{t} +
-     \frac{g_{\m,\infty}\brac{\Delta V_{\m}(t)}-g_{\m}\brac{t}}{\tau}\Delta t,
+g_{\m}(t + \Delta t) = g_{\m}(t) +
+\frac{g_{\m,\infty}(\Delta V_{\m}(t)) - g_{\m}(t)}{\tau} \Delta t,
 \label{eq:conduct}
 \end{equation}
-with initial condition $g_{\m}(t=0)=g_0$. At each time-step, the potential drop $\Delta V_{m}(t)$ across each memristor is calculated using Kirchoff's law, that reduces to the expressions
+with initial condition $g_{\m}(t = 0) = g_0$.
+The potential drops across the memristors, $\Delta V_1(t)$ and $\Delta V_2(t)$, are computed from Kirchhoff's laws.
+In the case of a simple voltage divider ,see \cref{fig:app_vd}, these simplify to:
 \begin{equation}
-    \Delta V_1(t) = \frac{5 g_2(t)}{g_1(t)+g_2(t)}, \ \ \ \ \ \ \ \Delta V_2(t) = \frac{5 g_1(t)}{g_1(t)+g_2(t)},
+\Delta V_1(t) = \frac{5 g_2(t)}{g_1(t)+g_2(t)}, \qquad
+\Delta V_2(t) = \frac{5 g_1(t)}{g_1(t)+g_2(t)},
 \label{eq:potentials}
 \end{equation}
-found by minimizing the power dissipated by the resistances with respect to the free potential $\partial P/\partial V_2=0$.
 
-The algorithm works as follows:
+The simulation proceeds as follows:
 
 \begin{itemize}
+\item At $t = 0$, initialize: $g_1(0) = g_2(0) = g_0$.
+\item Compute $\Delta V_1(0)$ and $\Delta V_2(0)$ using \cref{eq:potentials}.
+\item Use \cref{eq:conduct} to update $g_1(\Delta t)$ and $g_2(\Delta t)$.
+\item Repeat the process at each time step until $|g_{\m}(t) - g_{\m,\infty}(t)| < \epsilon$ for all memristors.
+\end{itemize}
 
-    \item At time $t=0$, the potentials $\Delta V_1(t=0)$ and $\Delta V_2(t=0)$ are computed from \cref{eq:potentials} using the initial condition $g_1(t=0)=g_2(t=0)=g_0$.
-    \item In the following time-step $t=\Delta t$, the potentials $\Delta V_1(t=0)$ and $\Delta V_2(t=0)$ are used to compute conductances $g_{\m}(\Delta t)$ using \cref{eq:conduct}.
-    \item The previous step is iterated, and the system reaches the steady-state when $g_{\m}(t)=g_{\m,\infty}(t)$.
-
-\end{itemize}
+\begin{algorithm}
+    \caption{Relaxation of a Memristor Voltage Divider to Steady State}
+    \begin{algorithmic}[1]
+    \State \textbf{Input:} Initial conductance $g_0$, time step $\Delta t$, convergence threshold $\epsilon$, relaxation time $\tau$
+    \State Initialize $g_1 \gets g_0$, $g_2 \gets g_0$, $t \gets 0$
+    \While{not converged}
+        \State Compute $\Delta V_1 \gets \frac{5 \cdot g_2}{g_1 + g_2}$
+        \State Compute $\Delta V_2 \gets \frac{5 \cdot g_1}{g_1 + g_2}$
+        \State $g_1 \gets g_1 + \frac{g_{\infty}(\Delta V_1) - g_1}{\tau} \cdot \Delta t$
+        \State $g_2 \gets g_2 + \frac{g_{\infty}(\Delta V_2) - g_2}{\tau} \cdot \Delta t$
+        \If{$|g_1 - g_{\infty}(\Delta V_1)| < \epsilon$ \textbf{and} $|g_2 - g_{\infty}(\Delta V_2)| < \epsilon$}
+            \State \textbf{break}
+        \EndIf
+    \EndWhile
+    \end{algorithmic}
+\end{algorithm}
 

### 2025-05-28 codes/linear_regression.py

@@ -50,18 +50,18 @@ training_type = 'regression'    # choose
 
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
-learning_rate_vec = [1e-6, 1e-6, 1e-4, 2e2, 1e3]
-constant_source = [3, 3, 7, 3]
+learning_rate_vec = [5e-7, 1e-6, 7e-4, 2e2, 1e3]
+constant_source = [11, 4, 4, 11]
 
 weight_type_index = 0   # choose
 
-for weight_type_index in [2]:
+for weight_type_index in [0,1,3]:
     
     G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 #     G = nx.read_graphml(f'{DATA_PATH}G00050001.graphml')
 #     # G = nx.read_graphml(f'{DATA_PATH}G00010001.graphml')
 #     # G = nx.read_graphml(f'{DATA_PATH}G00010003.graphml')
-#     # G.nodes['3']['voltage'] = constant_source[weight_type_index]
+    G.nodes['3']['voltage'] = constant_source[weight_type_index]
 
     training.train(G, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index], save_final_graph=True, write_weights=True)
 
@@ -82,10 +82,9 @@ for weight_type_index in [2]:
     fig.savefig(f"{DATA_PATH}mse.pdf", transparent=True)
 
 #     # --------- TEST REGRESSION AND PLOT RESULT ---------
-
+    training_steps = 391
     training.test_regression(G, step=0, weight_type=f'{weight_type_vec[weight_type_index]}')
     training.test_regression(G, step=int(training_steps/2), weight_type=f'{weight_type_vec[weight_type_index]}')
-    # training.test_regression(G, step=50, weight_type=f'{weight_type_vec[weight_type_index]}')
     training.test_regression(G, step=training_steps, weight_type=f'{weight_type_vec[weight_type_index]}')
 
     fig, ax = plt.subplots(1, 3, figsize=(15,5))

### 2025-05-28 codes/parameters.py

@@ -48,8 +48,8 @@ memr_resistances_style = dict(marker = 'o', markersize=3, lw=1)
 regression_styles = {
     'length': dict(marker = 'o', s=5, c = cmap.colors[0], lw=0.6, label = rf'$L$'),
     'length_des': dict(c = 'lightpink', lw=2, label = rf'$V^D$'),
-    'rho': dict(marker = 'o', c = cmap.colors[1], lw=1, label = rf'$\rho$'),
-    'rho_des': dict(c = 'moccasin', lw=4, label = rf'$V^D$'),
+    'rho': dict(marker = 'o', s=5, c = cmap.colors[1], lw=1, label = rf'$\rho$'),
+    'rho_des': dict(c = 'moccasin', lw=2, label = rf'$V^D$'),
     'radius_base': dict(marker = 'o', c = cmap.colors[2], lw=1, label = rf'$R_b$'),
     'radius_base_des': dict(c = 'yellow', lw=4, label = rf'$V^D$'),
     'pressure': dict(marker = 'o', c = cmap.colors[3], lw=1, label = rf'$P$'),

### 2025-05-28 codes/plotting.py

@@ -215,11 +215,9 @@ def plot_final_potential_vd(ax, target_values):
 
 def plot_regression(ax, graph_id, weight_type, step):
     
-    data = np.loadtxt(f"{par.DATA_PATH}regression{graph_id}/relations_regression/relations_regression{step}.txt", unpack=True)
-    
+    data = np.loadtxt(f"{par.DATA_PATH}regression{graph_id}/relations_regression/relations_regression{weight_type}{step}.txt", unpack=True)
     x = data[0]
     y1 = data[1]
-    print(y1)
     
     x_interval = np.linspace(np.min(x),np.max(x))
     y1_desired = training.regression_function(x_interval)

### 2025-05-28 codes/regression_plots_paper.py

@@ -12,8 +12,13 @@ import matplotlib.gridspec as gridspec
 graph_id = 'G00010002'
 DATA_PATH = f'{par.DATA_PATH}regression{graph_id}/'
 G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
-training_steps = 400
+training_steps = 391
 training_type = 'regression'
+if graph_id == 'G00010002':
+    weight_type_regression = 'rho'
+else:
+    weight_type_regression = 'length'
+
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
 
@@ -32,15 +37,15 @@ ax2.legend(fontsize = par.legend_size)
 
 bottom = gridspec.GridSpecFromSubplotSpec(1, 3, subplot_spec=outer[1])
 ax3 = fig.add_subplot(bottom[0, 0])
-plotting.plot_regression(ax3, graph_id, 'length', step=0)
+plotting.plot_regression(ax3, graph_id, weight_type_regression, step=0)
 ax3.legend(fontsize = par.legend_size)
 
 ax4 = fig.add_subplot(bottom[0, 1])
-plotting.plot_regression(ax4, graph_id, 'length', int(50))
+plotting.plot_regression(ax4, graph_id, weight_type_regression, int(training_steps/2))
 ax4.legend(fontsize = par.legend_size)
 
 ax5 = fig.add_subplot(bottom[0, 2])
-plotting.plot_regression(ax5, graph_id, 'length', step=400)
+plotting.plot_regression(ax5, graph_id, weight_type_regression, step=training_steps)
 ax5.legend(fontsize = par.legend_size)
 
 
@@ -61,17 +66,18 @@ ax2.legend(fontsize=par.legend_size)
 
 # Add inset axes inside ax2
 inset_ax1 = ax2.inset_axes([0.07, 0.5, 0.2, 0.2])  # [x0, y0, width, height]
-plotting.plot_regression(inset_ax1, graph_id, 'length', step=0)
+plotting.plot_regression(inset_ax1, graph_id, weight_type_regression, step=0)
 # inset_ax1.set_title("Step 0", fontsize=(par.size_ticks-7))
 inset_ax1.tick_params(axis='both', labelsize=(par.size_ticks-7))
 
 inset_ax2 = ax2.inset_axes([0.55, 0.6, 0.2, 0.2])
-plotting.plot_regression(inset_ax2, graph_id, 'length', step=50)
[…]

### 2025-05-28 codes/training.py

@@ -625,7 +625,7 @@ def test_regression(G, step, weight_type):
         for index, edge in enumerate(G.edges):
             G.edges[edge][f'{weight_type}'] = weight_vec[index]
             
-    reg_file = open(f"{par.DATA_PATH}regression{G.graph['name']}/relations_regression/relations_regression{step}.txt", "w") 
+    reg_file = open(f"{par.DATA_PATH}regression{G.graph['name']}/relations_regression/relations_regression{weight_type}{step}.txt", "w") 
 
     counter_inputs = 0
     for node in G.nodes():

### 2025-05-28 paper/paper.tex
Finished appendix and made new regr graph style.

@@
 \end{equation}
-
-The simulation proceeds as follows:
-
-\begin{itemize}
-\item At $t = 0$, initialize: $g_1(0) = g_2(0) = g_0$.
-\item Compute $\Delta V_1(0)$ and $\Delta V_2(0)$ using \cref{eq:potentials}.
-\item Use \cref{eq:conduct} to update $g_1(\Delta t)$ and $g_2(\Delta t)$.
-\item Repeat the process at each time step until $|g_{\m}(t) - g_{\m,\infty}(t)| < \epsilon$ for all memristors.
-\end{itemize}
+Starting from initial values, the potential drops across the memristors are computed using Kirchhoff’s laws.
+These potential differences then drive the time evolution of the memristors’ conductances, following the discretized dynamical equation.
+The process—computing potential drops and updating conductances—is repeated iteratively until the conductance values converge to their steady-state counterparts.
+This iterative relaxation procedure is outlined in Algorithm 1.
 
 \begin{algorithm}
+    \label{alg:relaxation}
     \caption{Relaxation of a Memristor Voltage Divider to Steady State}
@@
 
+Since the initial conductance is the same, we have $\Delta V_1(0) = \Delta V_2(0) = 2.5\,\text{V}$.
+When the memristors' channels have the same length, their steady-state function $g_{\infty}$ is identical, as shown in \cref{fig:equal_memr}(a).
+As a consequence, their conductances will evolve according to \cref{eq:conduct} and \cref{eq:potentials}, remaining equal throughout the simulation, as depicted in \cref{fig:equal_memr}(b).
+This results in the same, constant potential difference across both memristors, as shown in \cref{fig:equal_memr}(c).
 \begin{figure}[h]
     \centering
-    \includegraphics[width=0.8\columnwidth]{plots/appendixA/grid_initial_condition.pdf}
-    \caption{Relaxation toward the steady
-    state when $g_{1,\infty}(V)=g_{2,\infty}(V)$.}
-    \label{fig:memristor_network}
+    \includegraphics[width=\columnwidth]{plots/appendixA/grid_initial_condition.pdf}
+    \caption{Relaxation toward the steady state of a memristor voltage divider when both memristors have the same length.
+(a) Steady-state conductance function of memristor $\m_1$ (light green solid line) and memristor $\m_2$ (light blue solid line).
+The steady-state conductance values reached upon convergence of \cref{eq:conduct} are indicated by a triangular marker for $\m_1$ and a circular marker for $\m_2$.
+(b) Time evolution of the conductance of memristor $\m_1$ (green) and $\m_2$ (light blue) during relaxation toward the steady state.
+The final conductance values are indicated by the same triangular and circular markers as in (a).
+(c) Voltages at the input nodes (green lines) and potential drops across the two memristors (light pink and purple lines) during relaxation.
+    }
+    \label{fig:equal_memr}
 \end{figure}
+
+Performing the training algorithm outlined in \cref{sec:training}, with the objective of setting the output voltage to $V_2 = 4\,\mathrm{V}$, results in specific values of the channel length for each memristor.
+Consequently, the steady-state conductance functions deviate from their original forms, as shown in \cref{fig:trained_memr}(a).
+These updated functions guide the evolution of the memristor conductances toward a steady state that satisfies the training objective, as illustrated in \cref{fig:trained_memr}(c).
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\columnwidth]{plots/appendixA/grid_trained.pdf}
+    \caption{Relaxation toward the steady state of a memristor voltage divider, where the memristor lengths have been set by a training algorithm with the objective of producing $V_2 = 4\,\mathrm{V}$.
+(a) Steady-state conductance functions of memristor $\m_1$ (light green solid line) and memristor $\m_2$ (light blue solid line).
+The conductance values reached upon convergence of \cref{eq:conduct} are indicated by a triangular marker for $\m_1$ and a circular marker for $\m_2$.
+(b) Time evolution of the conductance of memristor $\m_1$ (green) and $\m_2$ (light blue) during relaxation toward the steady state.
+Final conductance values are indicated by the same markers as in (a).
+(c) Voltages at the input nodes (green lines) and potential drops across the two memristors (light pink and purple lines) during relaxation.
+The potential drops reflect the trained voltage output at the middle node.
+    }
+    \label{fig:trained_memr}
+\end{figure}
+
+Once convergence is reached, the final conductance values corresponding to the desired potential drops across the two memristors can be read from \cref{fig:trained_memr}(b).
+However, knowing only these steady-state conductance values is not sufficient to guarantee relaxation to the desired final state.
+In fact, if one fixes those points on the $g_{\infty}$ curves while altering the functional form elsewhere, the system may converge to a different steady state, as demonstrated in \cref{fig:changed_func_ginfty}.
+
+This observation highlights that the complete functional form of $g_{\infty}$, which is determined by the trained weight parameter, is essential in the voltage range relevant to the system’s evolution.
+While the final steady-state conductances may be sufficient in a purely resistive network with tunable resistors, memristors differ in that their conductance is inherently dynamic and depends on the applied voltage.
+Therefore, to reliably achieve the desired steady state, control over the entire conductance function is necessary.
 
@@
     \centering
-    \includegraphics[width=0.8\columnwidth]{plots/appendixA/grid_trained.pdf}
-    \caption{Relaxation toward the steady state when the system has been trained to give $V_2 = 4V$. The training sets the two different functional forms of $g_{\infty}$ seen in the right figure.}
-    \label{fig:memristor_network}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.8\columnwidth]{plots/appendixA/grid_trained_change_func.pdf}
-    \caption{We consider the trained system in Figure 3, but we define the funtion $g_{1, \infty}$ such that it passes througth the steady state point (triangle in Figure 3), now indicated with a red cross, but with a different functional form.
-Due to the different functinal form, the system reaches a steady state that doesn't coincide with the desired in Figure 3.}
-    \label{fig:memristor_network}
+    \includegraphics[width=\columnwidth]{plots/appendixA/grid_trained_change_func.pdf}
+    \caption{Relaxation toward the steady state of a memristor voltage divider.
+The steady-state function of $\m_1$ is artificially modified to a sine curve that passes through the final conductance and potential drop point of the trained network (red cross), while the steady-state function of $\m_2$ is kept identical to that of the trained system.
+(a) Steady-state conductance functions of memristor $\m_1$ (light green solid line) and memristor $\m_2$ (light blue solid line).
+The conductance values reached upon convergence of \cref{eq:conduct} are indicated by a triangular marker for $\m_1$ and a circular marker for $\m_2$.
+(b) Time evolution of the conductance of memristor $\m_1$ (green) and $\m_2$ (light blue) during relaxation toward the steady state.
+Final conductance values are marked as in (a).
+(c) Voltages at the input nodes (green lines) and potential drops across the two memristors (light pink and purple lines) during relaxation.
+Due to the altered functional form of the steady-state conductance of $\m_1$, the evolution deviates from the desired one.
+    }
+    \label{fig:changed_func_ginfty}
 \end{figure}

### 2025-05-28 codes/linear_regression.py

@@ -50,12 +50,13 @@ training_type = 'regression'    # choose
 
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
-learning_rate_vec = [5e-7, 1e-6, 7e-4, 2e2, 1e3]
+# learning_rate_vec = [5e-7, 1e-6, 7e-4, 2e2, 1e3]
+learning_rate_vec = [3e-7, 1e-6, 9e-4, 2e2, 1e3]
 constant_source = [11, 4, 4, 11]
 
 weight_type_index = 0   # choose
 
-for weight_type_index in [0,1,3]:
+for weight_type_index in [2]:
     
     G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 #     G = nx.read_graphml(f'{DATA_PATH}G00050001.graphml')

### 2025-05-28 codes/plotting.py

@@ -75,7 +75,11 @@ def plot_mse(ax, fig, graph_id, training_type, weight_type, show_xlabel=True):
     ax.set_yscale('log')   
     
     # ax.legend(fontsize = par.legend_size)
-    ax.set_ylabel(r'$C(w)$', fontsize = par.axis_fontsize)
+    if training_type=='regression':
+        ax.set_ylabel(r'$C_{test}(w)$', fontsize = par.axis_fontsize)
+    else:
+        ax.set_ylabel(r'$C(w)$', fontsize = par.axis_fontsize)
+
     if show_xlabel:
         ax.set_xlabel(r'Training steps', fontsize = par.axis_fontsize)
     ax.tick_params(axis='both', labelsize=par.size_ticks)

### 2025-05-28 codes/regression_plots_paper.py

@@ -53,7 +53,7 @@ ax5.legend(fontsize = par.legend_size)
 fig.savefig(f"../paper/plots/regression/{graph_id}.pdf")
 
 
-fig = plt.figure(figsize=(13, 6.5), constrained_layout=True)
+fig = plt.figure(figsize=(13, 7), constrained_layout=True)
 outer = gridspec.GridSpec(1, 2, width_ratios=[1, 2], figure=fig)
 
 # Right column for MSE plot
@@ -65,18 +65,18 @@ plotting.plot_mse(ax2, fig, graph_id, training_type, 'pressure')
 ax2.legend(fontsize=par.legend_size)
 
 # Add inset axes inside ax2
-inset_ax1 = ax2.inset_axes([0.07, 0.5, 0.2, 0.2])  # [x0, y0, width, height]
+inset_ax1 = ax2.inset_axes([0.07, 0.4, 0.23, 0.23])  # [x0, y0, width, height]
 plotting.plot_regression(inset_ax1, graph_id, weight_type_regression, step=0)
 # inset_ax1.set_title("Step 0", fontsize=(par.size_ticks-7))
 inset_ax1.tick_params(axis='both', labelsize=(par.size_ticks-7))
 
-inset_ax2 = ax2.inset_axes([0.55, 0.6, 0.2, 0.2])
+inset_ax2 = ax2.inset_axes([0.6, 0.6, 0.23, 0.23])
 plotting.plot_regression(inset_ax2, graph_id, weight_type_regression, step=int(training_steps/2))
 print(int(training_steps/2))
 # inset_ax2.set_title("Step 50", fontsize=(par.size_ticks-7))
 inset_ax2.tick_params(axis='both', labelsize=(par.size_ticks-7))
 
-inset_ax3 = ax2.inset_axes([0.7, 0.1, 0.2, 0.2])
+inset_ax3 = ax2.inset_axes([0.25, 0.1, 0.23, 0.23])
 plotting.plot_regression(inset_ax3, graph_id, weight_type_regression, step=training_steps)
 # inset_ax3.set_title("Step 400", fontsize=(par.size_ticks-7))
 inset_ax3.tick_params(axis='both', labelsize=(par.size_ticks-7))

### 2025-06-02 paper/paper.tex
Uploaded data for plot reproducing local

@@
 Modern computing algortihms are able to efficiently perform complicated nuemrical and symbolic operations, but their sequential structure limits their performance on more perceptual tasks.
-Inspired by the architecture and the functioning of the human brain that performs tasks via distributed and parallel fashion, artificial neural network (ANN) algorithms outreached traditional computing achieving remarkable success in challenging tasks ranging from image recognition to natural language processing and became central to many technological advancements in the field of artificial intelligence.
+Inspired by the architecture and the functioning of the human brain, that performs tasks via distributed and parallel fashion, artificial neural network (ANN) algorithms outreached traditional computing achieving remarkable success in challenging tasks, such as visual and audio pattern recognition~\cite{pattern_recognition,review_image_rec, speech_rec} to natural language processing and became central to many technological advancements in the field of artificial intelligence\cite{ai_tech1}.
 
-Recent advances in AI systems have been powered by the silicon-based computing power of the Graphics Processing Units (GPUs) and by an unprecedented abundance of data.
-With a clear trend of larger ANN models, their the energy requirements have grown significantly, negatively impacting their efficiency and scalability\cite{energy_cost_ml1, energy_cost_ml2}.
-With the rapid increase in computation requirements of AI training and the slower improvemnts in computing hardware traditionally predicted by Moore's Law, the necessity of new computing paradigms became more relevant.
-As an alternative to ANN performed strictly in-silico, physical neural networks (PNN) have been introduced, where physical processes rather than mathematical operations are trained\cite{trainingphysicalneuralnetworks}.
-Since physical processes can be faster and more energetically efficient than their digital representation, this direction constitutes a promosing research direction to address this issue.
+Recent developments in artificial intelligence have been driven by the computational power of Graphics Processing Units and the availability of large amounts of data.
+However, as ANNs continue to grow in size and complexity, their energy demands have increased substantially, ultimately impacting their efficiency and limiting their scalability \cite{energy_cost_ml1, energy_cost_ml2}.
+Meanwhile, the gap between the accelerating computational needs of AI training and the gradual improvements in traditional silicon-based hardware, as historically described by Moore’s Law, has highlighted the need for innovative computing architectures.
+One promising alternative is the development of physical neural networks (PNNs), which train physical processes rather than relying solely on digital calculations \cite{trainingphysicalneuralnetworks,backporp_pnn}.
+Because physical systems can often achieve faster and more energy-efficient operations than their digital representations, this direction constitutes a promising research direction to address this issue.
 
-Applications of PNNs have been explored across diverse fields, including optics \cite{optics1}, electronics \cite{electronics1}, and fluidic and mechanical systems \cite{}, among others.
+Applications of PNNs have been explored across diverse fields, including optics \cite{optics1}, electronics \cite{electronics1}, photonics \cite{acoustic1} and mechanical systems \cite{mechanics1}, among others.
 Many existing training algorithms rely entirely on in silico methods, which often face challenges when transferring the learned model to real physical devices.
-To address this, hybrid training approaches have been proposed, where the inference phase is executed physically while the backward phase is computed numerically.
-Other methods, based on coupled learning, implement local learning rules at the level of each connection or edge.
+To address this, hybrid training approaches have been proposed, where the inference phase is executed physically while the backward phase is computed numerically\cite{backporp_pnn}.
+Other methods, based on coupled learning\cite{supervised_learning}, implement local learning rules at the level of each connection or edge\cite{demonstr_coupled_learning}.
+Applying local rules removed the need of the optimiziation of a global function during training, as in standard backpropagation methods.
 However, these approaches still face the need for two identical physical systems to apply different boundary conditions.
-In this work, we propose a novel algorithm in which both inference and backpropagation are carried out through physical processes, specifically leveraging the natural relaxation dynamics of the system in response to external stimuli and weight modifications.
+In this work, we propose a novel algorithm in which both inference and backpropagation are carried out mainly taking advantage of the physical processes inherent in the system, specifically leveraging the natural relaxation dynamics of the system in response to external stimuli and weight modifications.
 
 A key advantage of PNNs is their ability to more closely emulate certain functional aspects of biological neural systems.
-One of the defining features of the brain is its capacity to process and integrate multiple types of stimuli—such as electrical, chemical, and mechanical inputs—simultaneously.
+One of the defining features of the brain is its capacity to process and integrate multiple types of stimuli, such as electrical, chemical, and mechanical inputs, simultaneously.
 This multimodal responsiveness is believed to contribute significantly to the brain’s efficiency and adaptability \cite{}.
-Inspired by this, we focus on neural networks constructed from memristive elements.
-Specifically, we utilize ionic microfluidic channels in aqueous solutions\cite{Rene_IonicNeuromorphic}, which exhibit the unique ability to respond concurrently to diverse physical stimuli.
+Inspired by this functionality, we base our approach on physical neural networks constructed from memristive elements.
+Specifically, we utilize ionic microfluidic channels in aqueous solutions\cite{Rene_IonicNeuromorphic}, which exhibit the ability to respond concurrently to diverse physical stimuli.
 This characteristic is central to the operation of our proposed training algorithm.
@@
 The paper is organized as follows.
-Section 2 reviews related work on memristor networks, machine learning algorithms, and physical learning methods.
-Section 3 describes the methods used in our study, including the network model, machine learning algorithm, and the physical learning approach.
-In Section 4, we present our proposed method for coupling memristors with capacitors and discuss the necessary properties for effective training.
-Section 5 details our experimental setup and implementation.
-The results and analysis are provided in Section 6, followed by conclusions and suggestions for future work in Section 7.
+\cref{sec:memristor_network} presents the physical network we define using memristor elements, called memristor network, and explains how this system is numerically solved.
+\cref{sec:training} describes the training algorithm that we use to achieve desired responses of the memristor network.
+In \cref{sec:train_memr_vd}, we exemplify the proposed algorithm by training a simple system, namely a voltage divider.
+\cref{sec:train_memr_nw} s The results and analysis are provided in Section 6, followed by conclusions and suggestions for future work in Section 7.
 
@@
 
-\subsection{Training a Memristor Voltage Divider}
+\subsection{\label{sec:train_memr_vd}Training a Memristor Voltage Divider}
 
@@
 
-\subsection{Training a memristor network}
+\subsection{\label{sec:train_memr_nw}Training a memristor network}
 
@@
 % \cleardoublepage
-\subsection{Linear Regression}
+\subsection{\label{sec:linear_regression}Linear Regression}
 

### 2025-06-02 codes/linear_regression.py

@@ -10,21 +10,21 @@ import numpy as np
 
 start = time.time()
 
-graph_id = 'G00010001'
+graph_id = 'G00060001'
 DATA_PATH = f'{par.DATA_PATH}regression{graph_id}/'
 
 # --------- INITIALIZE NETWORK ---------
 
 # -> DEFINE graph from networks module
-# G = networks.random_graph(save_data=True) 
-# G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
-G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
+# G = networks.random_graph(number_edges=20, number_nodes=10, save_data=True) 
+G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
+# G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 
 # Using graphs:
 # regression_working: wokring nw for length not directed with 3V extra source
 # regression_working_rho: wokring nw for length directed with 6V extra source, working for rho training
 
-# print(G.edges())
+print(G.edges())
 # G.add_edge('1','7')
 # networks.initialize_edges(G)
 # G = networks.to_directed_graph(G, shuffle=True)
@@ -50,13 +50,13 @@ training_type = 'regression'    # choose
 
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
-# learning_rate_vec = [5e-7, 1e-6, 7e-4, 2e2, 1e3]
-learning_rate_vec = [3e-7, 1e-6, 9e-4, 2e2, 1e3]
-constant_source = [11, 4, 4, 11]
+# learning_rate_vec = [2e-7, 1e-6, 1e-4, 2e2, 1e3]
+learning_rate_vec = [5e-7, 1e-6, 9e-4, 2e2, 1e3]
+constant_source = [11, 4, 4, 4]
 
 weight_type_index = 0   # choose
 
-for weight_type_index in [0]:
+for weight_type_index in [0,1,2,3]:
     
     G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 #     G = nx.read_graphml(f'{DATA_PATH}G00050001.graphml')

### 2025-06-04 paper/paper.tex
Updated graphs in paper

@@
 Physical relaxation replaces the feedforward pass, while a combined physical-numerical gradient descent drives the backward pass.
-This approach enables tasks such as input-output voltage mapping and linear regression.
+This approach enables tasks such as input-output voltage mapping and linear regression with bias.
 \end{abstract}
@@
 
-Modern computing algortihms are able to efficiently perform complicated nuemrical and symbolic operations, but their sequential structure limits their performance on more perceptual tasks.
+Modern computing algorithms are able to efficiently perform complicated numerical and symbolic operations, but their sequential structure limits their performance on more perceptual tasks.
 Inspired by the architecture and the functioning of the human brain, that performs tasks via distributed and parallel fashion, artificial neural network (ANN) algorithms outreached traditional computing achieving remarkable success in challenging tasks, such as visual and audio pattern recognition~\cite{pattern_recognition,review_image_rec, speech_rec} to natural language processing and became central to many technological advancements in the field of artificial intelligence\cite{ai_tech1}.
@@
     \caption{A schematic representation of the conical fluidic memristor.
-A cone of lenght $L$, base radius $R_b$ and tip radius $R_t$ with charged surface connnects two bulk reservoirs of a 1:1 electrolyte in an acqueous solution.
+A cone of length $L$, base radius $R_b$ and tip radius $R_t$ with charged surface connects two bulk reservoirs of a 1:1 electrolyte in an aqueous solution.
 The bulk density in the base $\rho_b$ differs from the bulk density in the tip $\rho_t$.
 At the far side of the memristor, an electrical potential and pressure drop are applied.
-Overall, this results in a chemical, electrical and mechanical sensistive system.}\label{fig:memristor_scheme}
+Overall, this results in a chemical, electrical and mechanical sensitive system.}\label{fig:memristor_scheme}
 \end{figure} 
@@
 However, we consider only the pressure and potential contributions to the total fluid flow, $Q = Q_P + Q_V$, assuming the diffusive flow to be negligible.
-The resulting fluid flow generates non-trivial ion concentration profiles which, in turn, directly infulence the channel's conductance $g$.
+The resulting fluid flow generates non-trivial ion concentration profiles which, in turn, directly influence the channel's conductance $g$.
 %It has already been shown that, for $\Delta P = 0$, the channel shows current rectification, thus working as a diode \cite{}, due to concentration polarization.
@@
 
-When the external stimuli vary dynamically in time, they generate ion accumulation and deplition in the channel, changing consequently the conductivity.
+When the external stimuli vary dynamically in time, they generate ion accumulation and depletion in the channel, changing consequently the conductivity.
 We assume the dynamics of the time-dependent conductance $g(t)$ as a single exponential decay towards the steady-state conductance $g_{\infty}$ with a diffusion-like timescale $\tau = L^2/12D$, as in Ref.
@@
     \caption{An example of a network of five nodes connected by six memristors.
-The nodes are divided in input nodes (green circles), hidden nodes (gray nodes) and output nodes (purple circles) each of them is characterized by a triplet of physical quantities, representing the potential, pressure, and density.
-Th resulting stimuli on the memristor is given by the difference between base and tip signal, it thus depends on the oreintation of the memristor.
-In the case of the memristor that connects the first and the second node, for example, the exteranl stimuli are $\Delta V = V_2 - V_1$, $\Delta P = P_2 - P_1$ and $\Delta \rho = \rho_2 - \rho_1$.
+The nodes are divided in input nodes (green circles), hidden nodes (grey nodes) and output nodes (purple circles) each of them is characterized by a triplet of physical quantities, representing the potential, pressure, and density.
+Th resulting stimuli on the memristor is given by the difference between base and tip signal, it thus depends on the orientation of the memristor.
+In the case of the memristor that connects the first and the second node, for example, the external stimuli are $\Delta V = V_2 - V_1$, $\Delta P = P_2 - P_1$ and $\Delta \rho = \rho_2 - \rho_1$.
 The zig-zag lines directed towards the input nodes indicate where the electrical signal is applied, while the zig-zag lines pointing outwards from the nodes indicate where the electrical signal is measured.}
@@
 In contrast, pressure and density are externally imposed at each node and do not propagate through the network.
-The set of nodes is divided in thee sets.
-A node belongs to the set of \textit{input nodes} if it is used to imput current in the circuit, its value of voltage is known and fixed.
-After the imputs are imposed, the electrical signal travels throught the network and the resulting output potential is read in the nodes belonging to \textit{output nodes}.
+The set of nodes is divided in three sets.
+A node belongs to the set of \textit{input nodes} if it is used to input current in the circuit, its value of voltage is known and fixed.
+After the inputs are imposed, the electrical signal travels through the network and the resulting output potential is read in the nodes belonging to \textit{output nodes}.
 The remaining nodes, that do not function as input or output, are included in the set of \textit{hidden nodes}.
@@
 The nodes in the PNN are connected by $\M$ memristive elements.
-Consequently, a memristor connecting two nodes experinces potential drop, pressure drop and concentration gradient given by the difference between the node where the base of the memristor is connected to, and the node to which the tip is linked.
-The memristor is characterized by its conductance state $g_{\m}$ with $\m\in[1,\M]$, consequence of both the geomtery parameters and the external stimuli.
+Consequently, a memristor connecting two nodes experiences potential drop, pressure drop and concentration gradient given by the difference between the node where the base of the memristor is connected to, and the node to which the tip is linked.
+The memristor is characterized by its conductance state $g_{\m}$ with $\m\in[1,\M]$, consequence of both the geometry parameters and the external stimuli.
 
@@
 To incorporate the memristive elements, we approximate the time evolution of the conductances using a discretized form of \cref{eq:eqofmotconductance}, employing the Euler-forward method.
-Specifically, the conductance at a given timestep is calculated from its value at the previous timestep as:
+Specifically, the conductance at a given time-step is calculated from its value at the previous time-step as:
 \begin{multline}
@@
 We developed a training algorithm that makes use of the physical dependencies of memristor conductivity on both external stimuli and geometric properties to implement a physical neural network.
-These dependencies allow us to interpret such physical parameters as tunable weights, analogous to standard artificial neural networks, and to encode learning directly into the physical structure of the system.
+These dependencies allow us to interpret such physical parameters as tuneable weights, analogous to standard artificial neural networks, and to encode learning directly into the physical structure of the system.
 As in traditional ANNs, the goal of the training algorithm is to modify these weights so that the network maps a given set of inputs to a corresponding set of desired outputs.
@@
 
-A modification to any of these weights affects the network's behavior by altering the functional form of the memristor’s steady-state conductance, $g_{\infty}(\boldsymbol{\Delta})$, which depends on the local potential, pressure, and concentration drops across the device.
+A modification to any of these weights affects the network's behaviour by altering the functional form of the memristor’s steady-state conductance, $g_{\infty}(\boldsymbol{\Delta})$, which depends on the local potential, pressure, and concentration drops across the device.
 Importantly, the \emph{entire functional shape} of $g_{\infty}$ plays a role in determining the network’s dynamics and ultimate steady state, as illustrated in \cref{app:dyn_evol_steady_state}.
@@
     \includegraphics[width=\textwidth]{plots/training/training_scheme.pdf}
-    \caption{Scheme representing the two phases of the training algorithm, they are iteraitvely performed for a selected number of training steps.}
+    \caption{Scheme representing the two phases of the training algorithm, they are iteratively performed for a selected number of training steps.}
     \label{fig:training_scheme}
@@
 \]
-where $\Lambda$ represents the set of indeces belonging to the output nodes, $V_i\brac{\boldsymbol{w}}$ the voltage measured on the output nodes and $V^D$ is a vector containing the values of desired output nodes.
+where $\Lambda$ represents the set of indices belonging to the output nodes, $V_i\brac{\boldsymbol{w}}$ the voltage measured on the output nodes and $V^D$ is a vector containing the values of desired output nodes.
 
@@
 \end{equation}
-results in a decrease in the cost funtion until a minimum is reached, for sufficienlty small values of $\alpha$ \cite{steepest_descent_book}.
+results in a decrease in the cost function until a minimum is reached, for sufficiently small values of $\alpha$ \cite{steepest_descent_book}.
 The gradient in the update rule is computed using a \textit{finite differences method}
@@
 
-In the training algortihm, we first initialize the system with the memristor parameters specified in \cref{sec:memristor_network}, an initial pressure of $1bar$ and concentration of $0.2mM$ at each node.
-With the knowledge of input and desired output voltage values, it is possible to performe the first forward pass, from which we obtain the cost function $C\brac{\boldsymbol{w}}$, that we store since it is needed in the computation its gradient.
+In the training algorithm, we first initialize the system with the memristor parameters specified in \cref{sec:memristor_network}, an initial pressure of $1bar$ and concentration of $0.2mM$ at each node.
+With the knowledge of input and desired output voltage values, it is possible to perform the first forward pass, from which we obtain the cost function $C\brac{\boldsymbol{w}}$, that we store since it is needed in the computation its gradient.
 Subsequently, we proceed with the backward pass.
@@
 
-Althought performed numerically in this work, we highlight that the feedforward pass is a physical process in which the system natually relaxes to its steady state.
+Although performed numerically in this work, we highlight that the feedforward pass is a physical process in which the system naturally relaxes to its steady state.
 Moreover, also the backward pass we use can be translated to a physical event since involves performing the forward pass a number of time as the number of the weights.
-Once the gradient of the cost function is determined and stored, only the simple algebric calculations of \cref{eq:weight_update} are left to be computed.
-We propose this method as a hybrid physical and in-silico training algorithm, as a future experimental approach to the probelm.
+Once the gradient of the cost function is determined and stored, only the simple algebraic calculations of \cref{eq:weight_update} are left to be computed.
+We propose this method as a hybrid physical and in-silico training algorithm, as a future experimental approach to the problem.
 
@@
 
-We initialize the system with pressures $P_1 =  P_2 = 1 bar$ and ion concetration $\rho_1 = \rho_2 = 0.2 mM$ on each node, length $L_1 = L_2 = 10\mu m$ and base radius  $R_{b1} = R_{b2} = 200 nm$ on each edge.
-After choosing one of these four physical quantities as training parameter $\boldsymbol{w} = \brac{w_1, w_2}$, we implement the training as descibed in \cref{sec:training} that modifies them, while the other parameters are kept constant.
-In \cref{fig:mse_weights_vd} we show that the cost function normalized to its initial value decreases of many order of magnitude during the training for each of the choosen weight.
-The values of the choosen set of weights simultaneouly changes from the initial condition, as shown in Figures [], adjusting the behaviour of the network to the desired one.
-If the values of a choosen type of weight at the end of the training are imposed to the netowork together with the voltage inputs, the network will autonomously realx to a staedy state that coincides with the desired state.
+We initialize the system with pressures $P_1 =  P_2 = 1 bar$ and ion concentration $\rho_1 = \rho_2 = 0.2 mM$ on each node, length $L_1 = L_2 = 10\mu m$ and base radius  $R_{b1} = R_{b2} = 200 nm$ on each edge.
+After choosing one of these four physical quantities as training parameter $\boldsymbol{w} = \brac{w_1, w_2}$, we implement the training as described in \cref{sec:training} that modifies them, while the other parameters are kept constant.
+In \cref{fig:mse_weights_vd} we show that the cost function normalized to its initial value decreases of many order of magnitude during the training for each of the chosen weight.
+The values of the chosen set of weights simultaneously changes from the initial condition, as shown in Figures [], adjusting the behaviour of the network to the desired one.
+If the values of a chosen type of weight at the end of the training are imposed to the network together with the voltage inputs, the network will autonomously relax to a steady state that coincides with the desired state.
 To exemplify this point, the inset in Figure shows the physical relaxation of the voltage divider when the trained values of pressure, which correspond to the three values in the last training step, are imposed on the nodes together with the constant inputs voltages.
@@
     \caption{(a) Behaviour of the cost function during the training of the voltage divider.
-Different colors indicate that the training is done with a specific choise of training weights, as indiacted in the legend.
+Different colors indicate that the training is done with a specific choice of training weights, as indicated in the legend.
 (b) Pressures imposed on the three nodes of the voltage divider during training.
 The inset shows the relaxation to the steady state of the output voltage $V_2$ to the desired value $V_D$ when the pressures imposed are the values obtained in the last training step, and the input nodes are stimulated with fixed voltage.
-(c) Ion concentration desnities imposed on the three nodes of the voltage divider during training.
+(c) Ion concentration densities imposed on the three nodes of the voltage divider during training.
 (d) Length of the memristors during training.
@@
 In order to investigate the adaptability of the algorithm, we trained the system with a set of three consequent desired voltages $V_D=\{1V, 3V, 4V\}$.
-In \cref{fig:evolution_targets} we show how the output voltgage $V_2$ subsequently adapts to the desired voltages during the training of the pressures in the nodes, the evolution of which can be seen in \cref{fig:evolution_targets}.
+In \cref{fig:evolution_targets} we show how the output voltage $V_2$ subsequently adapts to the desired voltages during the training of the pressures in the nodes, the evolution of which can be seen in \cref{fig:evolution_targets}.
 It is evident that the system can be retrained at any stage to a new desired objective making it reusable.
@@
     \includegraphics[width=0.8\columnwidth]{plots/voltage_divider/evolution_targets.pdf}
-    \caption{(a) The trainiang of a memristor voltage divider to a set of desired voltage outputs $V_D = {1V, 3V, 4V}$, indicated by dashed light purple lines.
+    \caption{(a) The training of a memristor voltage divider to a set of desired voltage outputs $V_D = {1V, 3V, 4V}$, indicated by dashed light purple lines.
 The output voltage $V_2$, indicated by dark purple dots, adapts to the desired output during the training.
 The input voltages $V_1$ and $V_3$ are constant at $5V$ and $0V$ respectively.
-(b) The dots with different shades of gray show the values of pressures, chosen as weights, imposed on the three nodes during training.}\label{fig:evolution_targets}
+(b) The dots with different shades of grey show the values of pressures, chosen as weights, imposed on the three nodes during training.}\label{fig:evolution_targets}
 \end{figure}
@@
 The network is trained to produce output voltages of $[3,V, 4,V]$ when provided with input voltages of $[0,V, 2,V, 5,V]$.
-Reaching a desired input-output voltage mapping in a generic electric circuit can be useful for variuous electronic purpuses \cite{voltage_controlled_oscillator, onchip_powerdistributed}.
+Reaching a desired input-output voltage mapping in a generic electric circuit can be useful for various electronic purposes \cite{voltage_controlled_oscillator, onchip_powerdistributed}.
 
@@
     \includegraphics[width=0.5\textwidth]{plots/general_network/mse_general.pdf}
-    \caption{(a) Generic network with $9$ nodes and $15$ edges with inputs $[V_{2}, V_{4}, V_{9}] = [0V, 2V, 5V]$ and desired outputs $[V_{5}^D, V_{7}^D] = [3V, 4V]$, delta weights a third of their intial value and learning rates $[0.001, 1, 0.0001, 0.001]$.
-(b) Cost funtion during training of generic graph for input-output mapping task.
+    \caption{(a) Generic network with $9$ nodes and $15$ edges with inputs $[V_{2}, V_{4}, V_{9}] = [0V, 2V, 5V]$ and desired outputs $[V_{5}^D, V_{7}^D] = [3V, 4V]$, delta weights a third of their initial value and learning rates $[0.001, 1, 0.0001, 0.001]$.
+(b) Cost function during training of generic graph for input-output mapping task.
 The different colors indicate different weight choice.}\label{fig:mse_general}
@@
 
-The result of the training is presented in \cref{fig:mse_general}(b), which shows how the cost function responds to the wieght updates performed in the algorithm, for each of the four different weights.
+The result of the training is presented in \cref{fig:mse_general}(b), which shows how the cost function responds to the weight updates performed in the algorithm, for each of the four different weights.
 All of the possible different choices of weight result in a trained set that decreases the initial error of many orders of magnitudes.
@@
 \subsection{\label{sec:linear_regression}Linear Regression}
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{plots/regression/regression_G00010001.pdf}
+    \caption{}\label{fig:lin_regr1}
+\end{figure*}
 
@@
 The performance of the algorithm on this task is shown in \cref{fig:lin_regr2}(b), where the learning rates for the different weights have been fine-tuned to prevent overshooting while still maintaining comparable convergence speed.
-From the behavior of the cost function, it is evident that the choice of weight type has a decisive impact on the network’s ability to learn a complex task.
-Specifically, training the lengths of the channles on the edges results in successful convergence, whereas training the node pressures proves to be extremely inefficient.
+From the behaviour of the cost function, it is evident that the choice of weight type has a decisive impact on the network’s ability to learn a complex task.
+Specifically, training the lengths of the channels on the edges results in successful convergence, whereas training the node pressures proves to be extremely inefficient.
 For a visual interpretation of the regression cost function, \cref{fig:lin_regr1}(c) shows the state of the training at three different time steps.
-
-\begin{figure}[h]
+\begin{figure*}[t]
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/regression/G00010001.pdf}
-    \caption{}\label{fig:lin_regr1}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.5\textwidth]{plots/regression/G00010002.pdf}
+    \includegraphics[width=\textwidth]{plots/regression/regression_G00010002.pdf}
     \caption{}\label{fig:lin_regr2}
-\end{figure}
+\end{figure*}
 
@@
 
-This modification significantly affects the behavior of the network.
+This modification significantly affects the behaviour of the network.
 As shown in \cref{fig:lin_regr2}(b), the new orientation alters the trainability of different weight types: in this configuration, training node concentration leads to better performance, while training edge length becomes less efficient.
@@
 Bigger networks have more degrees of freedom, and should allow for a bigger range of exploration of a solution.
-However, the experimantal realization would become more challenging.
-In this work, we show that an adequate geometry for a specific training goal can be sufficent to make a small network trainable.
-A deper analysis on the influence of geometry on the trainabiliy is needed in the research contest of physical learning and can be explored in future research.
+However, the experimental realization would become more challenging.
+In this work, we show that an adequate geometry for a specific training goal can be sufficient to make a small network trainable.
+A deeper analysis on the influence of geometry on the trainability is needed in the research contest of physical learning and can be explored in future research.
 
@@
 In the second phase, the update phase, the weights are adjusted to minimize a cost function based on the difference between the actual and desired outputs.
-By iteratively applying this procedure, the network is gradually tuned to achieve the desired input-output behavior.
+By iteratively applying this procedure, the network is gradually tuned to achieve the desired input-output behaviour.
 
@@
 Alongside outlining the algorithm used to solve the circuit, we highlight the importance of the dependence on the functional form of the steady-state conductance, which itself is determined by the values of the weights.
-Selecting appropriate weights shapes the  staedy-state conductance function in such a way that the network naturally relaxes to a steady state aligned with the training objective.
+Selecting appropriate weights shapes the staedy state conductance function in such a way that the network naturally relaxes to a steady state aligned with the training objective.
 
@@
 \begin{algorithm}
+    \caption{Relaxation of a Memristor Voltage Divider to Steady State}
     \label{alg:relaxation}
-    \caption{Relaxation of a Memristor Voltage Divider to Steady State}
     \begin{algorithmic}[1]
@@
 This observation highlights that the complete functional form of $g_{\infty}$, which is determined by the trained weight parameter, is essential in the voltage range relevant to the system’s evolution.
-While the final steady-state conductances may be sufficient in a purely resistive network with tunable resistors, memristors differ in that their conductance is inherently dynamic and depends on the applied voltage.
+While the final steady-state conductances may be sufficient in a purely resistive network with tuneable resistors, memristors differ in that their conductance is inherently dynamic and depends on the applied voltage.
 Therefore, to reliably achieve the desired steady state, control over the entire conductance function is necessary.

### 2025-06-04 codes/linear_regression.py

@@ -10,15 +10,15 @@ import numpy as np
 
 start = time.time()
 
-graph_id = 'G00060001'
+graph_id = 'G00010002'
 DATA_PATH = f'{par.DATA_PATH}regression{graph_id}/'
 
 # --------- INITIALIZE NETWORK ---------
 
 # -> DEFINE graph from networks module
 # G = networks.random_graph(number_edges=20, number_nodes=10, save_data=True) 
-G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
-# G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
+# G = nx.read_graphml(f'{par.DATA_PATH}random_graph.graphml')
+G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 
 # Using graphs:
 # regression_working: wokring nw for length not directed with 3V extra source
@@ -56,7 +56,7 @@ constant_source = [11, 4, 4, 4]
 
 weight_type_index = 0   # choose
 
-for weight_type_index in [0,1,2,3]:
+for weight_type_index in [2]:
     
     G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 #     G = nx.read_graphml(f'{DATA_PATH}G00050001.graphml')
@@ -64,7 +64,7 @@ for weight_type_index in [0,1,2,3]:
 #     # G = nx.read_graphml(f'{DATA_PATH}G00010003.graphml')
     G.nodes['3']['voltage'] = constant_source[weight_type_index]
 
-    training.train(G, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index], save_final_graph=True, write_weights=True)
+    # training.train(G, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index], save_final_graph=True, write_weights=True)
 
 #     # --------- PLOT ERROR, WEIGHTS & RESISTANCE ---------
 

### 2025-06-04 codes/parameters.py

@@ -46,9 +46,9 @@ memr_resistances_style = dict(marker = 'o', markersize=3, lw=1)
 # REGRESSION TRAINING
 
 regression_styles = {
-    'length': dict(marker = 'o', s=5, c = cmap.colors[0], lw=0.6),
+    'length': dict(marker = 'o', s=12, c = cmap.colors[0], lw=0.6),
     'length_des': dict(c = 'lightpink', lw=2, label = rf'$V^D$'),
-    'rho': dict(marker = 'o', s=5, c = cmap.colors[1], lw=1,),
+    'rho': dict(marker = 'o', s=12, c = cmap.colors[1], lw=1,),
     'rho_des': dict(c = 'moccasin', lw=2, label = rf'$V^D$'),
     'radius_base': dict(marker = 'o', c = cmap.colors[2], lw=1, label = rf'$R_b$'),
     'radius_base_des': dict(c = 'yellow', lw=4, label = rf'$V^D$'),

### 2025-06-04 codes/regression_plots_paper.py

@@ -53,36 +53,36 @@ ax5.legend(fontsize = par.legend_size)
 fig.savefig(f"../paper/plots/regression/{graph_id}.pdf")
 
 
-fig = plt.figure(figsize=(13, 7), constrained_layout=True)
-outer = gridspec.GridSpec(1, 2, width_ratios=[1, 2], figure=fig)
+fig, ax2 = plt.subplots(figsize=(11, 8), constrained_layout=True)
+# outer = gridspec.GridSpec(1, 2, width_ratios=[1, 2], figure=fig)
 
 # Right column for MSE plot
-ax2 = fig.add_subplot(outer[0, 1])
+# ax2 = fig.add_subplot(outer[0, 1])
 plotting.plot_mse(ax2, fig, graph_id, training_type, 'length')
 plotting.plot_mse(ax2, fig, graph_id, training_type, 'radius_base')
 plotting.plot_mse(ax2, fig, graph_id, training_type, 'rho')
 plotting.plot_mse(ax2, fig, graph_id, training_type, 'pressure')
-ax2.legend(fontsize=par.legend_size)
+ax2.legend(fontsize=par.legend_size, loc = 'upper right')
 
 # Add inset axes inside ax2
-inset_ax1 = ax2.inset_axes([0.07, 0.4, 0.23, 0.23])  # [x0, y0, width, height]
+inset_ax1 = ax2.inset_axes([0.06, 0.25, 0.23, 0.23])  # G00010002
+# inset_ax1 = ax2.inset_axes([0.065, 0.3, 0.23, 0.23])  # G00010001
 plotting.plot_regression(inset_ax1, graph_id, weight_type_regression, step=0)
-# inset_ax1.set_title("Step 0", fontsize=(par.size_ticks-7))
 inset_ax1.tick_params(axis='both', labelsize=(par.size_ticks-7))
 inset_ax1.legend(fontsize=(par.legend_size-4))
 
 
-inset_ax2 = ax2.inset_axes([0.6, 0.6, 0.23, 0.23])
-plotting.plot_regression(inset_ax2, graph_id, weight_type_regression, step=int(training_steps/2))
-print(int(training_steps/2))
-# inset_ax2.set_title("Step 50", fontsize=(par.size_ticks-7))
-inset_ax2.tick_params(axis='both', labelsize=(par.size_ticks-7))
-inset_ax2.legend(fontsize=(par.legend_size-4))
[…]

### 2025-06-05 paper/paper.tex
New geometry working

@@
 \usepackage{orcidlink}
-\usepackage{natbib}
+% \usepackage{natbib}
 \usepackage{amsmath}
@@
 \cref{sec:training} describes the training algorithm that we use to achieve desired responses of the memristor network.
-In \cref{sec:train_memr_vd}, we exemplify the proposed algorithm by training a simple system, namely a voltage divider.
-\cref{sec:train_memr_nw} s The results and analysis are provided in Section 6, followed by conclusions and suggestions for future work in Section 7.
+In \cref{sec:train_memr_vd}, we exemplify the proposed algorithm by training a simple system, namely a voltage divider, for input-output voltage mapping.
+\cref{sec:train_memr_nw} shows a bigger network able to be trained for more complex input-output relationships.
+Finally, in \cref{sec:linear_regression} we adapt the training algorthm to train a network to perform a linear regression with bias.
+This section is followed by conclusions and suggestions for future work in \cref{sec:concl}.
 
@@
 \end{figure} 
-An azimuthally symmetric conical channel connects two reservoirs that contain an incompressible aqueous 1:1 electrolyte with viscosity $\eta=1.01mPa s$ containing ions with diffusion coefficients $D = 1.75\mu m^2 ms^{-1}$ and charge $\pm e$, with $e$ the proton charge.
+An azimuthally symmetric conical channel connects two reservoirs that contain an incompressible aqueous 1:1 electrolyte with viscosity $\eta=1.0$1mPa s and electric permittivity $\epsilon = 0.71$nF$\text{m}^{-1}$ containing ions with diffusion coefficient $D = 1.75\mu \text{m}^2 \text{ms}^{-1}$ and charge $\pm e$, with $e$ the proton charge.
 The cone has a base radius of $R_b = 200$nm, a tip radius of $R_t=50$nm and has length $L = 10\mu$m, which sets it in the long channel limit, where entrance and exit effects can be neglected.
@@
 The PNN is composed of $\N$ nodes, an example is shown in \cref{fig:memristor_network}. 
-\begin{figure}[h]
+\begin{figure}[t]
     \centering
-    \includegraphics[width=0.8\columnwidth]{plots/memristor/memristor_network.pdf}
+    \includegraphics[width=0.6\columnwidth]{plots/memristor/memristor_network.pdf}
     \caption{An example of a network of five nodes connected by six memristors.
@@
 The memristor is characterized by its conductance state $g_{\m}$ with $\m\in[1,\M]$, consequence of both the geometry parameters and the external stimuli.
-
 To solve numerically the resulting circuit, it is necessary to simultaneously address the circuit equations and the time evolution equation for the memristors' conductance. 
@@
 \section{\label{sec:training}Training Algorithm for a Memristor Network}
-
-We developed a training algorithm that makes use of the physical dependencies of memristor conductivity on both external stimuli and geometric properties to implement a physical neural network.
-These dependencies allow us to interpret such physical parameters as tuneable weights, analogous to standard artificial neural networks, and to encode learning directly into the physical structure of the system.
-As in traditional ANNs, the goal of the training algorithm is to modify these weights so that the network maps a given set of inputs to a corresponding set of desired outputs.
-In the case of the memristor network considered here, training aims to produce specific voltage values at designated output nodes, given fixed voltage inputs at the input nodes.
-\begin{figure}[!h]
+\begin{figure}[b]
     \centering
@@
 \end{figure} 
+\begin{figure*}[t] 
+    \centering
+    \includegraphics[width=\textwidth]{plots/training/training_scheme.pdf}
+    \caption{Scheme representing the two phases of the training algorithm, they are iteratively performed for a selected number of training steps.}
+    \label{fig:training_scheme}
+\end{figure*}
+We developed a training algorithm that makes use of the physical dependencies of memristor conductivity on both external stimuli and geometric properties to implement a physical neural network.
+These dependencies allow us to interpret such physical parameters as tuneable weights, analogous to standard artificial neural networks, and to encode learning directly into the physical structure of the system.
+As in traditional ANNs, the goal of the training algorithm is to modify these weights so that the network maps a given set of inputs to a corresponding set of desired outputs.
+In the case of the memristor network considered here, training aims to produce specific voltage values at designated output nodes, given fixed voltage inputs at the input nodes.
+
 Crucially, the physical quantities that influence memristor conductance fall into two distinct categories: external stimuli, such as pressure or concentration, that are applied to the nodes, and geometric parameters, such as channel length or base radius, that are defined on the edges.
@@
 The training process is carried out by iterating a scheme, illustrated in \cref{fig:training_scheme}, which consists of two phases: a forward pass and a backward pass.
+
 \begin{figure*}[t]
     \centering
-    \includegraphics[width=\textwidth]{plots/training/training_scheme.pdf}
-    \caption{Scheme representing the two phases of the training algorithm, they are iteratively performed for a selected number of training steps.}
-    \label{fig:training_scheme}
+    \includegraphics[width=1.7\columnwidth]{plots/voltage_divider/mse_weights_vd.pdf}
+    \caption{(a) Behaviour of the cost function during the training of the memristor voltage divider.
+Different colors indicate that the training is done with a specific choice of training weights, as indicated in the legend.
+Learning rates are set to $[3\cdot 10^{-6}, 3\cdot 10^{-6}, 5\cdot 10^{-4}, 100]$.
+(b) Pressures imposed on the three nodes of the voltage divider during training.
+The inset shows the relaxation to the steady state of the output voltage $V_2$ to the desired value $V_D$ when the pressures imposed are the values obtained in the last training step, and the input nodes are stimulated with fixed voltage.
+(c) Ion concentration densities imposed on the three nodes of the voltage divider during training.
+(d) Length of the memristors during training.
+(e) Base radius of the memristors during training.}\label{fig:mse_weights_vd}
 \end{figure*} 
@@
 \end{equation}
-results in a decrease in the cost function until a minimum is reached, for sufficiently small values of $\alpha$ \cite{steepest_descent_book}.
-The gradient in the update rule is computed using a \textit{finite differences method}
+results in a decrease in the cost function until a minimum is reached, for sufficiently small values of $\alpha$ \cite{steepest_descent_book}. The gradient in the update rule
 \begin{equation}
-\boldsymbol{\nabla}C\brac{\boldsymbol{w}} = \frac{C\brac{\boldsymbol{w}+\boldsymbol{\Delta w}}-C\brac{\boldsymbol{w}}}{\Delta w},
+    \boldsymbol{\nabla}C\brac{\boldsymbol{w}} = \left[ \frac{\partial C(\boldsymbol{w})}{\partial w_1}, \dots, \frac{C(\boldsymbol{w})}{\partial w_M}  \right],
     \label{eq:gradient_cost_func}
 \end{equation}
-where $\boldsymbol{\Delta w}$ is a vector with the same number of entries as the weight vector, but every entry has a value $\Delta w$.
+is computed using a \textit{finite differences method} for each $m$ component
+\begin{equation}
+\frac{C(\boldsymbol{w})}{\partial w_m} = \frac{C\brac{w_1, \dots, w_m +\Delta w, \dots, w_M}-C\brac{\boldsymbol{w}}}{\Delta w},
+\label{eq:gradient_cost_func_comp}
+\end{equation}
+where $\Delta w$ is a small increment, that we always set such that $w_m(t=0)/\Delta w = 10^{3}$.
 
-In the training algorithm, we first initialize the system with the memristor parameters specified in \cref{sec:memristor_network}, an initial pressure of $1bar$ and concentration of $0.2mM$ at each node.
+In the training algorithm, we first initialize the system with the memristor parameters specified in \cref{sec:memristor_network}, an initial pressure of $1\text{bar}$ and concentration of $0.2\text{mM}$ at each node.
 With the knowledge of input and desired output voltage values, it is possible to perform the first forward pass, from which we obtain the cost function $C\brac{\boldsymbol{w}}$, that we store since it is needed in the computation its gradient.
 Subsequently, we proceed with the backward pass.
-We compute each entry of the gradient in \cref{eq:gradient_cost_func} by selecting the corresponding weight, a node or an edge parameter, increment its value of $\Delta w$ and applying a forward step to obtain the corresponding entry of $C\brac{\boldsymbol{w}+\boldsymbol{\Delta w}}$.
-With the stored value of $C\brac{\boldsymbol{w}}$, we are able to compute the gradient in \cref{eq:gradient_cost_func} and use it to calculate the weight update in \cref{eq:weight_update}.
+We compute each entry of the gradient in \cref{eq:gradient_cost_func} by selecting the corresponding weight, a node or an edge parameter, increment its value of $\Delta w$ and applying a forward step to obtain the corresponding entry of $C\brac{w_1, \dots, w_m +\Delta w, \dots, w_M}$.
+With the stored value of $C\brac{\boldsymbol{w}}$, we are able to compute the component of the gradient as in \cref{eq:gradient_cost_func_comp}, and use the gradient to calculate the weight update in \cref{eq:weight_update}.
 
@@
 \subsection{\label{sec:train_memr_vd}Training a Memristor Voltage Divider}
-
 A voltage divider is an electrical circuit made of three nodes connected in series by two resistances, that returns a fraction of the input voltage.
@@
 In \cref{fig:vd_scheme} a schematic of the memristor voltage divider is shown.
-
-\begin{figure}[h]
+\begin{figure}[t]
     \centering
-    \includegraphics[width=0.8\columnwidth]{plots/voltage_divider/vd_scheme.pdf}
-    \caption{}\label{fig:vd_scheme}
+    \includegraphics[width=0.5\columnwidth]{plots/voltage_divider/vd_scheme.pdf}
+    \caption{Schematical representation of a memristor voltage divider.}\label{fig:vd_scheme}
 \end{figure}
 
-We initialize the system with pressures $P_1 =  P_2 = 1 bar$ and ion concentration $\rho_1 = \rho_2 = 0.2 mM$ on each node, length $L_1 = L_2 = 10\mu m$ and base radius  $R_{b1} = R_{b2} = 200 nm$ on each edge.
+We initialize the system with pressures $P_1 =  P_2 = 1 \text{bar}$ and ion concentration $\rho_1 = \rho_2 = 0.2 \text{mM}$ on each node, length $L_1 = L_2 = 10\mu \text{m}$ and base radius  $R_{b1} = R_{b2} = 200 \text{nm}$ on each edge.
 After choosing one of these four physical quantities as training parameter $\boldsymbol{w} = \brac{w_1, w_2}$, we implement the training as described in \cref{sec:training} that modifies them, while the other parameters are kept constant.
-In \cref{fig:mse_weights_vd} we show that the cost function normalized to its initial value decreases of many order of magnitude during the training for each of the chosen weight.
-The values of the chosen set of weights simultaneously changes from the initial condition, as shown in Figures [], adjusting the behaviour of the network to the desired one.
-If the values of a chosen type of weight at the end of the training are imposed to the network together with the voltage inputs, the network will autonomously relax to a steady state that coincides with the desired state.
-To exemplify this point, the inset in Figure shows the physical relaxation of the voltage divider when the trained values of pressure, which correspond to the three values in the last training step, are imposed on the nodes together with the constant inputs voltages.
-The inset shows that the output voltage $V_2$ autonomously relaxes to the desired value of $V_D=4V$ in a time scale characteristic of the memristor.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\columnwidth]{plots/voltage_divider/mse_weights_vd.pdf}
-    \caption{(a) Behaviour of the cost function during the training of the voltage divider.
-Different colors indicate that the training is done with a specific choice of training weights, as indicated in the legend.
-(b) Pressures imposed on the three nodes of the voltage divider during training.
-The inset shows the relaxation to the steady state of the output voltage $V_2$ to the desired value $V_D$ when the pressures imposed are the values obtained in the last training step, and the input nodes are stimulated with fixed voltage.
-(c) Ion concentration densities imposed on the three nodes of the voltage divider during training.
-(d) Length of the memristors during training.
-(e) Base radius of the memristors during training.}\label{fig:mse_weights_vd}
-\end{figure}
-
-In order to investigate the adaptability of the algorithm, we trained the system with a set of three consequent desired voltages $V_D=\{1V, 3V, 4V\}$.
-In \cref{fig:evolution_targets} we show how the output voltage $V_2$ subsequently adapts to the desired voltages during the training of the pressures in the nodes, the evolution of which can be seen in \cref{fig:evolution_targets}.
-It is evident that the system can be retrained at any stage to a new desired objective making it reusable.
-Any other weight type can be chosen, depending on the necessity.
-
-\begin{figure}[h]
+\begin{figure}[b]
     \centering
     \includegraphics[width=0.8\columnwidth]{plots/voltage_divider/evolution_targets.pdf}
-    \caption{(a) The training of a memristor voltage divider to a set of desired voltage outputs $V_D = {1V, 3V, 4V}$, indicated by dashed light purple lines.
+    \caption{(a) The training of a memristor voltage divider to a set of desired voltage outputs, indicated by dashed light purple lines.
 The output voltage $V_2$, indicated by dark purple dots, adapts to the desired output during the training.
@@
 \end{figure}
+In \cref{fig:mse_weights_vd}(a) we show that the cost function normalized to its initial value decreases of many order of magnitude during the training for each of the chosen weight.
+The values of the chosen set of weights simultaneously changes from the initial condition, as shown in \cref{fig:mse_weights_vd}(b)-(e), adjusting the behaviour of the network to the desired one.
+If the values of a chosen type of weight at the end of the training are imposed to the network together with the voltage inputs, the network will autonomously relax to a steady state that coincides with the desired state.
+To exemplify this point, the inset in \cref{fig:mse_weights_vd}(b) shows the physical relaxation of the voltage divider when the trained values of pressure, which correspond to the three values in the last training step, are imposed on the nodes together with the constant inputs voltages.
+The inset shows that the output voltage $V_2$ autonomously relaxes to the desired value of $V_D=4V$ in a time scale characteristic of the memristor.
+
+In order to investigate the adaptability of the algorithm, we trained the system with a set of three consequent desired voltages $V_D=\{1V, 3V, 4V\}$.
+In \cref{fig:evolution_targets} we show how the output voltage $V_2$ subsequently adapts to the desired voltages during the training of the pressures in the nodes, the evolution of which can be seen in \cref{fig:evolution_targets}(b).
+It is evident that the system can be retrained at any stage to a new desired objective making it reusable.
+Any other weight type can be chosen, depending on the necessity.
 
@@
     \includegraphics[width=0.5\textwidth]{plots/general_network/mse_general.pdf}
-    \caption{(a) Generic network with $9$ nodes and $15$ edges with inputs $[V_{2}, V_{4}, V_{9}] = [0V, 2V, 5V]$ and desired outputs $[V_{5}^D, V_{7}^D] = [3V, 4V]$, delta weights a third of their initial value and learning rates $[0.001, 1, 0.0001, 0.001]$.
+    \caption{(a) Generic network with $9$ nodes and $15$ edges with inputs $[V_{2}, V_{4}, V_{9}] = [0V, 2V, 5V]$ and desired outputs $[V_{5}^D, V_{7}^D] = [3V, 4V]$, learning rates $[10^{-3}, 1, 10^{-4}, 10^{-3}]$.
 (b) Cost function during training of generic graph for input-output mapping task.
@@
     \centering
-    \includegraphics[width=\textwidth]{plots/regression/regression_G00010001.pdf}
+    \includegraphics[width=0.85\textwidth]{plots/regression/regression_G00010001.pdf}
     \caption{}\label{fig:lin_regr1}
@@
 The training algorithm described in \cref{sec:training} can be slightly adapted to support this training objective.
-At each training step, an input-output voltage pair is selected from the training set and used as the input voltage and target output in the algorithm.
+At each training step, an input-output voltage pair, or sets, is selected from the training set and used as the input voltage and target output in the algorithm.
 This differs from the original algorithm, where the same input-output pair was presented at every step.
@@
     \centering
-    \includegraphics[width=\textwidth]{plots/regression/regression_G00010002.pdf}
+    \includegraphics[width=0.85\textwidth]{plots/regression/regression_G00010002.pdf}
     \caption{}\label{fig:lin_regr2}
@@
 
-\section{Conclusions}
+\section{\label{sec:concl}Conclusions}
 
@@
 
-\begin{algorithm}
-    \caption{Relaxation of a Memristor Voltage Divider to Steady State}
-    \label{alg:relaxation}
-    \begin{algorithmic}[1]
-    \State \textbf{Input:} Initial conductance $g_0$, time step $\Delta t$, convergence threshold $\epsilon$, relaxation time $\tau$
-    \State Initialize $g_1 \gets g_0$, $g_2 \gets g_0$, $t \gets 0$
-    \While{not converged}
-        \State Compute $\Delta V_1 \gets \frac{5 \cdot g_2}{g_1 + g_2}$
-        \State Compute $\Delta V_2 \gets \frac{5 \cdot g_1}{g_1 + g_2}$
-        \State $g_1 \gets g_1 + \frac{g_{\infty}(\Delta V_1) - g_1}{\tau} \cdot \Delta t$
-        \State $g_2 \gets g_2 + \frac{g_{\infty}(\Delta V_2) - g_2}{\tau} \cdot \Delta t$
-        \If{$|g_1 - g_{\infty}(\Delta V_1)| < \epsilon$ \textbf{and} $|g_2 - g_{\infty}(\Delta V_2)| < \epsilon$}
-            \State \textbf{break}
-        \EndIf
-    \EndWhile
-    \end{algorithmic}
-\end{algorithm}
+% \begin{algorithm}
+%     \caption{Relaxation of a Memristor Voltage Divider to Steady State}
+%     % \label{alg:relaxation}
+%     \begin{algorithmic}[1]
+%     \State \textbf{Input:} Initial conductance $g_0$, time step $\Delta t$, convergence threshold $\epsilon$, relaxation time $\tau$
+%     \State Initialize $g_1 \gets g_0$, $g_2 \gets g_0$, $t \gets 0$
+%     \While{not converged}
+%         \State Compute $\Delta V_1 \gets \frac{5 \cdot g_2}{g_1 + g_2}$
+%         \State Compute $\Delta V_2 \gets \frac{5 \cdot g_1}{g_1 + g_2}$
+%         \State $g_1 \gets g_1 + \frac{g_{\infty}(\Delta V_1) - g_1}{\tau} \cdot \Delta t$
+%         \State $g_2 \gets g_2 + \frac{g_{\infty}(\Delta V_2) - g_2}{\tau} \cdot \Delta t$
+%         \If{$|g_1 - g_{\infty}(\Delta V_1)| < \epsilon$ \textbf{and} $|g_2 - g_{\infty}(\Delta V_2)| < \epsilon$}
+%             \State \textbf{break}
+%         \EndIf
+%     \EndWhile
+%     \end{algorithmic}
+% \end{algorithm}
 

### 2025-06-05 codes/linear_regression.py

@@ -10,7 +10,7 @@ import numpy as np
 
 start = time.time()
 
-graph_id = 'G00010002'
+graph_id = 'G00060001'
 DATA_PATH = f'{par.DATA_PATH}regression{graph_id}/'
 
 # --------- INITIALIZE NETWORK ---------
@@ -27,7 +27,7 @@ G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 print(G.edges())
 # G.add_edge('1','7')
 # networks.initialize_edges(G)
-# G = networks.to_directed_graph(G, shuffle=True)
+G = networks.to_directed_graph(G, shuffle=True)
 G.graph['name'] = graph_id
 print(G.graph['name'])
 nx.write_graphml(G, f'{DATA_PATH}{graph_id}.graphml')
@@ -51,12 +51,12 @@ training_type = 'regression'    # choose
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
 # learning_rate_vec = [2e-7, 1e-6, 1e-4, 2e2, 1e3]
-learning_rate_vec = [5e-7, 1e-6, 9e-4, 2e2, 1e3]
-constant_source = [11, 4, 4, 4]
+learning_rate_vec = [3e-7, 1e-6, 9e-4, 2e2, 1e4]
+constant_source = [11, 4, 4, 11]
 
 weight_type_index = 0   # choose
 
-for weight_type_index in [2]:
+for weight_type_index in [0,1,2,3]:
     
     G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 #     G = nx.read_graphml(f'{DATA_PATH}G00050001.graphml')
@@ -64,7 +64,7 @@ for weight_type_index in [2]:
 #     # G = nx.read_graphml(f'{DATA_PATH}G00010003.graphml')
     G.nodes['3']['voltage'] = constant_source[weight_type_index]
 
-    # training.train(G, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index], save_final_graph=True, write_weights=True)
[…]

### 2025-06-05 paper/paper.tex
Paper beofre incorporating comments

@@
 A modification to any of these weights affects the network's behaviour by altering the functional form of the memristor’s steady-state conductance, $g_{\infty}(\boldsymbol{\Delta})$, which depends on the local potential, pressure, and concentration drops across the device.
-Importantly, the \emph{entire functional shape} of $g_{\infty}$ plays a role in determining the network’s dynamics and ultimate steady state, as illustrated in \cref{app:dyn_evol_steady_state}.
+Importantly, the functional shape of $g_{\infty}$ plays a role in determining the network’s dynamics and ultimate steady state, as illustrated in \cref{app:dyn_evol_steady_state}.
 
@@
 (b) Pressures imposed on the three nodes of the voltage divider during training.
-The inset shows the relaxation to the steady state of the output voltage $V_2$ to the desired value $V_D$ when the pressures imposed are the values obtained in the last training step, and the input nodes are stimulated with fixed voltage.
+The inset shows the relaxation to the steady state of the output voltage $V_2$ to the desired value $V_2^D$ when the pressures imposed are the values obtained in the last training step, and the input nodes are stimulated with fixed voltage.
 (c) Ion concentration densities imposed on the three nodes of the voltage divider during training.
@@
 The value of the outputs can be used to quantify the status of the network, meaning how much its answer differs from the desired one.
-Specifically, we define a cost function that computes the difference squared between the voltage in the output nodes and the values of desired voltages
+Specifically, we define a \emph{cost function} that computes the difference squared between the voltage in the output nodes and the values of desired voltages
 \[
@@
 Given the simplicity of its structure, we use it as an initial playground for the training algorithm described above.
-Specifically, we replace the resistances with memristor channels, to be trained such that giving $V_1 = 5V$ and $V_3 = 0V$ as inputs, we get $V_2 = 4V$ as output.
+Specifically, we replace the resistances with memristor channels, to be trained such that giving $V_1 = 5V$ and $V_3 = 0V$ as inputs, we get $V_2^D = 4V$ as output.
 In \cref{fig:vd_scheme} a schematic of the memristor voltage divider is shown.
@@
 To exemplify this point, the inset in \cref{fig:mse_weights_vd}(b) shows the physical relaxation of the voltage divider when the trained values of pressure, which correspond to the three values in the last training step, are imposed on the nodes together with the constant inputs voltages.
-The inset shows that the output voltage $V_2$ autonomously relaxes to the desired value of $V_D=4V$ in a time scale characteristic of the memristor.
+The inset shows that the output voltage $V_2$ autonomously relaxes to the desired value of $V_2^D=4V$ in a time scale characteristic of the memristor.
 
-In order to investigate the adaptability of the algorithm, we trained the system with a set of three consequent desired voltages $V_D=\{1V, 3V, 4V\}$.
+In order to investigate the adaptability of the algorithm, we trained the system with a set of three consequent desired voltages $V_2^D=\{1V, 3V, 4V\}$.
 In \cref{fig:evolution_targets} we show how the output voltage $V_2$ subsequently adapts to the desired voltages during the training of the pressures in the nodes, the evolution of which can be seen in \cref{fig:evolution_targets}(b).
@@
     \includegraphics[width=0.85\textwidth]{plots/regression/regression_G00010001.pdf}
-    \caption{}\label{fig:lin_regr1}
+    \caption{(a) Network geometry used for linear regression training.
+The network comprises $17$ edges connecting $10$ nodes, including one output node (purple dot) and three input nodes (green dots).
+Among the three input nodes, one is used to ground the circuit ($V_2 = 0V$), one ($V_4$) provides a constant voltage source for bias, and the remaining one ($V_4$) is used to input the training data point.
+(b) Test cost function evaluated every $10$ training steps for four different weight choices.
+Insets show visual representations of the network’s output trained with varying channel lengths at three different training steps.}\label{fig:lin_regr1}
 \end{figure*}
@@
 From the behaviour of the cost function, it is evident that the choice of weight type has a decisive impact on the network’s ability to learn a complex task.
-Specifically, training the lengths of the channels on the edges results in successful convergence, whereas training the node pressures proves to be extremely inefficient.
-For a visual interpretation of the regression cost function, \cref{fig:lin_regr1}(c) shows the state of the training at three different time steps.
+Specifically, training the lengths of the channels on the edges results in successful convergence, whereas training the node pressures proves to be less efficient.
+For a visual interpretation, insets in \cref{fig:lin_regr1}(b) show the state of the training at three different time steps when the selected weight is the length of the channel.
 \begin{figure*}[t]
@@
     \includegraphics[width=0.85\textwidth]{plots/regression/regression_G00010002.pdf}
-    \caption{}\label{fig:lin_regr2}
+    \caption{(a) Network geometry used for linear regression training.
+It is equivalent to the geometry shown in \cref{fig:lin_regr1}, but the direction of the memristors highlighted in orange has been inverted.
+(b) Test cost function evaluated every $10$ training steps for four different weight choices.
+Insets show visual representations of the network’s output trained with varying node ion density at two different training steps.}\label{fig:lin_regr2}
 \end{figure*}
@@
 Specifically, if in the original configuration the base of a memristor pointed to one node and the tip to another, we reversed this direction.
-
 This modification significantly affects the behaviour of the network.
 As shown in \cref{fig:lin_regr2}(b), the new orientation alters the trainability of different weight types: in this configuration, training node concentration leads to better performance, while training edge length becomes less efficient.
-The underlying reason is that inverting the orientation of a channel also inverts the sign of the external stimulus applied to it, since the stimuli are defined node-wise and the difference is always taken as "base minus tip."
+The underlying reason is that inverting the orientation of a channel also inverts the sign of the external stimulus applied to it, since the stimuli are defined node-wise and the difference is always taken as ''base minus tip".
 
-This reversal changes both the shape and the conductivity range over which the function $g_{\infty}(\boldsymbol{\Delta})$ is defined, thereby limiting or enabling the conductivity values the channel can attain.
+This reversal changes both the shape and the conductivity range over which the function $g_{\infty}(\boldsymbol{\Delta})$ is defined, thereby limiting or enabling the conductivity values the channel can reach.
 A network with well-oriented channels can therefore access conductivity ranges that make the training solvable, while a poorly oriented network may be constrained to regions where solutions are not found.
-To exemplify this point, Figure~(X) of Ref.~(Y) shows $g_{\infty}$ as a function of pressure for positive and negative potential drops, assuming a zero concentration drop.
+To exemplify this point, Figure 2 of Ref.\cite{Rene_PressureSensitive} shows $g_{\infty}$ as a function of pressure for positive and negative potential drops, assuming a zero concentration drop.
 The plot reveals two completely disjoint conductivity ranges depending on the sign of the potential drop, which explains why training on pressure alone may be challenging.
@@
 This suggests that particular attention should be given to these edges in future explorations, as they may have a bigger impact on trainability.
-As for the length-based training, \cref{fig:lin_regr2}(c) illustrates how the network responds to the test set at three different stages of the training process.
-
-Bigger networks have more degrees of freedom, and should allow for a bigger range of exploration of a solution.
-However, the experimental realization would become more challenging.
-In this work, we show that an adequate geometry for a specific training goal can be sufficient to make a small network trainable.
-A deeper analysis on the influence of geometry on the trainability is needed in the research contest of physical learning and can be explored in future research.
-
-Larger networks offer more degrees of freedom and can, in principle, enable broader exploration of the solution space.
-However, their experimental realization becomes increasingly complex.
-In this work, we showed that an appropriately chosen geometry adapted to a specific training objective can be sufficient to make even a small networks trainable.
-A deeper analysis of the role of geometry in determining trainability is still needed in the context of physical learning.
 
@@
 Additionally, their conductivity is sensitive to changes in the geometric parameters of their channel-like structure.
-
 Our motivation for using these devices lies in the ability to exploit these dependencies to control the conductance of each memristor in the network.
@@
 Training larger and more complex memristor networks is also feasible with the algorithm we proposed.
-We demonstrated that a network composed of 9 nodes and 15 edges can be successfully trained for input-output voltage mapping using all the weight types considered.
+We demonstrated that a network composed of 9 nodes and 15 edges can be successfully trained for more elaborated input-output voltage mapping using all the weight types considered.
 
-We then challenged a more complex network, with 10 nodes and 20 edges, to perform a linear regression task with an offset.
+We then challenged a more complex network, with 10 nodes and 17 edges, to perform a linear regression task with an offset.
 In this setting, we observed that the trainability of the network using a specific weight type strongly depends on the network's geometry.
@@
 Given that the expressiveness of deep neural networks grows exponentially with depth\cite{big_neuralnet1, big_neuralnet2}, we interpret the limitations encountered in training linear regression tasks as a consequence of the small size of the network.
-However, small-scale networks are experimentally attractive, and in such cases, a training error of a few orders of magnitude may be acceptable.
-A key challenge for scaling such networks lies in the physical control of individual weights, especially when the weight type involves mechanical or geometric parameters.
-Emerging technologies in microfluidics, soft robotics, and programmable matter may provide practical tools to overcome these limitations and scale the network while preserving control.
+Larger networks offer more degrees of freedom and can, in principle, enable broader exploration of the solution space.
+However, their experimental realization becomes complex.
+In this work, we showed that an appropriately chosen geometry adapted to a specific training objective can be sufficient to make even a small networks trainable.
+A deeper analysis of the role of geometry in determining trainability is still needed in the context of physical learning.
 

### 2025-06-05 codes/linear_regression.py

@@ -27,7 +27,7 @@ G = nx.read_graphml(f'{DATA_PATH}{graph_id}.graphml')
 print(G.edges())
 # G.add_edge('1','7')
 # networks.initialize_edges(G)
-G = networks.to_directed_graph(G, shuffle=True)
+# G = networks.to_directed_graph(G, shuffle=True)
 G.graph['name'] = graph_id
 print(G.graph['name'])
 nx.write_graphml(G, f'{DATA_PATH}{graph_id}.graphml')
@@ -50,8 +50,9 @@ training_type = 'regression'    # choose
 
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure', 'resistance']
 delta_weight_vec = [1e-3, 1e-3, 1e-4, 1e-3, 1e-3]
-# learning_rate_vec = [2e-7, 1e-6, 1e-4, 2e2, 1e3]
-learning_rate_vec = [3e-7, 1e-6, 9e-4, 2e2, 1e4]
+# learning_rate_vec = [2e-7, 1e-6, 1e-4, 2e2, 1e3] #1
+# learning_rate_vec = [3e-7, 1e-6, 9e-4, 2e2, 1e4] #2
+learning_rate_vec = [8e-7, 3e-6, 2e-4, 5e1, 1e4]
 constant_source = [11, 4, 4, 11]
 
 weight_type_index = 0   # choose

### 2025-06-06 paper_overleaf/paper.tex
Modified vd radius base.

--- 2025-06-05 paper/paper.tex
@@
 
-\title{Efficient Machine Learning in a Memristor Network}
+\title{Multistimulus Machine Learning in Microfluidic Memristor Networks}
 
 \author{Monica Conte}
-\affiliation{Soft Condensed Matter \& Biophysics, Debye Institute for Nanomaterials Science, Utrecht University, Princetonplein 1, 3584 CC Utrecht, The Netherlands.}
+\affiliation{Soft Condensed Matter \& Biophysics, Debye Institute for Nanomaterials Science, Utrecht University, Princetonplein 1, 3584 CC Utrecht, The Netherlands,}
+\author{René van Roij}
+\affiliation{Institute for Theoretical Physics, Utrecht University, Princetonplein 5, 3584 CC Utrecht, The Netherlands.}
+\author{Marjolein Dijkstra}
+\affiliation{Soft Condensed Matter \& Biophysics, Debye Institute for Nanomaterials Science, Utrecht University, Princetonplein 1, 3584 CC Utrecht, The Netherlands,}
 
@@
 \begin{abstract}
-Inspired by the brain's energy-efficient processing, we propose a physical implementation of artificial neural networks to surpass digital systems in speed and energy efficiency.
+Inspired by the brain's energy-efficient processing, we propose a physical implementation of artificial neural networks to surpass digital systems in thier capabilities.
 We consider a network with nodes connected by conical microfluidic memristor channels filled with aqueous electrolyte [1].
-These memristors exhibit tunable conductance, responsive to electrical, chemical, and mechanical stimuli, as well as channel geometry.
-Based on this adaptability, we develop a hybrid training algorithm that adjusts either channel geometry or external stimuli as weights.
-Physical relaxation replaces the feedforward pass, while a combined physical-numerical gradient descent drives the backward pass.
-This approach enables tasks such as input-output voltage mapping and linear regression with bias.
+These memristive channels exhibit tunable conductance, in response to electrical, chemical, and mechanical stimuli, as well as to changes in channel geometry.
+Leveraging this multistimulus adaptability, we develop a hybrid training algorithm that treats either the channel geometry or external stimuli as adjustable weights.
+In this framework, the system itself performs the feedforward pass through physical relaxation, while a combined physical-numerical gradient descent executes the backward pass.
+The network performs basic learning tasks, such as input-output voltage mapping and linear regression with bias.
 \end{abstract}
@@
 Other methods, based on coupled learning\cite{supervised_learning}, implement local learning rules at the level of each connection or edge\cite{demonstr_coupled_learning}.
-Applying local rules removed the need of the optimiziation of a global function during training, as in standard backpropagation methods.
+Applying local rules removed the need of the optimiziation of a global cost function during learning, as in standard backpropagation methods.
 However, these approaches still face the need for two identical physical systems to apply different boundary conditions.
@@
 This section is followed by conclusions and suggestions for future work in \cref{sec:concl}.
-
-\newpage
+% \newpage
 
@@
 Meanwhile, the pressure drop $\Delta P = P_b - P_t$, given by the difference between the base and the tip pressure, induces a Poiseuille-like flow $Q_P = (\pi R_b^3 R_t^3/8L\eta\langle R^2\rangle)\Delta P$.
-Finally, the ions experience a concentration gradient $\Delta \rho = \rho_b - \rho_t$, defined by the difference between the ion concentration in the reservoir connected to the base of the channel, $\rho_b$, and the concentration in the reservoir connected to the tip, $\rho_t$.
+Finally, the ions experience a salt concentration gradient $\Delta \rho = \rho_b - \rho_t$, defined by the difference between the ion concentration in the reservoir connected to the base of the channel, $\rho_b$, and the concentration in the reservoir connected to the tip, $\rho_t$.
 Consequently, a diffusive fluid flow arises.
@@
 
-The PNN is composed of $\N$ nodes, an example is shown in \cref{fig:memristor_network}. 
+The PNN is composed of $N$ nodes, an example is shown in \cref{fig:memristor_network}. 
 \begin{figure}[t]
@@
 \end{figure} 
-Each node $\n\in[1,\N]$ is characterized by a value of electrical potential $V_{\n}$, pressure $P_{\n}$ and bulk density $\rho_{\n}$.
+Each node $\n\in[1,N]$ is characterized by a value of electrical potential $V_{\n}$, pressure $P_{\n}$ and bulk density $\rho_{\n}$.
 Even though each node in the network is characterized by three physical properties, only electrical current flows through the network.
@@
 
-The nodes in the PNN are connected by $\M$ memristive elements.
-Consequently, a memristor connecting two nodes experiences potential drop, pressure drop and concentration gradient given by the difference between the node where the base of the memristor is connected to, and the node to which the tip is linked.
-The memristor is characterized by its conductance state $g_{\m}$ with $\m\in[1,\M]$, consequence of both the geometry parameters and the external stimuli.
+The nodes in the PNN are connected by $M$ memristive elements.
+Consequently, a memristor connecting two nodes experiences a potential drop, pressure drop and concentration gradient given by the difference between the node where the base of the memristor is connected to, and the node to which the tip is linked.
+The memristor is characterized by its conductance state $g_{\m}$ with $\m\in[1,M]$, consequence of both the geometry parameters and the external stimuli.
 To solve numerically the resulting circuit, it is necessary to simultaneously address the circuit equations and the time evolution equation for the memristors' conductance. 
@@
     \includegraphics[width=1.7\columnwidth]{plots/voltage_divider/mse_weights_vd.pdf}
-    \caption{(a) Behaviour of the cost function during the training of the memristor voltage divider.
+    \caption{(a) Behaviour of the cost function $C(\boldsymbol{w})$ during the training of the memristor voltage divider.
 Different colors indicate that the training is done with a specific choice of training weights, as indicated in the legend.
@@
 
-% \cleardoublepage
 \subsection{\label{sec:linear_regression}Linear Regression}
@@
 Among the three input nodes, one is used to ground the circuit ($V_2 = 0V$), one ($V_4$) provides a constant voltage source for bias, and the remaining one ($V_4$) is used to input the training data point.
+For the four weight types (channle length, base radius, ion density and pressure), we used as constant voltage input $V_4 = [11V,4V,4V,11V]$ and learning rates $[2\cdot 10^{-7}, 1\cdot 10^{-6}, 1\cdot 10^{-4}, 2\cdot 10^{2}]$.
 (b) Test cost function evaluated every $10$ training steps for four different weight choices.
@@
 
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=0.85\textwidth]{plots/regression/regression_G00010002.pdf}
+    \caption{(a) Network geometry used for linear regression training.
+It is equivalent to the geometry shown in \cref{fig:lin_regr1}, but the direction of the memristors highlighted in orange has been inverted.
+For the four weight types (channle length, base radius, ion density and pressure), we used as constant voltage input $V_4 = [11V,4V,4V,11V]$ and learning rates $[3\cdot 10^{-7}, 1\cdot 10^{-6}, 9\cdot 10^{-4}, 2\cdot 10^{2}]$.
+(b) Test cost function evaluated every $10$ training steps for four different weight choices.
+Insets show visual representations of the network’s output trained with varying node ion density at two different training steps.}\label{fig:lin_regr2}
+\end{figure*} 
 To evaluate how well the algorithm performs during training, we compute the \emph{test cost function} $ C_{\text{test}} $ over the entire test set.
@@
 For a visual interpretation, insets in \cref{fig:lin_regr1}(b) show the state of the training at three different time steps when the selected weight is the length of the channel.
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=0.85\textwidth]{plots/regression/regression_G00010002.pdf}
-    \caption{(a) Network geometry used for linear regression training.
-It is equivalent to the geometry shown in \cref{fig:lin_regr1}, but the direction of the memristors highlighted in orange has been inverted.
-(b) Test cost function evaluated every $10$ training steps for four different weight choices.
-Insets show visual representations of the network’s output trained with varying node ion density at two different training steps.}\label{fig:lin_regr2}
-\end{figure*}
 
@@
 
-% \begin{algorithm}
-%     \caption{Relaxation of a Memristor Voltage Divider to Steady State}
-%     % \label{alg:relaxation}
-%     \begin{algorithmic}[1]
-%     \State \textbf{Input:} Initial conductance $g_0$, time step $\Delta t$, convergence threshold $\epsilon$, relaxation time $\tau$
-%     \State Initialize $g_1 \gets g_0$, $g_2 \gets g_0$, $t \gets 0$
-%     \While{not converged}
-%         \State Compute $\Delta V_1 \gets \frac{5 \cdot g_2}{g_1 + g_2}$
-%         \State Compute $\Delta V_2 \gets \frac{5 \cdot g_1}{g_1 + g_2}$
-%         \State $g_1 \gets g_1 + \frac{g_{\infty}(\Delta V_1) - g_1}{\tau} \cdot \Delta t$
-%         \State $g_2 \gets g_2 + \frac{g_{\infty}(\Delta V_2) - g_2}{\tau} \cdot \Delta t$
-%         \If{$|g_1 - g_{\infty}(\Delta V_1)| < \epsilon$ \textbf{and} $|g_2 - g_{\infty}(\Delta V_2)| < \epsilon$}
-%             \State \textbf{break}
-%         \EndIf
-%     \EndWhile
-%     \end{algorithmic}
-% \end{algorithm}
+\begin{algorithm}
+    \caption{}
+    \label{alg:relaxation}
+    \begin{algorithmic}[1]
+    \State \textbf{Input:} Initial conductance $g_0$, time step $\Delta t$, convergence threshold $\epsilon$, relaxation time $\tau$
+    \State Initialize $g_1 \gets g_0$, $g_2 \gets g_0$, $t \gets 0$
+    \While{not converged}
+        \State Compute $\Delta V_1 \gets \frac{5 \cdot g_2}{g_1 + g_2}$
+        \State Compute $\Delta V_2 \gets \frac{5 \cdot g_1}{g_1 + g_2}$
+        \State $g_1 \gets g_1 + \frac{g_{\infty}(\Delta V_1) - g_1}{\tau} \cdot \Delta t$
+        \State $g_2 \gets g_2 + \frac{g_{\infty}(\Delta V_2) - g_2}{\tau} \cdot \Delta t$
+        \If{$|g_1 - g_{\infty}(\Delta V_1)| < \epsilon$ \textbf{and} $|g_2 - g_{\infty}(\Delta V_2)| < \epsilon$}
+            \State \textbf{break}
+        \EndIf
+    \EndWhile
+    \end{algorithmic}
+\end{algorithm}
 

### 2025-06-06 codes/plotting.py

@@ -106,8 +106,8 @@ def plot_weights(ax, G, training_steps, training_type, weight_type, show_xlabel=
     
     style = par.weight_styles[f'{weight_type}']
     base_color = style['c']
-    # palette = [lighten_color(base_color, factor = i * color_factor) for i in range(number_weights)]
-    palette = plt.get_cmap('tab20')
+    palette = [lighten_color(base_color, factor = i * color_factor) for i in range(number_weights)]
+    # palette = plt.get_cmap('tab20')
       
     # GET data: data/training_job/weight_type contains files weight_type{step} with the list of weights per step
     for weight_indx in range(number_weights):
@@ -119,8 +119,8 @@ def plot_weights(ax, G, training_steps, training_type, weight_type, show_xlabel=
             weight.append(y[weight_indx])
 
         label_without_weightindex = style['label'][1:-1]
-        # ax.plot(x, weight, color=palette[weight_indx], marker = style['marker'], lw = style['lw'], label = rf'${{{label_without_weightindex}}}_{{{weight_indx+1}}}$')
-        ax.plot(x, weight, color=palette(weight_indx), marker = style['marker'], lw = style['lw'], label = rf'${{{label_without_weightindex}}}_{{{weight_indx+1}}}$')
+        ax.plot(x, weight, color=palette[weight_indx], marker = style['marker'], lw = style['lw'], label = rf'${{{label_without_weightindex}}}_{{{weight_indx+1}}}$')
+        # ax.plot(x, weight, color=palette(weight_indx), marker = style['marker'], lw = style['lw'], label = rf'${{{label_without_weightindex}}}_{{{weight_indx+1}}}$')
         # ax.plot(x, weight, marker = style['marker'], lw = style['lw'], label = rf'${{{label_without_weightindex}}}_{{{weight_indx+1}}}$')
         
     label = style['ylabel_weights']

### 2025-06-06 codes/voltage_divider.py

@@ -20,24 +20,25 @@ fig, ax = plt.subplots()
 pos = plotting.plot_graph(G)
 fig.tight_layout()
 fig.savefig(f"../plots/voltage_divider/graph.pdf")
+graph_id = 'voltage_divider'
 
 # --------- TRAIN NETWORK WITH DIFFERENT WEIGHTS ---------
 
-training_steps = 10
+training_steps = 50
 training_type = 'allostery'
 weight_type_vec = ['length', 'radius_base', 'rho', 'pressure']
 delta_weight_vec = [1e-3, 1, 1e-4, 1e-3]
-learning_rate_vec = [3e-6, 3e-6, 5e-4, 1e2]
+learning_rate_vec = [3e-6, 3.5e-6, 5e-4, 1e2]
 # learning_rate_vec = [5e-7, 3e-7, 5e-3, 1e4]
 # learning_rate_vec = [1e-5, 1e-5, 5e-3, 1e3]
 # learning_rate_vec = [1e-5, 2e-6, 5e-3, 5e2]
 
 
 # for weight_type_index in range(len(weight_type_vec)):
-weight_type_index = 3
+weight_type_index = 1
 
 G_ml = G.copy(as_view=False)  
-training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index])
+training.train(G_ml, training_type=training_type, training_steps=training_steps, weight_type=weight_type_vec[weight_type_index], delta_weight = delta_weight_vec[weight_type_index], learning_rate=learning_rate_vec[weight_type_index], write_weights=True)
 
 # --------- PLOT EVOLUTION OF TRAINED NW ---------
  
@@ -52,23 +53,23 @@ fig = plt.figure(figsize=(12, 8))
 gs = gridspec.GridSpec(2, 3, height_ratios=[1, 1])
 
 ax1 = fig.add_subplot(gs[0, 0:2]) 
-plotting.plot_mse(ax1, fig, f'pressure', show_xlabel = False)
-plotting.plot_mse(ax1, fig, f'rho', show_xlabel = False)
-plotting.plot_mse(ax1, fig, f'length', show_xlabel = False)
-plotting.plot_mse(ax1, fig, f'radius_base', show_xlabel = False)
[…]
